---
title: "dw-enrollment-check"
author: "XRZ"
date: '2022-10-26'
output: html_document
---

#Purpose:
This R markdown script examines the accuracy of conversions from raw source tables to
data_warehouse tables


# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(DBI, odbc, rstudioapi, keyring, openxlsx, tidyverse, beepr, tictoc, here)

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password


#Connect to Greenplum
tac <- dbConnect(odbc::odbc(),
	 dsn = "PostgreSQL30",
	 database = "uthealth",
	 UID = "xrzhang",
	 PWD = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(),
	 dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc")))
```

## 0.5 Set print to 25 rows
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)

```

# SECTION 1: Define global variables

```{r}
#Define the starting and ending years for checking (4-digit year)
starting_year = 2012
ending_year = 2021

#Define how many rows to check per year
rows_to_check = '100000'

#convert to 2-digit year
starting_yr = starting_year - 2000
ending_yr = ending_year - 2000
```

# SECTION 2: Prep local SQL server for scrutiny

## 2.1 Pull ELIG_DATE, AGE, SEX, DOB, and MCO into a table from all tables for cleaning

### 2.11 Declare base sql queries for modification
```{r}
#SEX, AGE, DOB, and MCO need to be cleaned, SO pull those into an ETL

spc_sql1 = 'insert into work.dbo.xz_mcd_reconciliation_etl
select a.CLIENT_NBR, \'@year\' as ENRL_FY, a.elig_date, try_cast(a.DOB as date) as dob, 
a.SEX, b.MCO_PROGRAM_NM as MCO, a.RACE, a.ZIP, a.SMIB,
case when a.me_code = \'W\' then 1 else 0 end as HTW
from medicaid.dbo.enrl_@year a left join medicaid.dbo.LU_Contract as b on a.CONTRACT_ID = b.PLAN_CD;

insert into work.dbo.xz_mcd_reconciliation_etl
select CLIENT_NBR, \'@year\' as ENRL_FY, elig_month, 
try_cast(substring(date_of_birth, 1, 9) as date) as dob, 
gender_cd, \'CHIP\' as MCO, ethnicity as race, substring(MAILING_ZIP, 1, 5) as zip, \'0\' as SMIB,
\'0\' as HTW
from medicaid.dbo.CHIP_UTH_SFY@year_Final;'

spc_sql2 = 'insert into work.dbo.xz_mcd_reconciliation_etl
select a.CLIENT_NBR, \'@year\' as ENRL_FY, a.elig_date, try_cast(a.DOB as date) as dob, 
a.SEX, b.MCO_PROGRAM_NM as MCO, a.RACE, a.ZIP, a.SMIB,
case when a.me_code = \'W\' then 1 else 0 end as HTW
from medicaid.dbo.ENRL_@year_HTW a left join medicaid.dbo.LU_Contract as b on a.CONTRACT_ID = b.PLAN_CD;'

```

### 2.12 Initialize table to hold data from yearly enrollment tables
```{sql, connection = spc}
--Initialize table
drop table if exists work.dbo.xz_mcd_reconciliation_etl;
create table work.dbo.xz_mcd_reconciliation_etl (
	CLIENT_NBR varchar(50),
	FY varchar(4),
	elig_date varchar(20),
	DOB date,
	SEX varchar(2),
	MCO varchar(50),
	RACE varchar(2),
	ZIP varchar(10),
	SMIB varchar(2),
	HTW int
);

```

### 2.13 Run query for all years
```{r}

#run query for all years
for (year in starting_year:ending_year){
  
  print(paste('Processing', year))
  spc_sql1.mod = spc_sql1 %>% gsub('@year', year, .)
  dbGetQuery(spc, spc_sql1.mod)
}

#add in HTW
for (year in 2018:2019){
  print(paste('Processing HTW', year))
  spc_sql2.mod = spc_sql2 %>% gsub('@year', year, .)
  dbGetQuery(spc, spc_sql2.mod)
}

```

## 2.2 Clean variables that need special treatment

### 2.21 Clean DOB across all data, bc DOB should be immutable

```{sql, connection = spc}
--clean dob
drop table if exists work.dbo.xz_mcd_reconcilation_dob_t;
select client_nbr, dob, count(distinct elig_date) as count, max(elig_date) as recent
into work.dbo.xz_mcd_reconcilation_dob_t
from work.dbo.xz_mcd_reconciliation_etl
group by client_nbr, dob;

drop table if exists work.dbo.xz_mcd_reconciliation_dob;
with cte as (select *,
  	    row_number() over (partition by client_nbr order by count desc, recent desc) as row_num
	from work.dbo.xz_mcd_reconcilation_dob_t)

select client_nbr, dob
into work.dbo.xz_mcd_reconciliation_dob
from cte
where row_num = 1;

--delete temp table
drop table if exists work.dbo.xz_mcd_reconcilation_dob_t;
```

### 2.22 Clean SEX on an FY basis
```{sql, connection = spc}
drop table if exists work.dbo.xz_mcd_reconcilation_sex_t;
select client_nbr, fy, sex, count(distinct elig_date) as count, max(elig_date) as recent
into work.dbo.xz_mcd_reconcilation_sex_t
from work.dbo.xz_mcd_reconciliation_etl
where sex in ('F', 'M') --clean out U or J
group by client_nbr, fy, sex;

drop table if exists work.dbo.xz_mcd_reconciliation_sex;
with cte as (select *,
  	    row_number() over (partition by client_nbr, fy order by count desc, recent desc) as row_num
	from work.dbo.xz_mcd_reconcilation_sex_t)

select client_nbr, fy, sex
into work.dbo.xz_mcd_reconciliation_sex
from cte
where row_num = 1;

--delete temp table
drop table if exists work.dbo.xz_mcd_reconcilation_sex_t;
```



### 2.23 Clean MCO (plan_type)
```{sql, connection = spc}
--Make MCO priority table
drop table if exists work.dbo.xz_mcd_mco_priority;

CREATE TABLE work.dbo.xz_mcd_mco_priority (
  plan_type varchar(20) NOT NULL,
  priority int NOT NULL
);

--add values to it
INSERT INTO work.dbo.xz_mcd_mco_priority(plan_type, priority)
  VALUES ('CHIP', 1 ),
	('STAR Kids', 2 ),
	('STAR+PLUS', 2 ),
	('STAR Health', 2 ),
	('STAR', 3 ),
	('MMP', 4 ),
	('FFS', 4 ),
	('PCCM', 4 );

--clean MCO
drop table if exists work.dbo.xz_mcd_reconcilation_mco_t;
select a.client_nbr, a.fy, a.mco, b.priority, count(distinct a.elig_date) as count, max(a.elig_date) as recent
into work.dbo.xz_mcd_reconcilation_mco_t
from work.dbo.xz_mcd_reconciliation_etl a left join work.dbo.xz_mcd_mco_priority b on a.mco = b.plan_type
group by a.client_nbr, a.fy, a.mco, b.priority;

drop table if exists work.dbo.xz_mcd_reconciliation_mco;
with cte as (select *,
  	    row_number() over (partition by client_nbr, fy order by count desc, priority, recent desc) as row_num
	from work.dbo.xz_mcd_reconcilation_mco_t)

select client_nbr, fy, mco
into work.dbo.xz_mcd_reconciliation_mco
from cte
where row_num = 1;

--delete temp tables
drop table if exists work.dbo.xz_mcd_mco_priority;
drop table if exists work.dbo.xz_mcd_reconcilation_mco_t;
```

## 2.3 Clean variables that do not need special treatment: RACE, ZIP, SMIB, HTW

###2.31 Declare list of variables to clean, base SQL query for modification
```{r}
variables_to_clean = c("race", "zip", "smib", "htw")

spc_sql3 = 'drop table if exists work.dbo.xz_mcd_reconcilation_@var_t;
            drop table if exists work.dbo.xz_mcd_reconciliation_@var;'

spc_sql4 = 'select client_nbr, fy, @var, count(distinct elig_date) as count, max(elig_date) as recent
into work.dbo.xz_mcd_reconcilation_@var_t
from work.dbo.xz_mcd_reconciliation_etl
group by client_nbr, fy, @var;

with cte as (select *,
  	    row_number() over (partition by client_nbr, fy order by count desc, recent desc) as row_num
	from work.dbo.xz_mcd_reconcilation_@var_t)

select client_nbr, fy, @var
into work.dbo.xz_mcd_reconciliation_@var
from cte
where row_num = 1;'

spc_sql5 = 'drop table if exists work.dbo.xz_mcd_reconcilation_@var_t;'
```

###2.32 Cycle through variables to clean
```{r}
for (i in 1:length(variables_to_clean)){
  current_var = variables_to_clean[i]
  
  print(paste("Cleaning", current_var))
  
  spc_sql3.mod = spc_sql3 %>% gsub('@var', current_var, .)
  spc_sql4.mod = spc_sql4 %>% gsub('@var', current_var, .)
  spc_sql5.mod = spc_sql5 %>% gsub('@var', current_var, .)
  
  dbGetQuery(spc, spc_sql3.mod)
  dbGetQuery(spc, spc_sql4.mod)
  dbGetQuery(spc, spc_sql5.mod)
}

```

## 2.4 Assemble it all together into a final table

```{sql, connection = spc}

--calculate enrolled_months and condense down to one row per client_nbr per fy
drop table if exists work.dbo.xz_mcd_enrl_reconciled_t;
select CLIENT_NBR as mem_id, FY, count(distinct elig_date) as enrolled_months
into work.dbo.xz_mcd_enrl_reconciled_t
from work.dbo.xz_mcd_reconciliation_etl
group by client_nbr, fy;

--join in half the data (do it in 2 operations to decrease server load)
drop table if exists work.dbo.xz_mcd_enrl_reconciled_t1;
select a.*, b.dob, c.sex, d.race
into work.dbo.xz_mcd_enrl_reconciled_t1
from work.dbo.xz_mcd_enrl_reconciled_t a
	left join work.dbo.xz_mcd_reconciliation_dob b on a.mem_id  = b.client_nbr
	left join work.dbo.xz_mcd_reconciliation_sex c on a.mem_id = c.client_nbr and a.fy = c.fy
	left join work.dbo.xz_mcd_reconciliation_race d on a.mem_id = d.client_nbr and a.fy = d.fy;

--join in other half of the data
drop table if exists work.dbo.xz_mcd_enrl_reconciled;
select a.*, e.zip, f.mco, g.smib, h.htw
into work.dbo.xz_mcd_enrl_reconciled
from work.dbo.xz_mcd_enrl_reconciled_t1 a
	left join work.dbo.xz_mcd_reconciliation_zip e on a.mem_id = e.client_nbr and a.fy = e.fy
	left join work.dbo.xz_mcd_reconciliation_mco f on a.mem_id = f.client_nbr and a.fy = f.fy
	left join work.dbo.xz_mcd_reconciliation_smib g on a.mem_id = g.client_nbr and a.fy = g.fy
	left join work.dbo.xz_mcd_reconciliation_htw h on a.mem_id = h.client_nbr and a.fy = h.fy;

--drop temp tables
drop table if exists work.dbo.xz_mcd_enrl_reconciled_t;
drop table if exists work.dbo.xz_mcd_enrl_reconciled_t1;

```

# SECTION 99: Close connections and clean-up

```{r close-connections, eval=FALSE}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env, eval=FALSE}
# clears R environment
rm(list=ls())
```



