---
title: "moving-chip-perinatal-raw-files-to-tacc"
author: "XRZ"
date: '2023-03-13'
output: html_document
---

#Purpose:
This R markdown script moves the CHIP perinatal raw files from SPCDEDPWPVS1 to TACC

Source tables: SPCDEDPWPVS1: medicaid.dbo.CHIP_Pren_FY[YEAR]
Target table: Greenplum: medicaid.CHIP_Pren


# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)


```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password

# Function for connecting to TACC/Greenplum
# TACC kicks you out for inactivity so just call function before connections
connect_to_tacc <- function() {
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
}

```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(),
	 dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment, eval=FALSE}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc", "connect_to_tacc")))
```

## 0.5 Declare root directory and set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation
here::i_am("moving-chip-perinatal-raw-files-to-tacc.rmd")

```

# SECTION 1: Initialization

```{r}

starting_year = 2016
ending_year = 2021
starting_yr = starting_year - 2000
ending_yr = ending_year - 2000

get_data_current_year = "select * from medicaid.dbo.CHIP_Pren_FY@year;"
count_rows_current_year = "select count(*) from medicaid.dbo.CHIP_Pren_FY@year;"
tac_current_year_rowcount = "select count(*) from medicaid.chip_pren_fy@year;"

#initialize DF to hold rowcounts
rowcounts = data.frame(matrix(ncol=4, nrow=0))
colnames(rowcounts) = c('year', 'spc_count', 'tac_count', 'difference')

```

# SECTION 2: Data transfer and rowcounting
```{r}
#Send all tables to SPC side

#refresh TACC connection bc it drops after 45 mins or so
tac = connect_to_tacc()

for (current_year in starting_year:ending_year){
  
  print(paste("Current year:", current_year))
    
  #modify all SQL code to reflect current year
  current_table_name = paste0("medicaid.chip_pren_fy", current_year)
  get_data_current_year.mod = get_data_current_year %>%
    gsub('@year', current_year, .)
  count_rows_current_year.mod = count_rows_current_year %>%
    gsub('@year', current_year, .)
  tac_current_year_rowcount.mod = tac_current_year_rowcount %>%
    gsub('@year', current_year, .)
  
  #Pull table from SPCDEDPWPVS1 and get the rowcount
  tic("Pulling data from SPC")
  current_year_data = dbGetQuery(spc, get_data_current_year.mod)
  current_year_rowcount = dbGetQuery(spc, count_rows_current_year.mod)
  toc()
  
  #send data to TACC and get rowcount
  tic("Sending data to TACC")
  dbWriteTable(tac, SQL(current_table_name), current_year_data, overwrite = TRUE)
  tac_side_rowcount = dbGetQuery(spc, count_rows_current_year.mod)
  toc()
  
  #Add data to rowcounts dataframe
  current_row = c(year = current_year, spc_count = current_year_rowcount,
                  tac_count = tac_side_rowcount, difference= (current_year_rowcount - tac_side_rowcount))
  rowcounts = rbind(rowcounts, current_row)
  
}

#fix colnames b/c that last column gets weird for some reason
colnames(rowcounts) = c('year', 'spc_count', 'tac_count', 'difference')

```

# SECTION 3: Compile chip_pren table on TACC side

```{r}
#Compile table on TACC side

tac_table_initialization1 = "drop table if exists medicaid.chip_pren;"

tac_table_initialization2 = "create table medicaid.chip_pren (
  fy int,
	client_nbr text, --10 digits
	elig_month text, -- 6 digit YYYYMM
	risk_group_cd text --3 digit numeric
) distributed by (client_nbr);"

tac_table_insert = "insert into medicaid.chip_pren
  select '@year' as fy, * from medicaid.chip_pren_fy@year;"

#refresh TACC connection bc it drops after 45 mins or so
tac = connect_to_tacc()

dbExecute(tac, tac_table_initialization1)
dbExecute(tac, tac_table_initialization2)

for (current_year in starting_year:ending_year){
  tac_table_insert.mod = tac_table_insert %>%
    gsub('@year', current_year, .)
  
  dbExecute(tac, tac_table_insert.mod)
}

```

# SECTION 4: Make new chip_enrl table

```{r}
#Compile table on TACC side

tac_make_chip_enrl1 = "drop table if exists medicaid.chip_enrl;"

tac_make_chip_enrl2 = "create table medicaid.chip_enrl as
select a.*, b.risk_group_cd,
	case when risk_group_cd in ('309', '310', '311') then 'CP'
	else 'C' end as CHIP_PER_FL
from medicaid.chip_uth a left join medicaid.chip_pren b on
a.year_fy = b.fy and a.client_nbr = b.client_nbr and a.elig_month = b.elig_month
distributed by (client_nbr);"

#refresh TACC connection bc it drops after 45 mins or so
tac = connect_to_tacc()

dbExecute(tac, tac_make_chip_enrl1)
dbExecute(tac, tac_make_chip_enrl2)


```


# SECTION 5: Count rows to make sure things worked right

## 5.1 Count SPC side
```{r}
#initialize DF to hold rowcounts
spc_rowcounts = data.frame(matrix(ncol=4, nrow=0))
colnames(spc_rowcounts) = c("year", "spc_uth_count", "spc_enrl_count")

#SQL queries to mod
spc_uth_count = "select count(*) from medicaid.dbo.CHIP_UTH_SFY20@yr_Final"
spc_enrl_count = "select count(*) from medicaid.dbo.CHIP_ENRL_FY@yr;"


#use 2-digit year
for (current_yr in starting_yr:ending_yr){
  
  spc_uth_count.mod = spc_uth_count %>%
    gsub('@yr', current_yr, .)
  
  spc_enrl_count.mod = spc_enrl_count %>%
    gsub('@yr', current_yr, .)
  
  current_uth_count = dbGetQuery(spc, spc_uth_count.mod)
  current_enrl_count = dbGetQuery(spc, spc_enrl_count.mod)
  
  current_row = c(year = current_yr + 2000,
                  spc_uth_count = current_uth_count[1,1],
                  spc_enrl_count = current_enrl_count[1,1])
  spc_rowcounts = rbind(spc_rowcounts, current_row)

}
#fix colnames at the end
colnames(spc_rowcounts) = c("year", "spc_uth_count", "spc_enrl_count")

```

## 5.1 Count TACC side
```{r}
#initialize DF to hold rowcounts

tac_uth_count = "select year_fy, count(*) as tac_uth_count from medicaid.chip_uth
where year_fy between @starting_year and @ending_year
group by year_fy order by year_fy;"

tac_enrl_count = "select year_fy, count(*) as tac_enrl_count from medicaid.chip_enrl
where year_fy between @starting_year and @ending_year
group by year_fy order by year_fy;"

#modify queries
tac_uth_count.mod = tac_uth_count %>%
  gsub("@starting_year", starting_year, .) %>%
  gsub("@ending_year", ending_year, .)

tac_enrl_count.mod = tac_enrl_count %>%
  gsub("@starting_year", starting_year, .) %>%
  gsub("@ending_year", ending_year, .)

#refresh TACC connection bc it drops after 45 mins or so
tac = connect_to_tacc()

#get counts
tac_uth_count_df = dbGetQuery(tac, tac_uth_count.mod)
tac_enrl_count_df = dbGetQuery(tac, tac_enrl_count.mod)

tac_rowcounts = tac_uth_count_df %>%
  left_join(tac_enrl_count_df, by = "year_fy")

#get counts of how many nulls there are
tac_enrl_null_count_df = dbGetQuery(tac,
  "select year_fy, count(*) as count from medicaid.chip_enrl
  where risk_group_cd is null and year_fy between 2016 and 2021
  group by year_fy order by year_fy;")

#fix colnames at the end
colnames(tac_rowcounts) = c("year", "tac_uth_count", "tac_enrl_count")

```

## 5.3 Mush tables together and see differences
```{r}

all_counts = spc_rowcounts %>%
  left_join(tac_rowcounts, by = "year") %>%
  mutate(uth_diff = spc_uth_count - tac_uth_count,
         enrl_diff = spc_enrl_count - tac_enrl_count,
         spc_uth_enrl_diff = spc_uth_count - spc_enrl_count)

```

# SECTION 6: Count rows, distinct member IDs and who exists where

```{r}


```

# SECTION 7: Output Summary

## 6.1 Make table legends
```{r}
legend1 = data.frame("column_name" = c("spc_uth_count",
                                       "spc_enrl_count",
                                       "tac_uth_count",
                                       "tac_enrl_count",
                                       "uth_diff",
                                       "enrl_diff",
                                       "spc_uth_enrl_diff"),
                     "description" = c("Count of rows per year in chip_uth tables on SPC server",
                                       "Count of rows per year in chip_enrl tables on SPC server",
                                       "Count of rows per year in chip_uth tables on TACC server",
                                       "Count of rows per year in chip_enrl tables on TACC server",
                                       "Difference between chip_uth tables between SPC and TACC servers",
                                       "Difference between chip_enrl tables between SPC and TACC servers",
                                       "Difference between chip uth and chip enrl tables within SPC server only"))

```

## 6.2 Output to spreadsheet
```{r}
wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "moving-chip-perinatal-raw-files-to-tacc.xlsx")

addWorksheet(wb, sheetName = "chip_pren counts")
addWorksheet(wb, sheetName = "server comparison")
addWorksheet(wb, sheetName = "chip_enrl counts")

#Sheet 1
current_sheet = 1
writeData(wb, sheet = current_sheet, "Count of rows in chip_pren by year", startCol=1, startRow=1)
writeData(wb, sheet = current_sheet, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = current_sheet, rowcounts, startCol=1, startRow=4)

setColWidths(wb, sheet = current_sheet, cols=1:ncol(rowcounts)+1, widths="auto")
setColWidths(wb, sheet = current_sheet, cols=1, widths=10)

#Sheet 2
current_sheet = 2
writeData(wb, sheet = current_sheet, "Count of rows in chip_uth and chip_enrl tables", startCol=1, startRow=1)
writeData(wb, sheet = current_sheet, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = current_sheet, all_counts, startCol=1, startRow=4)

setColWidths(wb, sheet = current_sheet, cols=1:ncol(all_counts)+1, widths="auto")
setColWidths(wb, sheet = current_sheet, cols=1:2, widths=c(16, 15))


#print legend
nextrow = nrow(all_counts) + 6
writeData(wb, sheet = current_sheet, "Note that the rowcount discrepancy is due to SPC side dropping rows if they do not have a corresponding member_id/elig_month combo in the chip_pren tables", startCol=1, startRow=nextrow+1)
writeData(wb, sheet = current_sheet, legend1, startCol=1, startRow=nextrow+1)

#Sheet 3
current_sheet = 3
writeData(wb, sheet = current_sheet, "Count of rows in chip_enrl (TACC side only) where risk_group_cd is null", startCol=1, startRow=1)
writeData(wb, sheet = current_sheet, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = current_sheet, tac_enrl_null_count_df, startCol=1, startRow=4)

setColWidths(wb, sheet = current_sheet, cols=1:ncol(tac_enrl_null_count_df)+1, widths="auto")
setColWidths(wb, sheet = current_sheet, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```


# SECTION 7: Clean up temp tables

```{r}
tacc_drop_table = "drop table if exists medicaid.chip_pren_fy@year;"

tac = connect_to_tacc()
for (current_year in starting_year:ending_year){
  tacc_drop_table.mod = tacc_drop_table %>%
    gsub('@year', current_year, .)
  
  dbExecute(tac, tacc_drop_table.mod)
}


```


# SECTION 99: Close connections and clean-up

```{r close-connections, eval=FALSE}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env, eval=FALSE}
# clears R environment
rm(list=ls())
```



