---
title: "dw-claims-details-qa"
author: "XRZ"
date: '2022-10-24'
output: html_document
---

#PURPOSE
This R markdown script counts distinct claims from SPC tables

# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(DBI, odbc, rstudioapi, keyring, openxlsx, tidyverse, beepr, tictoc)

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password


#Connect to Greenplum
tac <- dbConnect(odbc::odbc(),
	 dsn = "PostgreSQL30",
	 database = "uthealth",
	 UID = "xrzhang",
	 PWD = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(),
	 dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc")))
```

## 0.5 Set print to 25 rows
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)

```

# SECTION 1: Check for previous runs and define global variables

## 1.1 Does output already exist?
```{r}
#SPC server shouldn't have major changes year to year, so if output exists already
#use that

path = here("outputs", "spc-claims-counting.xlsx")

if (file.exists(path)) {

stop("Output already exists!")

}

print("No previous output exists, proceeding...")

```

## 1.2 Otherwise define global variables and proceed
```{r}
#define starting and ending year
starting_year = 2012
ending_year = 2021

#conver to 2-digit year
starting_yr = starting_year - 2000
ending_yr = ending_year - 2000

```

# SECTION 2: Count how many claims there are in each year

## 2.1 First make sure claims ICN and encounters DERV_ENC are distinct from each other

### 2.11 Declare base SQL query and initialize table
```{r}
#declare base queries to modify for getting the count of distinct ICNs each year

#counts it from details
sql1 = 'select count(distinct a.icn)
from medicaid.dbo.clm_proc_@yr a inner join medicaid.dbo.enc_proc_@yr b
on a.icn = b.DERV_ENC'

years = c(2013:ending_year)
clm_enc_overlaps = data.frame(cbind(years, matrix(ncol=1, nrow=ending_year-2013+1)))

colnames(clm_enc_overlaps) = c('Year', 'Count of clm/enc overlaps')

```

### 2.12 Run it for each year

```{r}

for (yr in 13:21){
  
  print(paste("Counting overlaps for", yr))
  
  sql1.mod = sql1 %>% gsub(pattern = '@yr', replacement = yr)
  
  num = dbGetQuery(spc, sql1.mod)
  
  clm_enc_overlaps[yr-12,2] = num[1,1]
  
  print(num[1,1])
  
}

```



## 2.2 Count claims and encounters for each 

### 2.22 Declare base SQL query for getting count of distinct ICNS each year from SPC server and initialize table
```{r}

#Counting from claims

clm_det = 'select count(distinct a.icn)
from medicaid.dbo.clm_proc_@yr a inner join medicaid.dbo.clm_detail_@yr b
on a.icn = b.icn;'

clm_head = 'select count(distinct a.icn)
from medicaid.dbo.clm_proc_@yr a inner join medicaid.dbo.clm_header_@yr b
on a.icn = b.icn;'

#Counting from encounters

enc_det = 'select count(distinct a.derv_enc)
from medicaid.dbo.enc_proc_@yr a inner join medicaid.dbo.enc_det_@yr b
on a.derv_enc = b.derv_enc;'

enc_head = 'select count(distinct a.derv_enc)
from medicaid.dbo.enc_proc_@yr a inner join medicaid.dbo.enc_header_@yr b
on a.derv_enc = b.derv_enc;'

years = c(starting_year:ending_year)
claim_counts = data.frame(cbind(years, matrix(ncol=4, nrow=ending_year-starting_year+1)))

colnames(claim_counts) = c('Year', 'CLM_DET', 'CLM_HEAD', 'ENC_DET', 'ENC_HEAD')

```

### 2.23 Run it for each year
```{r}

for (yr in starting_yr:ending_yr){
  
  print(paste0("Counting distinct claim numbers for 20", yr))
  
  if (yr == 12) { #if year = 2012 then count claims only
    
    clm_det.mod = clm_det %>% gsub(pattern = '@yr', replacement = yr)
    clm_head.mod = clm_head %>% gsub(pattern = '@yr', replacement = yr)
    
    clm_det_count = dbGetQuery(spc, clm_det.mod)
    clm_head_count = dbGetQuery(spc, clm_head.mod)
    
    enc_det_count = 0
    enc_head_count = 0
  
  } else {

    clm_det.mod = clm_det %>% gsub(pattern = '@yr', replacement = yr)
    clm_head.mod = clm_head %>% gsub(pattern = '@yr', replacement = yr)
    
    enc_det.mod = enc_det %>% gsub(pattern = '@yr', replacement = yr)
    enc_head.mod = enc_head %>% gsub(pattern = '@yr', replacement = yr)
    
    clm_det_count = dbGetQuery(spc, clm_det.mod)
    clm_head_count = dbGetQuery(spc, clm_head.mod)
    
    enc_det_count = dbGetQuery(spc, enc_det.mod)
    enc_head_count = dbGetQuery(spc, enc_head.mod)
  
  }
  
  #load it into dataframe
  claim_counts[yr-(starting_yr-1), 2] = clm_det_count
  claim_counts[yr-(starting_yr-1), 3] = clm_head_count
  claim_counts[yr-(starting_yr-1), 4] = enc_det_count
  claim_counts[yr-(starting_yr-1), 5] = enc_head_count
  
  #prints out to console so there's a record if things go south
  cat(paste(claim_counts[yr-(starting_yr-1),1],
            claim_counts[yr-(starting_yr-1),2],
            claim_counts[yr-(starting_yr-1),3],
            claim_counts[yr-(starting_yr-1),4],
            claim_counts[yr-(starting_yr-1),5], sep='\t'), '\n')
}

```

### 2.24 Count HTW claims
```{r}
#initialize dataframe
claim_counts_htw = data.frame(matrix(ncol=5, nrow=1))
colnames(claim_counts_htw) = c('Year', 'CLM_DET', 'CLM_HEAD', 'ENC_DET', 'ENC_HEAD')
claim_counts_htw[1,1] = 'HTW'
claim_counts_htw[1,4] = claim_counts_htw[1,5] = 0

#define queries
clm_det_htw = 'select count(distinct a.icn)
from medicaid.dbo.clm_proc_1819_htw a inner join medicaid.dbo.clm_detail_1819_htw b
on a.icn = b.icn;'

clm_head_htw = 'select count(distinct a.icn)
from medicaid.dbo.clm_proc_1819_htw a inner join medicaid.dbo.clm_header_1819_htw b
on a.icn = b.icn;'

#retrieve counts
claim_counts_htw[1, 2] = dbGetQuery(spc, clm_det_htw)
claim_counts_htw[1, 3] = dbGetQuery(spc, clm_head_htw)

```

## 2.3 Get the sum for each year
```{r}
claim_counts_sum = claim_counts %>%
  mutate_at(vars(Year), as.character) %>%
  rbind(., claim_counts_htw) %>%
  mutate(CLM_HEAD_EXCESS = CLM_HEAD - CLM_DET,
         CLM_DET_EXCESS = CLM_DET - CLM_HEAD,
         ENC_HEAD_EXCESS = ENC_HEAD - ENC_DET,
         ENC_DET_EXCESS = ENC_DET - ENC_HEAD,
         YR_TOTAL = pmin(CLM_HEAD, CLM_DET) + pmin(ENC_HEAD, ENC_DET)) %>%
  select(Year, CLM_HEAD, CLM_DET,
         ENC_HEAD, ENC_DET,
          CLM_HEAD_EXCESS, CLM_DET_EXCESS,
         ENC_HEAD_EXCESS, ENC_DET_EXCESS, YR_TOTAL)

```

# SECTION 3: Print it out so we won't have to do this again

## 3.1 Write to spreadsheet
```{r}
wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "spc-claims-counting.xlsx")

addWorksheet(wb, sheetName = "SPCDEDPWPVS1 claims counting")

writeData(wb, sheet = 1, "Count of distinct claims in SPCDEDPWPVS1", startCol=1, startRow=1)
writeData(wb, sheet = 1, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = 1, claim_counts_sum, startCol=1, startRow=4)

setColWidths(wb, sheet = 1, cols=1:ncol(claim_counts_sum)+1, widths="auto")
setColWidths(wb, sheet = 1, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```

#SECTION 99: Delete temp tables, Close connections, clear R environment

```{r close-connections, eval = FALSE}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env, eval = FALSE}
# clears R environment
rm(list=ls())
```
