---
title: "dw-claims-proc-spotcheck"
author: "XRZ"
date: '2022-11-30'
output: html_document
---

# PURPOSE
This R markdown script spot checks for the existence of proc codes in data_warehouse

# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password


#Connect to Greenplum
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(),
	 dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc")))
```

## 0.5 Set print to 25 rows
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)

```

# SECTION 1: Declare global variables
```{r}
#Define the starting and ending years for checking (4-digit year)
starting_year = 2012
ending_year = 2021

#Define how many rows to check - will check this many rows 
#from each of the clm_proc table and enc_proc table so double this number
#for rows checked per year (except for 2012)
rows_to_check = 10000

#Define how many sets of errors to print out per variable
records_to_print = 5

#convert to 2-digit year
starting_yr = starting_year - 2000
ending_yr = ending_year - 2000
```

# SECTION 2: Randomly select rows from SPC DX tables and uploads to TACC
## 2.1 Define base queries
```{r}
#set rows_to_sample as slightly higher than rows to check b/c of
#the funny way that tablesample works
rows_to_sample = as.integer(rows_to_check) * 1.2

#select random rows from a claims table
spc_sql1 = 'select top @rows_to_check ICN, PCN, PROC_ICD_QAL_1, PROC_ICD_CD_1,
	PROC_ICD_QAL_2, PROC_ICD_CD_2,
	PROC_ICD_QAL_3, PROC_ICD_CD_3,
	PROC_ICD_QAL_4, PROC_ICD_CD_4,
	PROC_ICD_QAL_5, PROC_ICD_CD_5,
	PROC_ICD_QAL_6, PROC_ICD_CD_6,
	PROC_ICD_QAL_7, PROC_ICD_CD_7,
	PROC_ICD_QAL_8, PROC_ICD_CD_8,
	PROC_ICD_QAL_9, PROC_ICD_CD_9,
	PROC_ICD_QAL_10, PROC_ICD_CD_10,
	PROC_ICD_QAL_11, PROC_ICD_CD_11,
	PROC_ICD_QAL_12, PROC_ICD_CD_12,
	PROC_ICD_QAL_13, PROC_ICD_CD_13,
	PROC_ICD_QAL_14, PROC_ICD_CD_14,
	PROC_ICD_QAL_15, PROC_ICD_CD_15,
	PROC_ICD_QAL_16, PROC_ICD_CD_16,
	PROC_ICD_QAL_17, PROC_ICD_CD_17,
	PROC_ICD_QAL_18, PROC_ICD_CD_18,
	PROC_ICD_QAL_19, PROC_ICD_CD_19,
	PROC_ICD_QAL_20, PROC_ICD_CD_20,
	PROC_ICD_QAL_21, PROC_ICD_CD_21,
	PROC_ICD_QAL_22, PROC_ICD_CD_22,
	PROC_ICD_QAL_23, PROC_ICD_CD_23,
	PROC_ICD_QAL_24, PROC_ICD_CD_24,
	PROC_ICD_QAL_25, PROC_ICD_CD_25
into work.dbo.xz_dwqa_temp1 
from medicaid.dbo.clm_proc_@yr
tablesample(@rows_to_sample rows)
where PROC_ICD_CD_1 != \'\' or PROC_ICD_CD_2 ! = \'\' or PROC_ICD_CD_3 != \'\';'

#join it to client nbr and DOS
spc_sql2 = 'select \'20@yr\' as fy, c.HDR_FRM_DOS as dos, a.*
into work.dbo.xz_dwqa_temp2
from work.dbo.xz_dwqa_temp1 a left join
	medicaid.dbo.clm_header_@yr c on a.icn = c.icn;'

spc_sql3 = 'select top @rows_to_check DERV_ENC, MEM_ID,
  PRIM_PROC_QAL, PRIM_PROC_CD,
	PROC_ICD_QAL_1, PROC_ICD_CD_1,
	PROC_ICD_QAL_2, PROC_ICD_CD_2,
	PROC_ICD_QAL_3, PROC_ICD_CD_3,
	PROC_ICD_QAL_4, PROC_ICD_CD_4,
	PROC_ICD_QAL_5, PROC_ICD_CD_5,
	PROC_ICD_QAL_6, PROC_ICD_CD_6,
	PROC_ICD_QAL_7, PROC_ICD_CD_7,
	PROC_ICD_QAL_8, PROC_ICD_CD_8,
	PROC_ICD_QAL_9, PROC_ICD_CD_9,
	PROC_ICD_QAL_10, PROC_ICD_CD_10,
	PROC_ICD_QAL_11, PROC_ICD_CD_11,
	PROC_ICD_QAL_12, PROC_ICD_CD_12,
	PROC_ICD_QAL_13, PROC_ICD_CD_13,
	PROC_ICD_QAL_14, PROC_ICD_CD_14,
	PROC_ICD_QAL_15, PROC_ICD_CD_15,
	PROC_ICD_QAL_16, PROC_ICD_CD_16,
	PROC_ICD_QAL_17, PROC_ICD_CD_17,
	PROC_ICD_QAL_18, PROC_ICD_CD_18,
	PROC_ICD_QAL_19, PROC_ICD_CD_19,
	PROC_ICD_QAL_20, PROC_ICD_CD_20,
	PROC_ICD_QAL_21, PROC_ICD_CD_21,
	PROC_ICD_QAL_22, PROC_ICD_CD_22,
	PROC_ICD_QAL_23, PROC_ICD_CD_23,
	PROC_ICD_QAL_24, PROC_ICD_CD_24
into work.dbo.xz_dwqa_temp3 
from medicaid.dbo.enc_proc_@yr
tablesample(@rows_to_sample rows)
where PROC_ICD_CD_1 != \'\' or PROC_ICD_CD_2 ! = \'\' or PRIM_PROC_CD != \'\';'

spc_sql4 = 'insert into work.dbo.xz_dwqa_temp2
select \'20@yr\' as fy, c.FRM_DOS as dos, a.*
from work.dbo.xz_dwqa_temp3 a left join
	medicaid.dbo.enc_header_@yr c on a.derv_enc = c.derv_enc;'

```

## 2.2 Send, year by year, random selections from dx tables
```{r}

dbGetQuery(tac, 'drop table if exists dev.xz_dwqa_temp1;')

for (yr in starting_yr:ending_yr){
  
  #clear tables
  dbGetQuery(spc, 'drop table if exists work.dbo.xz_dwqa_temp1;')
  dbGetQuery(spc, 'drop table if exists work.dbo.xz_dwqa_temp2;')
  dbGetQuery(spc, 'drop table if exists work.dbo.xz_dwqa_temp3;')
  
  if (yr == 12){
    print("Sampling records for 2012, the special year")
    
    #for 2012,
    #modify just the claims queries
    spc_sql1.mod = spc_sql1 %>% gsub('@rows_to_check', rows_to_check, .) %>%
      gsub('@rows_to_sample', rows_to_sample, .) %>%
      gsub('@yr', yr, .)
    spc_sql2.mod = spc_sql2 %>% gsub('@yr', yr, .)
    
    #and send queries
    tic("sample from claims")
    dbGetQuery(spc, spc_sql1.mod)
    dbGetQuery(spc, spc_sql2.mod)
    toc()
  } else {
    print(paste0("Sampling records for 20", yr))
    
    #for all other years
    #modify queries
    spc_sql1.mod = spc_sql1 %>% gsub('@rows_to_check', rows_to_check, .) %>%
      gsub('@rows_to_sample', rows_to_sample, .) %>%
      gsub('@yr', yr, .)
    spc_sql2.mod = spc_sql2 %>% gsub('@yr', yr, .)
    spc_sql3.mod = spc_sql3 %>% gsub('@rows_to_check', rows_to_check, .) %>%
      gsub('@rows_to_sample', rows_to_sample, .) %>%
      gsub('@yr', yr, .)
    spc_sql4.mod = spc_sql4 %>% gsub('@yr', yr, .)
    
    tic("sample from claims")
    dbGetQuery(spc, spc_sql1.mod)
    dbGetQuery(spc, spc_sql2.mod)
    toc()
    tic("sample from encounters")
    dbGetQuery(spc, spc_sql3.mod)
    dbGetQuery(spc, spc_sql4.mod)
    toc()
    
  }

  spc_selection = dbGetQuery(spc, 'select * from work.dbo.xz_dwqa_temp2;')
  #make all names lowercase bc GP gets case-sensitive
  names(spc_selection) = tolower(names(spc_selection))
  
  tic("Write to TACC")
  dbWriteTable(tac, SQL('dev.xz_dwqa_temp1'), spc_selection, append = T, overwrite = F)
  toc()
}

```

# SECTION 3: Looks for DX codes in data_warehouse.clm_dx

## 3.1 Declare base sql queries for modification
```{r}

tac_sql1 = 'select trim(icn) as icn, fy, trim(pcn) as pcn, trim(dos) as dos,
  	trim(proc_icd_qal_1) as icd, trim(proc_icd_cd_1) as proc
  into dev.xz_dwqa_temp2
  from dev.xz_dwqa_temp1
  where proc_icd_cd_1 is not null and trim(proc_icd_cd_1) != \'\'';

tac_sql2 = 'insert into dev.xz_dwqa_temp2
  select trim(icn) as icn, fy, trim(pcn) as pcn, trim(dos) as dos,
  	trim(proc_icd_qal_@num) as icd, trim(proc_icd_cd_@num) as proc
  from dev.xz_dwqa_temp1
  where proc_icd_cd_@num is not null and trim(proc_icd_cd_@num) != \'\'';

```

## 3.2 Linearize dx codes
```{r}
dbGetQuery(tac, 'drop table if exists dev.xz_dwqa_temp2;')
dbGetQuery(tac, tac_sql1)

for (i in 2:25) {
  print(paste0("Scraping proc_cd_", i))
  tac_sql2.mod = tac_sql2 %>% gsub('@num', i, .)
  dbGetQuery(tac, tac_sql2.mod)
}

```

## 3.3 Search for dx codes

```{sql, connection = tac}
drop table if exists dev.xz_dwqa_temp3;
```

```{sql, connection = tac}
select a.*, b.claim_id_src, b.fiscal_year, b.member_id_src, b.from_date_of_service, b.icd_version, b.proc_cd,
	case when b.claim_id_src is null then 1 else 0 end as claim_id_mismatch,
	case when b.fiscal_year is null then 1 
		when b.fiscal_year::text != a.fy then 1 else 0 end as fy_mismatch,
	case when b.member_id_src is null then 1 
		when b.member_id_src != a.pcn then 1 else 0 end as mem_id_mismatch,
	case when b.from_date_of_service is null then 1 
		when b.from_date_of_service::text != a.dos then 1 else 0 end as dos_mismatch,
	case when b.icd_version is null then 1
		when b.icd_version != a.icd then 1 else 0 end as icd_mismatch,
	case when b.proc_cd is null then 1
		when b.proc_cd != a.proc then 1 else 0 end as proc_mismatch
into dev.xz_dwqa_temp3
from dev.xz_dwqa_temp2 a left join data_warehouse.claim_icd_proc_1_prt_mdcd b on a.icn = b.claim_id_src and a.proc = b.proc_cd;

```

## 3.4 Get sum of mismatches
```{sql, connection = tac, output.var = sum_mismatches}

select fy, sum(claim_id_mismatch) as clam_id_mismatch, sum(fy_mismatch) as fy_mismatch, 
 sum(mem_id_mismatch) as mem_id_mismatch, sum(dos_mismatch) as dos_mismatch,
 sum(icd_mismatch) as icd_mismatch, sum(proc_mismatch) as proc_mismatch, count(*) as proc_cds_checked
from dev.xz_dwqa_temp3
group by fy
order by fy;

```

# SECTION 4: Outputs results

## 4.1 Assemble output table
```{r}

rows_sampled = c()

for (i in starting_yr:ending_yr){
  if (i == 12){ rows_sampled = append(rows_sampled, rows_to_check)
  } else { rows_sampled = append(rows_sampled, rows_to_check*2) }
}

output = sum_mismatches %>%
  cbind(rows_sampled)

```


## 4.2 Write to xlsx
```{r}
wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "dw-claim-proc-spotcheck.xlsx")

addWorksheet(wb, sheetName = "claim_proc spotcheck")

writeData(wb, sheet = 1, "Mismatches found in claim_icd_proc tables between SPC and data_warehouse", startCol=1, startRow=1)
writeData(wb, sheet = 1, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = 1, paste("Rows sampled per SPC table:", rows_to_check), startCol=1, startRow=3)

writeData(wb, sheet = 1, output, startCol=1, startRow=5)

setColWidths(wb, sheet = 1, cols=1:ncol(output)+1, widths="auto")
setColWidths(wb, sheet = 1, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```

#SECTION 99: Delete temp tables, Close connections, clear R environment

```{sql, connection = spc, eval = FALSE}
drop table if exists work.dbo.xz_dwqa_temp1;
drop table if exists work.dbo.xz_dwqa_temp2;
drop table if exists work.dbo.xz_dwqa_temp3;
```

```{sql, connection = tac, eval = FALSE}
drop table if exists dev.xz_dwqa_temp1;
drop table if exists dev.xz_dwqa_temp2;
drop table if exists dev.xz_dwqa_temp3;
```

```{r close-connections, eval = FALSE}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env, eval = FALSE}
# clears R environment
rm(list=ls())
```
