---
title: "raw-rowcounts"
author: "XRZ"
date: '2023-07-31'
output: html_document
---

#Purpose:
This R markdown script counts how many rows of data there are in the raw Medicaid 
data on SPC side and Greenplum side and compares them


# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password

# Function for connecting to TACC/Greenplum
# TACC kicks you out for inactivity so just call function before connections
connect_to_tacc <- function() {
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
}

```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(),
	 dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc", "connect_to_tacc")))
```

## 0.5 Declare root directory and set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation
here::i_am("01-raw-rowcounts.rmd")
```

# SECTION 1: Initialization

## 1.1 Define global variables
```{r}
#Define the starting and ending years for checking (4-digit year)
starting_year = 2016
ending_year = 2022

#convert to 2-digit year
starting_yr = starting_year - 2000
ending_yr = ending_year - 2000
```

## 1.2 Read in table names
```{r}
importfile = here("table_names.xlsx")

table_names = read.xlsx(importfile, "Sheet1")


```

## 1.3 Declare base queries
```{r}

spc_sql = "select count(*) from medicaid.dbo.@base_table; "


gp_sql = "select year_fy, '@base_table' as table, count(*)::int as gp from medicaid.@base_table group by 1 order by 1;"

```

## 1.4 Initialize DF for holding all information
```{r}

empty_df = data.frame(matrix(ncol=3, nrow=0))
empty_df = rbind(empty_df, c(0, "", 0))
spc_counts = empty_df
gp_counts = empty_df
colnames(spc_counts) = c("year_fy", "table", "spc")
colnames(gp_counts) = c("year_fy", "table", "gp")


```

# SECTION 2: Count rows

## 2.1 Count rows on SPC-side
```{r}

for (i in 1:nrow(table_names)){
  
  base_table = table_names[i,1]

  tic(paste("Count from", table_names[i,2]))
  
  #substitute in the table

  spc_sql.mod1 = spc_sql %>% gsub("@base_table", base_table, .)
  
  for (yr in starting_yr:ending_yr){
    #substitute in the year
    spc_sql.mod2 = spc_sql.mod1 %>% gsub('@YY', yr, .)
    
    #get count
    count = dbGetQuery(spc, spc_sql.mod2)
  
    #rbind it in
    spc_counts = rbind(spc_counts, c(2000+yr, table_names[i,2], count[1,1]))
    }
  
  toc()
  
}


```

## 2.2 Count rows on GP-side
```{r}

tac = connect_to_tacc()

for (i in 1:nrow(table_names)){
  
  base_table = table_names[i,2]

  tic(paste("Count from", table_names[i,2]))
  
  #substitute in the table

  gp_sql.mod = gp_sql %>% gsub("@base_table", base_table, .)
  
  #get count
  count = dbGetQuery(tac, gp_sql.mod)

  #rbind it in
  gp_counts = rbind(gp_counts, count)

  toc()
  
}


```
# SECTION 3: Merge data, find differences
```{r}
#spc_counts = spc_counts %>% distinct()

#make merged df
merged_counts = spc_counts %>%
  filter(year_fy != 0) %>%
  full_join(gp_counts, by=c("year_fy", "table")) %>%
  filter(year_fy >= starting_year, year_fy<=ending_year) %>%
  mutate (spc = as.integer(spc),
          gp = as.integer(gp)) %>%
  mutate(diff = spc - gp) %>%
  arrange(table, year_fy)

```


# SECTION 4: Outputs results

## 4.1 Write to xlsx
```{r eval=false}
output = merged_counts

wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "medicaid-raw-rowcounts.xlsx")

addWorksheet(wb, sheetName = "rowcounts")

writeData(wb, sheet = 1, "Raw rowcounts from SPC server and GP server", startCol=1, startRow=1)
writeData(wb, sheet = 1, paste("Run time:", Sys.time()), startCol=1, startRow=2)

writeData(wb, sheet = 1, output, startCol=1, startRow=4)

setColWidths(wb, sheet = 1, cols=1:ncol(output)+1, widths="auto")
setColWidths(wb, sheet = 1, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```

#SECTION 99: Delete temp tables, Close connections, clear R environment

```{sql, connection = spc, eval = FALSE}
drop table if exists work.dbo.xz_dwqa_temp1;
drop table if exists work.dbo.xz_dwqa_temp2;
drop table if exists work.dbo.xz_dwqa_temp3;
```

```{sql, connection = tac, eval = FALSE}
drop table if exists dev.xz_dwqa_temp1;
drop table if exists dev.xz_dwqa_temp2;
drop table if exists dev.xz_dwqa_temp3;
```

```{r close-connections, eval = FALSE}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env, eval = FALSE}
# clears R environment
rm(list=ls())
```
