---
title: "dwqa-truven-claim-diag-counts"
author: "XRZ"
date: '2023-01-10'
output: html_document
---


#Purpose:
This R markdown script examines the accuracy of conversions from raw source tables to
data_warehouse tables


# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

#packages I don't use anymore: rstudioapi

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password

# Function for connecting to TACC/Greenplum
# TACC kicks you out for inactivity so just call function before connections
connect_to_tacc <- function() {
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
}

```

## 0.3 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("connect_to_tacc")))
```

## 0.5 Set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation
here::i_am("05-claim-diag-counts.Rmd")
```

# SECTION 1: Check for existing counts from TRUVEN schema
```{r}
# First we're going to create the enrolid-msclmid combinations for the raw Truven tables
# Then save it to a file so we don't have to run it multiple times

# Check to see if raw counts for Truven exists - break if it does

path = here("outputs", "truven-raw-counts.xlsx")

if (!file.exists(path)) {

 print("Missing counts from Truven schema! Go back and run 02-truven-schema-counts.Rmd")

} else {
  
  truv_counts_in = read.xlsx(path, sheet = 1, startRow = 4,
                             colNames = TRUE, rowNames = FALSE)
  
  truv_concat_in = read.xlsx(path, sheet = 2, startRow = 4,
                             colNames = TRUE, rowNames = FALSE)
}

```

## 1.1 Base SQL queries for modification
```{r}

starting_year = 2011
ending_year = 2012

# sql query to initialize table to store counts in
dw_sql1 = " create table dev.xz_dwqa_temp (
  	year int,
  	concat text
  ) distributed by (concat);"

#sql query to write unique combinations of enrolid || msclmid to a temp table
dw_sql2 = "create table dev.xz_dwqa_temp2 as
  select year, member_id_src || claim_id_src as concat from dw_staging.claim_diag
  where year = @year
  distributed by (concat);"

#sql query to count unique enrolid || msclmids
dw_sql3 = "insert into dev.xz_dwqa_temp
  select year, count(distinct concat) from dev.xz_dwqa_temp2
  group by year;"

```

## 1.2 Get counts of distinct claim ids
```{r}
#this takes about 2-3-ish mins per year
# ~40 s to make the temp table of enrolid || msclmids
# ~1.2 min to count distinct

tac = connect_to_tacc()

# initialize temp table to hold counts
dbExecute(tac, "drop table if exists dev.xz_dwqa_temp;") 
dbExecute(tac, dw_sql1)

# for (i in starting_year:ending_year){
for (i in 2013:2021){
  
  # we count in pieces bc otherwise the query takes too long
  dbExecute(tac, "drop table if exists dev.xz_dwqa_temp2;")
  
  # modify sql query to grab only the enrolid || msclmids for current year
  dw_sql2.mod = dw_sql2 %>% gsub("@year", i, .)
  
  # make temp table with enrolid || msclmids
  tic(paste("Making temp table for", i))
  dbExecute(tac, dw_sql2.mod)
  toc()
  
  # count distinct enrolid || msclmids for current year
  # and inserting into a different temp table
  tic(paste("Counting distinct enrolid||msclmids for", i))
  dbExecute(tac, dw_sql3)
  toc()
}

# get results from server
dw_concat_counts = dbGetQuery(tac, "select * from dev.xz_dwqa_temp;")
  
```

# SECTION 2: Make table

## 2.1 Squish Truven raw counts table into 1 column
```{r}

#first need to make everything an int bc apparently it imported as chr
truv_concat_in$truv_concat_ccaeo = as.integer(truv_concat_in$truv_concat_ccaeo)
truv_concat_in$truv_concat_ccaes = as.integer(truv_concat_in$truv_concat_ccaes)
truv_concat_in$truv_concat_mdcro = as.integer(truv_concat_in$truv_concat_mdcro)
truv_concat_in$truv_concat_mdcrs = as.integer(truv_concat_in$truv_concat_mdcrs)

# rearrange dw table so that each column is a table_id_src
truv_squish = truv_concat_in %>%
  mutate(truv_concat = truv_concat_ccaes + truv_concat_ccaeo +
           truv_concat_mdcrs + truv_concat_mdcro) %>%
  select(year, truv_concat)


```

## 2.2 Make table for distinct enrolid-clmid combos
```{r}
# combine truven raw counts with dw counts

all_concat_counts = dw_concat_counts %>%
  left_join(truv_squish, by = "year") %>%
  mutate(dw_concat = as.integer(concat)) %>% # simultaneously convert to int and rename
  mutate(difference = truv_concat - dw_concat) %>%
  select(year, dw_concat, truv_concat, difference)

```


# SECTION 3: Output to spreadsheet
```{r}


###################

# this section not yet modified

###################


wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "truven-claim-diag-counting.xlsx")

addWorksheet(wb, sheetName="distinct-claim-ids")
addWorksheet(wb, sheetName="distinct-enrolid-clmid-combos")

#sheet 1
current_sheet = 1; current_df = all_counts
writeData(wb, sheet = current_sheet,
          "Count of distinct claim IDs (msclmid) in data_warehouse and Truven schema on TACC server",
          startCol=1, startRow=1)
writeData(wb, sheet = current_sheet, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = current_sheet, current_df, startCol=1, startRow=4)
nextrow = nrow(current_df) + 6

writeData(wb, sheet=current_sheet, "Difference between Truven schema and data_warehouse (Truven - DW):", startCol=1, startRow = nextrow)
writeData(wb, sheet = current_sheet, difference, startCol=1, startRow=nextrow+1)

nextrow = nextrow + nrow(difference) + 4

writeData(wb, sheet=current_sheet,
          "Note: The difference in claim id count in 2021 is because some claims have enrolids that exist in the s and o tables that do not map to any enrolid in the a or t tables", startCol=1, startRow = nextrow)
writeData(wb, sheet=current_sheet,
          "The reason that this discrepancy ONLY exists in 2021 is likely because for 2020 and earlier, Will created entries in dim_uth_member_id to accomodate them", startCol=1, startRow = nextrow+1)

setColWidths(wb, sheet = current_sheet, cols=1:ncol(current_df)+1, widths="auto")
setColWidths(wb, sheet = current_sheet, cols=1, widths=10)

#sheet 2
current_sheet = 2; current_df = all_concat_counts
writeData(wb, sheet = current_sheet,
          "Count of distinct enrolid-clmid combinations in data_warehouse and Truven schema on TACC server",
          startCol=1, startRow=1)
writeData(wb, sheet = current_sheet, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = current_sheet, current_df, startCol=1, startRow=4)
nextrow = nrow(current_df) + 6

writeData(wb, sheet=current_sheet, "Difference between Truven schema and data_warehouse (Truven - DW):", startCol=1, startRow = nextrow)
writeData(wb, sheet = current_sheet, difference_concat, startCol=1, startRow=nextrow+1)

nextrow = nextrow + nrow(difference) + 4

writeData(wb, sheet=current_sheet,
          "Note: The difference in enrolid || claim id count in 2021 is because some claims have enrolids that exist in the s and o tables that do not map to any enrolid in the a or t tables", startCol=1, startRow = nextrow)
writeData(wb, sheet=current_sheet,
          "The reason that this discrepancy ONLY exists in 2021 is likely because for 2020 and earlier, Will created entries in dim_uth_member_id to accomodate them", startCol=1, startRow = nextrow+1)

setColWidths(wb, sheet = current_sheet, cols=1:ncol(current_df)+1, widths="auto")
setColWidths(wb, sheet = current_sheet, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```

