---
title: "dwqa-truven-schema-counts"
author: "XRZ"
date: '2023-01-09'
output: html_document
---

#Purpose:
This R markdown script counts unique msclmids and unique msclmid-enrolid
combinations in truven schema

# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password

# Function for connecting to TACC/Greenplum
# TACC kicks you out for inactivity so just call function before connections
connect_to_tacc <- function() {
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
}

```

## 0.3 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("connect_to_tacc")))
```

## 0.5 Set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation

#Make sure that the here() function is pointing to the parent folder for this file
here::i_am("02-truven-schema-counts.Rmd")

```
# SECTION 1: Get counts of rows and distinct ENROLIDs

## 1.1 Base SQL queries for modification
```{r}
#this is the list of tables to look in and count
list_of_tables = c("ccaes", "ccaeo", "mdcrs", "mdcro")

#this is the lsit of tables to look in and count for icd_proc
list_of_tables2 = c("ccae", "mdcr")

#sql query to count distinct msclmids
truv_sql1 = "select year, '@table'::text as table, count(distinct msclmid) as count from truven.@table
where enrolid is not null
group by year
order by year;"

#sql query to write unique combinations of enrolid || msclmid to a temp table
truv_sql2 = "create table dev.xz_dwqa_temp as
select year, '@table'::text as table_src, enrolid::text || msclmid::text as concat
from truven.@table
where enrolid is not null
distributed by (concat);"

#sql query to count unique enrolid || msclmids
truv_sql3 = "select year, table_src, count(distinct concat) from dev.xz_dwqa_temp
group by year, table_src
order by table_src, year;"

# sql query to write unique combinations of enrolid || msclmid to a temp table
# ONLY for when dx columns are not all null
truv_sql4 = "create table dev.xz_dwqa_temp as
select year, '@table'::text as table_src, enrolid, enrolid::text || msclmid::text as concat
from truven.@table
where enrolid is not null
and (pdx is not null or
  dx1 is not null or
  dx2 is not null or
  dx3 is not null)
distributed by (concat);"

# count ONLY distinct enrolid || msclmids that map to an enrolid that exists
# in the enrollment table (match on enrolid and year)
truv_sql5 = "select a.year, a.table_src, count(distinct a.concat)
from dev.xz_dwqa_temp a inner join truven.ccaea b 
on a.enrolid = b.enrolid and a.year = b.year
group by a.year, a.table_src
order by a.year;"

#get enrolid || msclmids from 's' tables where pproc is not null
truv_sql6 = "create table dev.xz_dwqa_temp as
select year, '@table'::text as table_src, enrolid::text || msclmid::text as concat
from truven.@tables
where enrolid is not null
and pproc is not null
distributed by (concat);"

#append enrolid || msclmids from 'f' tables where proc1-6 is not null
truv_sql7 = "insert into dev.xz_dwqa_temp
select year, '@table'::text as table_src, enrolid::text || msclmid::text as concat
from truven.@tablef
where (proc1 is not null or
  proc2 is not null or
  proc3 is not null or
  proc4 is not null or
  proc5 is not null or
  proc6 is not null);"

truv_sql8 = "create table dev.xz_dwqa_temp as
select year, '@tabled'::text as table_src,
  enrolid::text || ndcnum::text || svcdate::text as concat
from truven.@tabled
where enrolid is not null
distributed by (concat);"

```


## 1.2 Get counts of distinct msclmids from truven schema
```{r}
tac = connect_to_tacc()

for (i in 1:4){
  
  current_table = list_of_tables[i]
  truv_sql1.mod = truv_sql1 %>% gsub("@table", current_table, .)
  
  tic(paste("Count distinct claim IDs from truven -", current_table))
  
  current_results = dbGetQuery(tac, truv_sql1.mod)
  
  if (i == 1) {
    truv_counts = current_results
  } else {
   truv_counts = rbind(truv_counts, current_results)
  }
  
  toc()

}
  
```

## 1.3: Count distinct enrolid-msclmid combinations
```{r}

tac = connect_to_tacc()

for (i in 1:4){
  
  current_table = list_of_tables[i]
  
  truv_sql2.mod = truv_sql2 %>% gsub("@table", current_table, .)
  
  tic(paste("Creating table of enrolid || msclmid from truven -", current_table))
  
  dbExecute(tac, "drop table if exists dev.xz_dwqa_temp;")
  dbExecute(tac, truv_sql2.mod)
  
  toc()
  
  tic(paste("Counting distinct enrolid || msclmid from truven -", current_table))
  
  current_results = dbGetQuery(tac, truv_sql3)
  
  toc()
  
  if (i == 1) {
    truv_concat_counts = current_results
  } else {
   truv_concat_counts = rbind(truv_concat_counts, current_results)
  }
  

}


```

## 1.4: Count distinct enrolid-msclmid combinations (has dx only, enrolid exists in 'a' tables)
```{r, eval = FALSE}

tac = connect_to_tacc()

for (i in 1:4){
  
  current_table = list_of_tables[i]
  
  truv_sql4.mod = truv_sql4 %>% gsub("@table", current_table, .)
  
  #'o' tables don't have pdx column so take that stipulation out
  if (i == 2 || i == 4){
  truv_sql4.mod = truv_sql4.mod %>% gsub("pdx is not null or", "", .)
  }
  
  tic(paste("Creating table of enrolid || msclmid (dx only) from truven -", current_table))
  
  dbExecute(tac, "drop table if exists dev.xz_dwqa_temp;")
  dbExecute(tac, truv_sql4.mod)
  
  toc()
  
  tic(paste("Counting distinct enrolid || msclmid (dx only) from truven -", current_table))
  
  # check for enrolid in mdcra for mdcro and mdcrs
  if (i == 3 || i == 4){
  truv_sql5.mod = truv_sql5 %>% gsub("ccaea", "mdcra", .)
  } else {
    truv_sql5.mod = truv_sql5
  }
  
  current_results = dbGetQuery(tac, truv_sql5.mod)
  
  toc()
  
  if (i == 1) {
    truv_dx_counts = current_results
  } else {
   truv_dx_counts = rbind(truv_dx_counts, current_results)
  }
  

}


```
## 1.5: Count distinct enrolid-msclmid combinations (has dx only, enrolid does not have to exist in 'a' tables)
```{r}

tac = connect_to_tacc()

for (i in 1:4){
  
  current_table = list_of_tables[i]
  
  truv_sql4.mod = truv_sql4 %>% gsub("@table", current_table, .)
  
  #'o' tables don't have pdx column so take that stipulation out
  if (i == 2 || i == 4){
  truv_sql4.mod = truv_sql4.mod %>% gsub("pdx is not null or", "", .)
  }
  
  tic(paste("Creating table of enrolid || msclmid (dx only) from truven -", current_table))
  
  dbExecute(tac, "drop table if exists dev.xz_dwqa_temp;")
  dbExecute(tac, truv_sql4.mod)
  
  toc()
  
  tic(paste("Counting distinct enrolid || msclmid (dx only) from truven -", current_table))
  
  current_results = dbGetQuery(tac, truv_sql3)
  
  toc()
  
  if (i == 1) {
    truv_dx_counts2 = current_results
  } else {
   truv_dx_counts2 = rbind(truv_dx_counts2, current_results)
  }
  

}


```

## 1.6: Count distinct enrolid-msclmid combinations with procs
```{r}

# this code is a bit different from other pieces, we're counting from
# the 's' and 'f' tables

tac = connect_to_tacc()

for (i in 1:2){
  
  if (i == 1) current_table = 'ccae' else current_table = 'mdcr'
  
  truv_sql6.mod = truv_sql6 %>% gsub("@table", current_table, .)
  truv_sql7.mod = truv_sql7 %>% gsub("@table", current_table, .)
  
  tic(paste0("Creating table of enrolid || msclmid (proc) from truven - ", 
            current_table, 's'))
  
  dbExecute(tac, "drop table if exists dev.xz_dwqa_temp;")
  dbExecute(tac, truv_sql6.mod)
  
  toc()
  
  tic(paste0("Appending enrolid || msclmid (proc) from truven - ", 
            current_table, 'f'))
  
  dbExecute(tac, truv_sql7.mod)
  
  toc()
  
  tic(paste("Counting distinct enrolid || msclmid (proc) from truven -", current_table, "tables"))
  
  current_results = dbGetQuery(tac, truv_sql3)
  
  toc()
  
  if (i == 1) {
    truv_proc_counts = current_results
  } else {
   truv_proc_counts = rbind(truv_proc_counts, current_results)
  }
  

}


```
## 1.6: Count distinct rx_ids from 'd' tables
```{r}

tac = connect_to_tacc()

for (i in 1:2){
  
  current_table = list_of_tables2[i]
  
  truv_sql8.mod = truv_sql8 %>% gsub("@table", current_table, .)
  
  tic(paste0("Creating table of rxids from truven - ", 
            current_table, 'd'))
  
  dbExecute(tac, "drop table if exists dev.xz_dwqa_temp;")
  dbExecute(tac, truv_sql8.mod)
  
  toc()
  
  tic(paste0("Counting distinct rxids from truven - ", current_table, "d"))
  
  current_results = dbGetQuery(tac, truv_sql3)
  
  toc()
  
  if (i == 1) {
    truv_rx_counts = current_results
  } else {
   truv_rx_counts = rbind(truv_rx_counts, current_results)
  }
  

}


```

## 1.8: Code blurb bc I did this bass-ackward
```{r, eval=FALSE}
# this code chunk intentially set to eval = FALSE
# it's here bc I added in counting for dx and proc later on and wanted to
# be able to make the spreadsheet w/o doing all the counting again

# read in data from prior runs

rm(truv_counts_in)

if (!file.exists(path)) {

 print("Missing counts from Truven schema! Go back and run 02-truven-schema-counts.Rmd")

} else {
  
  truv_counts_in = read.xlsx(path, sheet = 1, startRow = 4,
                             colNames = TRUE, rowNames = FALSE)
  
  truv_concat_in = read.xlsx(path, sheet = 2, startRow = 4,
                             colNames = TRUE, rowNames = FALSE)
}

#truv_counts_in = as.data.frame(truv_counts_in)
#truv_counts_in$truv_ccaes = as.integer(truv_counts_in$truv_ccaes)
#truv_counts_in$truv_ccaeo = as.integer(truv_counts_in$truv_ccaeo)
#truv_counts_in$truv_mdcrs = as.integer(truv_counts_in$truv_mdcrs)
#truv_counts_in$truv_mdcro = as.integer(truv_counts_in$truv_mdcro)

truv_clmid_tbl = truv_counts_in

truv_concat_tbl = truv_concat_in

typeof(truv_clmid_tbl)
typeof(truv_counts_in)
typeof(truv_dx_tbl)

```



# SECTION 2: Output to spreadsheet

## 2.1 Make tables
```{r}

# rearrange counts of distinct msclmids

for (i in 1:4){
  
  current_table = list_of_tables[i]
  newcolname = paste0("truv_", current_table)
  
  current = truv_counts %>%
    filter(table == current_table) %>%
    rename(!!newcolname := count) %>%
    select(-table)

    if (i==1){
      truv_clmid_tbl = current
    } else {
    truv_clmid_tbl = truv_clmid_tbl %>%
    left_join(current, by = "year")
    }
}

# rearrange counts of distinct enrolid || msclmid combos

for (i in 1:4){
  
  current_table = list_of_tables[i]
  newcolname = paste0("truv_concat_", current_table)
  
  current = truv_concat_counts %>%
    filter(table_src == current_table) %>%
    rename(!!newcolname := count) %>%
    select(-table_src)

    if (i==1){
      truv_concat_tbl = current
    } else {
    truv_concat_tbl = truv_concat_tbl %>%
    left_join(current, by = "year")
    }
}


# rearrange counts of distinct enrolid || msclmid combos for rows with dx only
# (enrolid in 'a' tables)

for (i in 1:4){
  
  current_table = list_of_tables[i]
  newcolname = paste0("truv_dx_", current_table)
  
  current = truv_dx_counts %>%
    filter(table_src == current_table) %>%
    rename(!!newcolname := count) %>%
    select(-table_src)

    if (i==1){
      truv_dx_tbl = current
    } else {
    truv_dx_tbl = truv_dx_tbl %>%
    left_join(current, by = "year")
    }
}

# rearrange counts of distinct enrolid || msclmid combos for rows with dx only
# (enrolid not necessarily in 'a' tables)

for (i in 1:4){
  
  current_table = list_of_tables[i]
  newcolname = paste0("truv_dx_", current_table)
  
  current = truv_dx_counts2 %>%
    filter(table_src == current_table) %>%
    rename(!!newcolname := count) %>%
    select(-table_src)

    if (i==1){
      truv_dx_tbl2 = current
    } else {
    truv_dx_tbl2 = truv_dx_tbl2 %>%
    left_join(current, by = "year")
    }
}

# rearrange counts of distinct enrolid || msclmid combos for rows with proc only
# from 's' and 'f' tables

for (i in 1:2){
  
  current_table = list_of_tables2[i]
  newcolname = paste0("truv_proc_", current_table)
  
  current = truv_proc_counts %>%
    filter(table_src == current_table) %>%
    rename(!!newcolname := count) %>%
    select(-table_src)

    if (i==1){
      truv_proc_tbl = current
    } else {
    truv_proc_tbl = truv_proc_tbl %>%
    left_join(current, by = "year")
    }
}

# rearrange counts of rx_ids from 'd' tables
for (i in 1:2){
  
  current_table = paste0(list_of_tables2[i], 'd')
  newcolname = paste0("truv_rx_", current_table)
  
  current = truv_rx_counts %>%
    filter(table_src == current_table) %>%
    rename(!!newcolname := count) %>%
    select(-table_src)

    if (i==1){
      truv_rx_tbl = current
    } else {
    truv_rx_tbl = truv_rx_tbl %>%
    left_join(current, by = "year")
    }
}


```

## 2.2 Output to spreadsheet
```{r}

# idk why setcoldwidths introduced some coerce to NA errors

wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "02-truven-raw-counts.xlsx")

addWorksheet(wb, sheetName="msclmids")
addWorksheet(wb, sheetName="enrolid || msclmid combos")
addWorksheet(wb, sheetName="dx - enrolids in a")
addWorksheet(wb, sheetName="dx - all enrolids")
addWorksheet(wb, sheetName="proc")
addWorksheet(wb, sheetName="rx")

# sheet 1: distinct msclmids
current_sheet = 1; current_df = truv_clmid_tbl
writeData(wb, sheet = current_sheet,
          "Count of distinct claim IDs (msclmid) in Truven schema on TACC server",
          startCol=1, startRow=1)
writeData(wb, sheet = current_sheet, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = current_sheet, current_df, startCol=1, startRow=4)
nextrow = nrow(current_df) + 6

# setColWidths(wb, sheet = 1, cols=1:ncol(truv_clmid_tbl)+1, widths="auto")
# setColWidths(wb, sheet = 1, cols=1, widths=10)

# sheet 2: distinct enrolid || msclmids
current_sheet = 2; current_df = truv_concat_tbl
writeData(wb, sheet = current_sheet,
          "Count of distinct enrolid-msclmid combinations in Truven schema on TACC server",
          startCol=1, startRow=1)
writeData(wb, sheet = current_sheet, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = current_sheet, current_df, startCol=1, startRow=4)
nextrow = nrow(current_df) + 6

#setColWidths(wb, sheet = 2, cols=1:ncol(current_df)+1, widths="auto")
#setColWidths(wb, sheet = 2, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

# sheet 3: distinct enrolid || msclmids ONLY for rows with dx
current_sheet = 3; current_df = truv_dx_tbl
writeData(wb, sheet = current_sheet,
          "Count of distinct enrolid-msclmid combinations in Truven schema on TACC server (rows with dx codes only, enrolid has to exist in 'a' tables)",
          startCol=1, startRow=1)
writeData(wb, sheet = current_sheet, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = current_sheet, current_df, startCol=1, startRow=4)
nextrow = nrow(current_df) + 6

#setColWidths(wb, sheet = 3, cols=1:ncol(current_df)+1, widths="auto")
#setColWidths(wb, sheet = 3, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

# sheet 4: distinct enrolid || msclmids ONLY for rows with dx, enrolid does not have to exist in 'a' tables
current_sheet = 4; current_df = truv_dx_tbl2
writeData(wb, sheet = current_sheet,
          "Count of distinct enrolid-msclmid combinations in Truven schema on TACC server (rows with dx codes only, enrolid DOES NOT have to exist in 'a' tables)",
          startCol=1, startRow=1)
writeData(wb, sheet = current_sheet, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = current_sheet, current_df, startCol=1, startRow=4)
nextrow = nrow(current_df) + 6

# setColWidths(wb, sheet = 4, cols=1:ncol(current_df)+1, widths="auto")
# setColWidths(wb, sheet = 4, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

# sheet 5: distinct enrolid || msclmids ONLY for rows with proc codes, enrolid does not have to exist in 'a' tables
current_sheet = 5; current_df = truv_proc_tbl
writeData(wb, sheet = current_sheet,
          "Count of distinct enrolid-msclmid combinations in Truven schema on TACC server (rows with proc codes only, counting from 's' and 'f' tables)",
          startCol=1, startRow=1)
writeData(wb, sheet = current_sheet, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = current_sheet, current_df, startCol=1, startRow=4)
nextrow = nrow(current_df) + 6

writeData(wb, sheet = current_sheet,
          "Note that ccaes/ccaef tables were combined, then count distinct (otherwise there are too many overlaps)", startCol = 1, startRow=nextrow)

# setColWidths(wb, sheet = 5, cols=1:ncol(current_df)+1, widths="auto")
# setColWidths(wb, sheet = 5, cols=1, widths=10)

# sheet 6: distinct enrolid || ndcnum || svcdate from 'd' tables, where enrolid is not null
current_sheet = 6; current_df = truv_rx_tbl
writeData(wb, sheet = current_sheet,
          "Count of distinct enrolid || ndcnum || svcdate from 'd' tables, where enrolid is not null in Truven schema on TACC server",
          startCol=1, startRow=1)
writeData(wb, sheet = current_sheet, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = current_sheet, current_df, startCol=1, startRow=4)
nextrow = nrow(current_df) + 6

# setColWidths(wb, sheet = 5, cols=1:ncol(current_df)+1, widths="auto")
# setColWidths(wb, sheet = 5, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)


```




