---
title: "moving-chip-perinatal-raw-files-to-tacc"
author: "XRZ"
date: '2023-03-13'
output: html_document
---

#Purpose:
This R markdown script uploads a new LU_CONTRACTS table to reference_tables.medicaid_lu_contracts

Source table: new updated table MasterPlan.xlsx from Lisa Kalkanis at HHS
Target table: Greenplum: reference_tables.medicaid_lu_contracts

# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)


```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password

# Function for connecting to TACC/Greenplum
# TACC kicks you out for inactivity so just call function before connections
connect_to_tacc <- function() {
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
}

```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment, eval=FALSE}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc", "connect_to_tacc")))
```

## 0.5 Declare root directory and set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation
here::i_am("update-mcd-lu_contract-ref-table.rmd")

```

# SECTION 1: Upload to TACC

```{r}
# Read files in
filename = 'resources/MasterPlan_03-29-23.xlsx'
importfile = here(filename)

lu_contract = read.xlsx(importfile, "Sheet1")

# make names lowercase
names(lu_contract) = tolower(names(lu_contract))

# trims whitespace
lu_contract[] <- lapply(lu_contract, trimws)

# uploads to GP
tac = connect_to_tacc()
dbWriteTable(tac, SQL("reference_tables.medicaid_lu_contract_upd"), lu_contract, overwrite = TRUE)

```

----------------------------------
After uploading table, there's a SQL file
----------------------------------

# SECTION 99: Close connections and clean-up

```{r close-connections, eval=FALSE}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env, eval=FALSE}
# clears R environment
rm(list=ls())
```



