---
title: "dw-rx-counting-pt2"
author: "XRZ"
date: '2022-11-22'
output: html_document
---

#PURPOSE
This R markdown script counts distinct rx from TACC tables

# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

#packages I don't use anymore: rstudioapi

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password


#Connect to Greenplum
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(),
	 dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc")))
```

## 0.5 Set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation

```

# SECTION 1: Read in runs from previous code

## 1.1 Read in output if it exists
```{r}
#SPC server shouldn't have major changes year to year, so if output exists already
#use that

path = here("outputs", "spc-rx-counting.xlsx")

if (file.exists(path)) {

spc_counts = read.xlsx(path, sheet=1, startRow = 4)

} else {
  stop("Output is missing! Go back and run the previous code file!")
}

```

## 1.2 Define global variables
```{r}
#define starting and ending year
starting_year = 2012
ending_year = 2021

#conver to 2-digit year
starting_yr = starting_year - 2000
ending_yr = ending_year - 2000

```

# SECTION 2: Count distinct rx_ids from data_warehouse schema on TACC

```{sql, connection = tac, output.var = dw_counts}

--gets rx claim ids by year
select fiscal_year::text, table_id_src, count(distinct rx_claim_id_src) as src_id, count(distinct uth_rx_claim_id) as uth_id
from data_warehouse.pharmacy_claims_1_prt_mdcd
group by fiscal_year, table_id_src
order by table_id_src, fiscal_year; 

```

# SECTION 3: Compile it all into a table and compare
```{r}
dw_chip = dw_counts %>%
  filter(table_id_src == 'chip_rx') %>%
  select(fiscal_year, src_id) %>%
  rename(fy = fiscal_year, dw_chip=src_id)

dw_ffs = dw_counts %>%
  filter(table_id_src == 'ffs_rx') %>%
  select(fiscal_year, src_id) %>%
  rename(fy = fiscal_year, dw_ffs=src_id)

dw_mco = dw_counts %>%
  filter(table_id_src == 'mco_rx') %>%
  select(fiscal_year, src_id) %>%
  rename(fy = fiscal_year, dw_mco=src_id)

dw_htw_only = dw_counts %>%
  filter(table_id_src == 'htw_ffs_rx')

dw_htw = sum(dw_htw_only$src_id)

all_counts = spc_counts %>%
  rename(spc_chip = chip, spc_ffs = ffs, spc_mco = mco, spc_sum = sum) %>%
  left_join(dw_chip, by = "fy") %>%
  left_join(dw_ffs, by = "fy") %>%
  left_join(dw_mco, by = "fy") %>%
  mutate(dw_sum = dw_chip + dw_ffs + dw_mco) %>%
  arrange(fy)

#insert HTW number
all_counts[which(all_counts$fy=='HTW'), 9] = dw_htw

all_counts = all_counts %>%
  mutate(chip_diff = spc_chip - dw_chip) %>%
  mutate(ffs_diff = spc_ffs - dw_ffs) %>%
  mutate(mco_diff = spc_mco - dw_mco) %>%
  mutate(sum_diff = spc_sum - dw_sum) %>%
  arrange(fy)

percent_diff = all_counts %>%
  mutate(chip_bad_records = chip_diff/dw_chip) %>%
  mutate(ffs_bad_records = ffs_diff/dw_ffs) %>%
  mutate(mco_bad_records = mco_diff/dw_mco) %>%
  mutate(sum_bad_records = sum_diff/dw_sum) %>%
  select(fy, chip_bad_records, ffs_bad_records, mco_bad_records, sum_bad_records)

```

# SECTION 4: Output to spreadsheet

```{r}
output = all_counts
output2 = percent_diff

wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "dw-rx-counting.xlsx")

addWorksheet(wb, sheetName = "rx_id spotcheck")

writeData(wb, sheet = 1, "Count of distinct PCN || NDC || FILL_DT combinations between SPC server and data_warehouse", startCol=1, startRow=1)
writeData(wb, sheet = 1, paste("Run time:", Sys.time()), startCol=1, startRow=2)

writeData(wb, sheet = 1, output, startCol=1, startRow=4)

nextrow = nrow(output) + 7
writeData(wb, sheet = 1, "Note: The missing RX claims are due to PCNs that do not exist in the enrollment tables", startCol=1, startRow=nextrow)
writeData(wb, sheet = 1, "The proportion of claims with PCNs that do not match is:", startCol=1, startRow=nextrow+1)

writeData(wb, sheet = 1, output2, startCol=1, startRow=nextrow+3)

setColWidths(wb, sheet = 1, cols=1:ncol(output)+1, widths="auto")
setColWidths(wb, sheet = 1, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```

```


#SECTION 99: Delete temp tables, Close connections, clear R environment

```{r close-connections, eval = FALSE}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env, eval = FALSE}
# clears R environment
rm(list=ls())
```
