---
title: "dw-qa-test"
author: "XRZ"
date: '2022-12-2'
output: html_document
---


# Purpose
This script compares the results for a sample query from Medicaid raw data on
SPC servers to the data_warehouse.

Sample query used: 5 Agencies - Wellness - Obesity

# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

#packages I don't use anymore: rstudioapi

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password


#Connect to Greenplum
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(),
	 dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc")))
```

## 0.5 Set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation

```

#SECTION 1: Define global variables

## 1.1 Global variables
```{r}
#define the years that we're trying to get data for [LAST 2 DIGITS, OMIT THE 20--]
start_year = 16
end_year = 21

#define where the template spreadsheet is
template_path = here("rows.csv")

```

## 1.2 Global functions
```{r function-definitions}
prep_df = function (df){
  
  #Prep vectors of column names for renaming
  colnames.old = colnames(df)
  colnames.new = c('FY', 'MCO', 'sex', 'agegrp', 'denominator', 'numerator')
  
  #Rename columns
  df = df %>%
    rename_at(vars(all_of(colnames.old)), ~colnames.new)
  
  #Calculate prevalence, trim white space from MCO column
  df = df %>% mutate(prevalence = numerator/denominator) %>%
        mutate(MCO = str_trim(MCO))
  
  #also add a blanks row for matching purposes
  df[nrow(df)+1,] <- NA
  
  return(df)
}

append_by_year = function(df, joint_df, yr){
  #subset by year
  df = df %>%
    filter(FY == (2000 + yr))

  #Join to row number
  df = rows %>%
    left_join(df, by = c('MCO', 'sex', 'agegrp'), keep=FALSE) %>%
    arrange(Row_num) %>%
    select(Row_num, MCO, sex, agegrp, denominator, numerator, prevalence)

  #Calcualtes total
  df[7, "denominator"] = sum(df$denominator[1:6], na.rm=TRUE)
  df[7, "numerator"] = sum(df$numerator[1:6], na.rm=TRUE)
  df[7, "prevalence"] = df[7, "numerator"]/df[7, "denominator"]
  
  #Prep column names for renaming
  colnames.old = colnames(df)
  colnames.new = c('Row_num', 'MCO', 'sex', 'agegrp',
                   paste0('denominator', yr),
                   paste0('numerator', yr),
                   paste0('prevalence', yr))
  
  #Renames columns with year
  df = df %>%
    rename_at(vars(all_of(colnames.old)), ~colnames.new)
  
  #Joins it to the final table
  joint_df = joint_df %>%
    left_join(df, by = c('Row_num', 'MCO', 'sex', 'agegrp'), keep=FALSE)
  
  return(joint_df)
  
}
```

# SECTION 2: Read in data from databases

# 2.1 Read in data from SPC
```{r}
#read just the obesity data in

for (yr in start_year:end_year){
  
  #define the query
  # sql1 = paste0("select * from work.dbo.xz_5a_mcd_depression_finaltab_", yr)
  # sql2 = paste0("select * from work.dbo.xz_5a_mcd_annual_finaltab_", yr)
  # sql3 = paste0("select * from work.dbo.xz_5a_mcd_flu_finaltab_", yr)
  # sql4 = paste0("select * from work.dbo.xz_5a_mcd_smoking_finaltab_", yr)
  # sql5 = paste0("select * from work.dbo.xz_5a_mcd_smoking_finaltab2_", yr)
  sql6 = paste0("select * from work.dbo.xz_5a_mcd_obesity_finaltab_", yr)
  sql7 = paste0("select * from work.dbo.xz_5a_mcd_obesity_finaltab2_", yr)
  
  #Initialize dfs for the first year
  if (yr == start_year){
    # adult_depression_raw = dbGetQuery(spc, sql1)
    # annual_exam_raw = dbGetQuery(spc, sql2)
    # flu_raw = dbGetQuery(spc, sql3)
    # smoking_raw = dbGetQuery(spc, sql4)
    # smoking_cessation_raw = dbGetQuery(spc, sql5)
    obesity_raw = dbGetQuery(spc, sql6)
    obesity_counseling_raw = dbGetQuery(spc, sql7)
  } else { #for all subsequent years, append data
    # adult_depression_raw = rbind(adult_depression_raw, dbGetQuery(spc, sql1))
    # annual_exam_raw = rbind(annual_exam_raw, dbGetQuery(spc, sql2))
    # flu_raw = rbind(flu_raw, dbGetQuery(spc, sql3))
    # smoking_raw = rbind(smoking_raw, dbGetQuery(spc, sql4))
    # smoking_cessation_raw = rbind(smoking_cessation_raw, dbGetQuery(spc, sql5))
    obesity_raw = rbind(obesity_raw, dbGetQuery(spc, sql6))
    obesity_counseling_raw = rbind(obesity_counseling_raw, dbGetQuery(spc, sql7))
  }
  
}

#and also read in HPV - should already have all years appended
# hpv_raw = dbGetQuery(spc, "select * from work.dbo.xz_5a_mcd_hpv_finaltab")

```

#2.2 Read in data from TACC

```{sql, connection = tac, output.var = tacc_obesity_raw}
select * from dev.xz_5a_mcd_obesity_finaltab
order by fy;
```

```{sql, connection = tac, output.var = tacc_obesity_counseling_raw}
select * from dev.xz_5a_mcd_obesity_finaltab2
order by fy;
```


```{r intialize_dfs, message=FALSE}
#Import rows so we can match Will's spreadsheets
rows = read.csv(template_path, header = TRUE)

#Age_cat imports as int, cast to character
#rows$agegrp = as.character(rows$agegrp)

results = rows[,-1] #don't need first column for matching

```

```{r prep-dfs, message=FALSE}

# Prep data from SQL server for joining to final results tables

# adult_depression_prep = prep_df(adult_depression_raw)
# annual_exam_prep = prep_df(annual_exam_raw)
# flu_prep = prep_df(flu_raw)
# hpv_prep = prep_df(hpv_raw)
# smoking_prep = prep_df(smoking_raw)
# smoking_cessation_prep = prep_df(smoking_cessation_raw)
obesity_prep = prep_df(obesity_raw)
obesity_counseling_prep = prep_df(obesity_counseling_raw)
tacc_obesity_prep = prep_df(tacc_obesity_raw)
tacc_obesity_counseling_prep = prep_df(tacc_obesity_counseling_raw)

```

```{r makesheets, message=FALSE}

#Make some empty sheets to put results into
# adult_depression_results = results
# annual_exam_results = results
# flu_results = results
# hpv_results = results
# smoking_results = results
# smoking_cessation_results = results
obesity_results = results
obesity_counseling_results = results
tacc_obesity_results = results
tacc_obesity_counseling_results = results

#Make the actual sheets

for (yr in start_year:end_year){
  # adult_depression_results = append_by_year(adult_depression_prep, adult_depression_results, yr)
  # annual_exam_results = append_by_year(annual_exam_prep, annual_exam_results, yr)
  # flu_results = append_by_year(flu_prep, flu_results, yr)
  # hpv_results = append_by_year(hpv_prep, hpv_results, yr)
  # smoking_results = append_by_year(smoking_prep, smoking_results, yr)
  # smoking_cessation_results = append_by_year(smoking_cessation_prep, smoking_cessation_results, yr)
  obesity_results = append_by_year(obesity_prep, obesity_results, yr)
  obesity_counseling_results = append_by_year(obesity_counseling_prep, obesity_counseling_results, yr)
  tacc_obesity_results = append_by_year(tacc_obesity_prep, tacc_obesity_results, yr)
  tacc_obesity_counseling_results = append_by_year(tacc_obesity_counseling_prep, tacc_obesity_counseling_results, yr)
}
```

```{r xlsx-prep}

#define styles
blank = createStyle(fgFill = NULL, border = NULL)
black = createStyle(fgFill = "#000000", border="TopBottomLeftRight", borderColour = "#000000", borderStyle="thin")
color1 = createStyle(fgFill = "lavenderblush", border="TopBottomLeftRight",  borderColour = "#000000", borderStyle="thin")
color2 = createStyle(fgFill = "lightgoldenrodyellow", border="TopBottomLeftRight",  borderColour = "#000000", borderStyle="thin")
color3 = createStyle(fgFill = "#E7FFE7", border="TopBottomLeftRight",  borderColour = "#000000", borderStyle="thin")
color4 = createStyle(fgFill = "lavender", border="TopBottomLeftRight",  borderColour = "#000000", borderStyle="thin")
boldcenter = createStyle(halign = "center", textDecoration = c("BOLD"))
bold = createStyle(textDecoration = c("BOLD"))
males = createStyle(fgFill = "dodgerblue2", border=NULL, textDecoration = c("BOLD"), fontColour="white")
females = createStyle(fgFill = "deeppink", border=NULL, textDecoration = c("BOLD"), fontColour="white")

# define how many years we're writing data for
num_years = end_year-start_year+1
colsend = (num_years+1)*3

#make mini-df of header names
tinycolnames = data.frame(matrix(c("Denominator", "Numerator", "Prevalence"), nrow=1))

#define which rows are black bars
black_rows = c(11, 19, 27, 35, 43, 51, 59, 69, 77, 85, 93, 101, 109,
              119, 127, 135, 143, 151, 159)

#define which rows are clear
clear_rows = c(60, 110)


```

```{r output-to-xlsx, message=FALSE}
#this chunk takes all the dataframes and outputs them into a workbook

# create blank workbook
wb = createWorkbook()

# Add data to workbook
# addWorksheet(wb, sheetName = "Adult Depression")      #1
# addWorksheet(wb, sheetName = "Annual Exam")           #2
# addWorksheet(wb, sheetName = "Influenza Vaccination") #3
# addWorksheet(wb, sheetName = "HPV Vaccination")       #4
# addWorksheet(wb, sheetName = "Smoking Prevalence")    #5
# addWorksheet(wb, sheetName = "Smoking Cessation")     #6
addWorksheet(wb, sheetName = "Obesity Prevalence SPC")    #7
addWorksheet(wb, sheetName = "Weight Counseling SPC")     #8
addWorksheet(wb, sheetName = "Obesity Prevalence TACC")    #7
addWorksheet(wb, sheetName = "Weight Counseling TACC")     #8


# writeData(wb, sheet = 1, x = adult_depression_results[,-1], startCol=1, startRow=2)
# writeData(wb, sheet = 2, x = annual_exam_results[,-1], startCol=1, startRow=2)
# writeData(wb, sheet = 3, x = flu_results[,-1], startCol=1, startRow=2)
# writeData(wb, sheet = 4, x = hpv_results[,-1], startCol=1, startRow=2)
# writeData(wb, sheet = 5, x = smoking_results[,-1], startCol=1, startRow=2)
# writeData(wb, sheet = 6, x = smoking_cessation_results[,-1], startCol=1, startRow=2)
writeData(wb, sheet = 1, x = obesity_results[,-1], startCol=1, startRow=2)
writeData(wb, sheet = 2, x = obesity_counseling_results[,-1], startCol=1, startRow=2)
writeData(wb, sheet = 3, x = tacc_obesity_results[,-1], startCol=1, startRow=2)
writeData(wb, sheet = 4, x = tacc_obesity_counseling_results[,-1], startCol=1, startRow=2)

#style it up all nice and pretty-like
for (j in 1:4){
  for (i in 1:num_years)
  {
    #define which columns each year section lives + assigns a color
    cellstart = ((i-1)*3 + 4)
    cellend = ((i-1)*3 + 6)
    style_num = if (i%%4==0) {4} else {i%%4}
    current_style = get(paste0("color", style_num))
    
    #Write what fiscal year it is
    writeData(wb, sheet = j, x = paste("FY", start_year+i-1),
              startCol = cellstart, startRow = 1)
    
    #Write column headers: denominator, numerator, prevalence
    writeData(wb, sheet = j, x = tinycolnames,
              startCol = cellstart, startRow = 2, colNames=FALSE)
  
    #merge fiscal year cells
    mergeCells(wb, sheet = j, cols = cellstart:cellend, rows = 1)
    
    #Add style: Fiscal year cells
    addStyle(wb, sheet = j, style = current_style, cols = cellstart:cellend, rows = 1)
    addStyle(wb, sheet = j, style = boldcenter, cols = cellstart:cellend, rows = 1, stack=TRUE)
    
    #Add style: colors each triplet of columns
    addStyle(wb, sheet = j, style = current_style, cols = cellstart:cellend, gridExpand=TRUE, rows = 2:158)

  }
  
  #Makes the horizontal black bars
  addStyle(wb, sheet = j, style = black, cols = 1:colsend, gridExpand=TRUE, rows = black_rows)
  
  #Makes two rows clear
  addStyle(wb, sheet = j, style = blank, cols = 1:colsend, gridExpand=TRUE, rows = clear_rows)
  
  #Makes male and female rows
  writeData(wb, sheet = j, x = "Males", startCol = 1, startRow = 61)
  writeData(wb, sheet = j, x = "Females", startCol = 1, startRow = 111)
  addStyle(wb, sheet = j, style = males, cols = 1:colsend, gridExpand=TRUE, rows =61)
  addStyle(wb, sheet = j, style = females, cols = 1:colsend, gridExpand=TRUE, rows =111)
  
  #Makes columns 1-3 bold
  addStyle(wb, sheet = j, style = bold, cols = 1:3, rows = 1:158, gridExpand=TRUE, stack=TRUE)
  
  #Makes row 2 bold
  addStyle(wb, sheet = j, style = bold, cols = 1:colsend, rows = 2, gridExpand=TRUE, stack=TRUE)
  
  #set column widths to auto
  setColWidths(wb, sheet = j, widths="auto", cols=1:colsend)
  
  #freezes panes
  freezePane(wb, sheet = j, firstActiveRow=3)
}

file_path = here("outputs", "dwqa_sample_query.xlsx")

saveWorkbook(wb, file=file_path, overwrite=TRUE)

```

```{r clean-up-after-yourself}
# This chunk will create a query to wipe all tables - does not actually do the wiping

wipe_query = dbGetQuery(spc, "select \'DROP TABLE IF EXISTS WORK.DBO.\' + TABLE_NAME + \';\'
from information_schema.tables where table_name like 'xz_5a_mcd_%'")

nrow(wipe_query)

wipe_all_tables = ""
for (i in 1:nrow(wipe_query)){
  wipe_all_tables = paste(wipe_all_tables, wipe_query[i,])
}
```


```{r clean-up-after-yourself}
# THIS CHUNK WILL WIPE ALL YOUR TABLES FROM THE SQL SERVER

# DO. NOT. RUN. THIS. CHUNK. UNTIL. AFTER. YOU. ARE. COMPLETELY. SURE. YOU. ARE. DONE


# DID YOU CHECK YOUR TABLES


# ARE YOU SURE


# CHECK AGAIN


# THERE ARE NO TAKE-BACKSIES


# OK YOUR FUNERAL


dbGetQuery(spc, wipe_all_tables)

```

```{r close-connections}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env}
# clears R environment
rm(list=ls())
```



