---
title: "dw-enrl-vs-jeffs-agg-enrl"
author: "XRZ"
date: '2022-12-5'
output: html_document
---


# Purpose
Compare Jeff's agg enrl tables to dw agg enrl table (FY yearly only)

# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

#packages I don't use anymore: rstudioapi

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password


#Connect to Greenplum
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(), dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc")))
```

## 0.5 Set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation

```

# SECTION 1: Define global variables
```{r}

starting_yr = 13
ending_yr = 21

dx = 'F32'

proc = '96127'

ndc = '4580208801'

```

# SECTION 2: Define base queries for modification


```{r}

spc_sql1 = 'select \'20@yr\' as fy, icn, \'clm\' as src_table
  into work.dbo.xz_temp1
  from medicaid.dbo.clm_dx_@yr where
  PRIM_DX_CD like \'@dx%\' or
  DX_CD_1 like \'@dx%\' or
  DX_CD_2 like \'@dx%\' or
  DX_CD_3 like \'@dx%\' or
  DX_CD_4 like \'@dx%\' or
  DX_CD_5 like \'@dx%\' or
  DX_CD_6 like \'@dx%\' or
  DX_CD_7 like \'@dx%\' or
  DX_CD_8 like \'@dx%\' or
  DX_CD_9 like \'@dx%\' or
  DX_CD_10 like \'@dx%\' or
  DX_CD_11 like \'@dx%\' or
  DX_CD_12 like \'@dx%\' or
  DX_CD_13 like \'@dx%\' or
  DX_CD_14 like \'@dx%\' or
  DX_CD_15 like \'@dx%\' or
  DX_CD_16 like \'@dx%\' or
  DX_CD_17 like \'@dx%\' or
  DX_CD_18 like \'@dx%\' or
  DX_CD_19 like \'@dx%\' or
  DX_CD_20 like \'@dx%\' or
  DX_CD_21 like \'@dx%\' or
  DX_CD_22 like \'@dx%\' or
  DX_CD_23 like \'@dx%\' or
  DX_CD_24 like \'@dx%\' or
  DX_CD_25 like \'@dx%\';
  --315240
  
  --enc
  
  select \'20@yr\' as fy, derv_enc, \'enc\' as src_table
  into work.dbo.xz_temp2
  from medicaid.dbo.enc_dx_@yr where
  PRIM_DX_CD like \'@dx%\' or
  DX_CD_1 like \'@dx%\' or
  DX_CD_2 like \'@dx%\' or
  DX_CD_3 like \'@dx%\' or
  DX_CD_4 like \'@dx%\' or
  DX_CD_5 like \'@dx%\' or
  DX_CD_6 like \'@dx%\' or
  DX_CD_7 like \'@dx%\' or
  DX_CD_8 like \'@dx%\' or
  DX_CD_9 like \'@dx%\' or
  DX_CD_10 like \'@dx%\' or
  DX_CD_11 like \'@dx%\' or
  DX_CD_12 like \'@dx%\' or
  DX_CD_13 like \'@dx%\' or
  DX_CD_14 like \'@dx%\' or
  DX_CD_15 like \'@dx%\' or
  DX_CD_16 like \'@dx%\' or
  DX_CD_17 like \'@dx%\' or
  DX_CD_18 like \'@dx%\' or
  DX_CD_19 like \'@dx%\' or
  DX_CD_20 like \'@dx%\' or
  DX_CD_21 like \'@dx%\' or
  DX_CD_22 like \'@dx%\' or
  DX_CD_23 like \'@dx%\' or
  DX_CD_24 like \'@dx%\';'


spc_sql2 = 'select a.fy, a.icn, b.pcn, a.src_table
  into work.dbo.xz_temp3
  from work.dbo.xz_temp1 a inner join medicaid.dbo.clm_proc_21 b
  on a.icn = b.icn
  where b.pcn is not null and trim(b.pcn) != \'\';
  
  insert into work.dbo.xz_temp3
  select a.fy, a.icn, b.MEM_ID as pcn, a.src_table
  from work.dbo.xz_temp2 a inner join medicaid.dbo.enc_proc_21 b
  on a.icn = b.DERV_ENC
  where b.MEM_ID is not null and trim(b.MEM_ID) != \'\';'

spc_sql3 = 'select count(*) as rows, count(distinct icn) as distinct_icn,
  count(distinct pcn) as distinct_pcn
  from work.dbo.xz_temp3;'

tac_sql1 = 'select fiscal_year as fy, claim_id_src as icn, member_id_src as pcn
  into dev.xz_temp1
  from data_warehouse.claim_diag_1_prt_mdcd
  where diag_cd like \'@dx%\' and
  fiscal_year = 20@yr;'

tac_sql2 = 'select count(*) as rows, count(distinct icn) as distinct_icn,
  count(distinct pcn) as distinct_pcn
  from dev.xz_temp1;'


```




drop table if exists work.dbo.xz_temp1;
drop table if exists work.dbo.xz_temp2;
drop table if exists work.dbo.xz_temp3;

drop table if exists dev.xz_temp1;

select fiscal_year as fy, claim_id_src as icn, member_id_src as pcn
into dev.xz_temp1
from data_warehouse.claim_diag_1_prt_mdcd
where diag_cd like 'F32%' and
fiscal_year = 2021;

select count(*) as rows, count(distinct icn) as distinct_icn,
  count(distinct pcn) as distinct_pcn
  from dev.xz_temp1;





```{r close-connections}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env}
# clears R environment
rm(list=ls())
```



