---
title: "dw-enrl-vs-jeffs-agg-enrl"
author: "XRZ"
date: '2022-12-5'
output: html_document
---


# Purpose
Compare Jeff's agg enrl tables to dw agg enrl table (FY yearly only)

# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

#packages I don't use anymore: rstudioapi

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password


#Connect to Greenplum
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(), dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc")))
```

## 0.5 Set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation

```

# SECTION 1: Global definitions

## 1.1 Define global variables
```{r}

starting_year_global = 2012
ending_year_global = 2021

dx9 = '296'
dx10 = 'F32'
# 296 is icd 9 (Episodic mood disorders)
# F32 is icd 10 (mild depressive episode)

proc10 = '10E0XZZ' #delivery (birth)
proc9 = '03995' #hemodialysis

ndc = '00065853302' # cipro

cpt = '99213' #patient office visit

```

## 1.2 Define base SQL queries for modification

```{r}

spc_sql1 = 'select \'20@yr\' as fy, icn, \'clm\' as src_table
  into work.dbo.xz_temp1
  from medicaid.dbo.clm_dx_@yr where
  PRIM_DX_CD like \'@dx%\' or
  DX_CD_1 like \'@dx%\' or
  DX_CD_2 like \'@dx%\' or
  DX_CD_3 like \'@dx%\' or
  DX_CD_4 like \'@dx%\' or
  DX_CD_5 like \'@dx%\' or
  DX_CD_6 like \'@dx%\' or
  DX_CD_7 like \'@dx%\' or
  DX_CD_8 like \'@dx%\' or
  DX_CD_9 like \'@dx%\' or
  DX_CD_10 like \'@dx%\' or
  DX_CD_11 like \'@dx%\' or
  DX_CD_12 like \'@dx%\' or
  DX_CD_13 like \'@dx%\' or
  DX_CD_14 like \'@dx%\' or
  DX_CD_15 like \'@dx%\' or
  DX_CD_16 like \'@dx%\' or
  DX_CD_17 like \'@dx%\' or
  DX_CD_18 like \'@dx%\' or
  DX_CD_19 like \'@dx%\' or
  DX_CD_20 like \'@dx%\' or
  DX_CD_21 like \'@dx%\' or
  DX_CD_22 like \'@dx%\' or
  DX_CD_23 like \'@dx%\' or
  DX_CD_24 like \'@dx%\' or
  DX_CD_25 like \'@dx%\';
  --315240
  
  --enc
  
  select \'20@yr\' as fy, derv_enc as icn, \'enc\' as src_table
  into work.dbo.xz_temp2
  from medicaid.dbo.enc_dx_@yr where
  PRIM_DX_CD like \'@dx%\' or
  DX_CD_1 like \'@dx%\' or
  DX_CD_2 like \'@dx%\' or
  DX_CD_3 like \'@dx%\' or
  DX_CD_4 like \'@dx%\' or
  DX_CD_5 like \'@dx%\' or
  DX_CD_6 like \'@dx%\' or
  DX_CD_7 like \'@dx%\' or
  DX_CD_8 like \'@dx%\' or
  DX_CD_9 like \'@dx%\' or
  DX_CD_10 like \'@dx%\' or
  DX_CD_11 like \'@dx%\' or
  DX_CD_12 like \'@dx%\' or
  DX_CD_13 like \'@dx%\' or
  DX_CD_14 like \'@dx%\' or
  DX_CD_15 like \'@dx%\' or
  DX_CD_16 like \'@dx%\' or
  DX_CD_17 like \'@dx%\' or
  DX_CD_18 like \'@dx%\' or
  DX_CD_19 like \'@dx%\' or
  DX_CD_20 like \'@dx%\' or
  DX_CD_21 like \'@dx%\' or
  DX_CD_22 like \'@dx%\' or
  DX_CD_23 like \'@dx%\' or
  DX_CD_24 like \'@dx%\';'

spc_htw1 = 'select \'2018\' as fy, icn, \'htw\' as src_table
  into work.dbo.xz_temp_htw
  from medicaid.dbo.CLM_DX_1819_HTW where
  PRIM_DX_CD like \'@dx%\' or
  DX_CD_1 like \'@dx%\' or
  DX_CD_2 like \'@dx%\' or
  DX_CD_3 like \'@dx%\' or
  DX_CD_4 like \'@dx%\' or
  DX_CD_5 like \'@dx%\' or
  DX_CD_6 like \'@dx%\' or
  DX_CD_7 like \'@dx%\' or
  DX_CD_8 like \'@dx%\' or
  DX_CD_9 like \'@dx%\' or
  DX_CD_10 like \'@dx%\' or
  DX_CD_11 like \'@dx%\' or
  DX_CD_12 like \'@dx%\' or
  DX_CD_13 like \'@dx%\' or
  DX_CD_14 like \'@dx%\' or
  DX_CD_15 like \'@dx%\' or
  DX_CD_16 like \'@dx%\' or
  DX_CD_17 like \'@dx%\' or
  DX_CD_18 like \'@dx%\' or
  DX_CD_19 like \'@dx%\' or
  DX_CD_20 like \'@dx%\' or
  DX_CD_21 like \'@dx%\' or
  DX_CD_22 like \'@dx%\' or
  DX_CD_23 like \'@dx%\' or
  DX_CD_24 like \'@dx%\' or
  DX_CD_25 like \'@dx%\';'


spc_sql2 = 'select a.fy, a.icn, b.pcn, a.src_table
  into work.dbo.xz_temp3
  from work.dbo.xz_temp1 a inner join medicaid.dbo.clm_proc_@yr b
  on a.icn = b.icn
  where b.pcn is not null and trim(b.pcn) != \'\';
  
  insert into work.dbo.xz_temp3
  select a.fy, a.icn, b.MEM_ID as pcn, a.src_table
  from work.dbo.xz_temp2 a inner join medicaid.dbo.enc_proc_@yr b
  on a.icn = b.DERV_ENC
  where b.MEM_ID is not null and trim(b.MEM_ID) != \'\';'

spc_htw2 = 'insert into work.dbo.xz_temp3
  select a.fy, a.icn, b.pcn, a.src_table
  from work.dbo.xz_temp_htw a inner join medicaid.dbo.CLM_PROC_1819_HTW b
  on a.icn = b.icn
  where b.pcn is not null and trim(b.pcn) != \'\';'

spc_sql3 = 'select fy, count(*) as rows, count(distinct icn) as distinct_icn,
  count(distinct pcn) as distinct_pcn
  from work.dbo.xz_temp3
  group by fy;'

tac_sql1 = 'select fiscal_year as fy, claim_id_src as icn, member_id_src as pcn
  into dev.xz_temp1
  from data_warehouse.claim_diag_1_prt_mdcd
  where diag_cd like \'@dx%\'
  and fiscal_year between @starting_year and @ending_year;'

tac_sql2 = 'select fy, count(*) as rows, count(distinct icn) as distinct_icn,
  count(distinct pcn) as distinct_pcn
  from dev.xz_temp1
  group by fy
  order by fy;'

```

# SECTION 2: Check dx codes
## 2.1 ICD-9 modify and send queries
```{r}
#define the dx code and years for ICD-9
dx = dx9

ending_year = if (ending_year_global > 2018) { 2018 } else { ending_year_global }
starting_year = if (starting_year_global < ending_year) { starting_year_global
  } else { ending_year}

starting_yr = starting_year - 2000
ending_yr = ending_year - 2000

#initialize df for holding spc results
spc_results = data.frame(matrix(ncol=4, nrow=0))
colnames(spc_results) = c('fy', 'rows', 'distinct_icn', 'distinct_pcn')

#get counts for 
for (yr in starting_yr:ending_yr) {
  print(paste0("Getting icd-9 dx counts from SPC for fy 20", yr))
  
  spc_sql1.mod = spc_sql1 %>% gsub('@yr', yr, .) %>% gsub('@dx', dx, .)
  spc_sql2.mod = spc_sql2 %>% gsub('@yr', yr, .) %>% gsub('@dx', dx, .)
  
  dbExecute(spc, 'drop table if exists work.dbo.xz_temp1;')
  dbExecute(spc, 'drop table if exists work.dbo.xz_temp2;')
  dbExecute(spc, 'drop table if exists work.dbo.xz_temp3;')
  dbGetQuery(spc, spc_sql1.mod) #looks for dx codes and creates temp1, temp2
  dbGetQuery(spc, spc_sql2.mod) #joins in pcns and inserts into temp3
  
  
  if (yr==18) #for 2018, also look in HTW table
  {
    print("Now looking in HTW for 2018")
    spc_htw1.mod = spc_htw1 %>% gsub('@dx', dx, .)
    dbGetQuery(spc, 'drop table if exists work.dbo.xz_temp_htw;')
    dbGetQuery(spc, spc_htw1.mod) #looks for dx codes and creates temp_htw
    dbGetQuery(spc, spc_htw2) #joins in pcns, inserts into temp3
  }
  
  spc_results = rbind(spc_results, dbGetQuery(spc, spc_sql3)) #counts
}


tac_sql1.mod = tac_sql1 %>% gsub('@dx', dx, .) %>%
  gsub('@starting_year', starting_year, .) %>%
  gsub('@ending_year', ending_year, .)
dbGetQuery(tac, 'drop table if exists dev.xz_temp1;')
dbGetQuery(tac, tac_sql1.mod)
tac_results = dbGetQuery(tac, tac_sql2)


```
## 2.2 ICD 9 make results table
```{r}
#rename columns
colnames(spc_results) = c('fy', 'spc_rows', 'spc_distinct_icn', 'spc_distinct_pcn')
colnames(tac_results) = c('fy', 'dw_rows', 'dw_distinct_icn', 'dw_distinct_pcn')

#coerce spc_results year to int so we can join
spc_results$fy = as.integer(spc_results$fy)

dx_results_icd9 = spc_results %>%
  left_join(tac_results, by = "fy") %>%
  mutate(rows_diff = spc_rows - dw_rows,
         icn_diff = spc_distinct_icn - dw_distinct_icn,
         pcn_diff = spc_distinct_pcn - dw_distinct_pcn)

```

## 2.3 ICD-10 modify and send queries
```{r}
#define the dx code and years for ICD-9
dx = dx10

# starting_year = if (starting_year_global < 2014) { 2014 } else { starting_year_global }
# ending_year = if (ending_year_global > starting_year) { ending_year_global
#   } else { starting_year}

starting_year = starting_year_global
ending_year = ending_year_global

starting_yr = starting_year - 2000
ending_yr = ending_year - 2000

#initialize df for holding spc results
spc_results = data.frame(matrix(ncol=4, nrow=0))
colnames(spc_results) = c('fy', 'rows', 'distinct_icn', 'distinct_pcn')

#get counts for 
for (yr in starting_yr:ending_yr) {
  print(paste0("Getting icd-10 dx counts from SPC for fy 20", yr))
  
  spc_sql1.mod = spc_sql1 %>% gsub('@yr', yr, .) %>% gsub('@dx', dx, .)
  spc_sql2.mod = spc_sql2 %>% gsub('@yr', yr, .) %>% gsub('@dx', dx, .)
  
  dbExecute(spc, 'drop table if exists work.dbo.xz_temp1;')
  dbExecute(spc, 'drop table if exists work.dbo.xz_temp2;')
  dbExecute(spc, 'drop table if exists work.dbo.xz_temp3;')
  dbGetQuery(spc, spc_sql1.mod) #looks for dx codes and creates temp1, temp2
  dbGetQuery(spc, spc_sql2.mod) #joins in pcns and inserts into temp3
  
  
  if (yr==18) #for 2018, also look in HTW table
  {
    print("Now looking in HTW for 2018")
    spc_htw1.mod = spc_htw1 %>% gsub('@dx', dx, .)
    dbGetQuery(spc, 'drop table if exists work.dbo.xz_temp_htw;')
    dbGetQuery(spc, spc_htw1.mod) #looks for dx codes and creates temp_htw
    dbGetQuery(spc, spc_htw2) #joins in pcns, inserts into temp3
  }
  
  spc_results = rbind(spc_results, dbGetQuery(spc, spc_sql3)) #counts
}


tac_sql1.mod = tac_sql1 %>% gsub('@dx', dx, .) %>%
  gsub('@starting_year', starting_year, .) %>%
  gsub('@ending_year', ending_year, .)
dbGetQuery(tac, 'drop table if exists dev.xz_temp1;')
dbGetQuery(tac, tac_sql1.mod)
tac_results = dbGetQuery(tac, tac_sql2)


```
## 2.4 ICD-10 make results table
```{r}
#rename columns
colnames(spc_results) = c('fy', 'spc_rows', 'spc_distinct_icn', 'spc_distinct_pcn')
colnames(tac_results) = c('fy', 'dw_rows', 'dw_distinct_icn', 'dw_distinct_pcn')

#coerce spc_results year to int so we can join
spc_results$fy = as.integer(spc_results$fy)

dx_results_icd10 = spc_results %>%
  left_join(tac_results, by = "fy") %>%
  mutate(rows_diff = spc_rows - dw_rows,
         icn_diff = spc_distinct_icn - dw_distinct_icn,
         pcn_diff = spc_distinct_pcn - dw_distinct_pcn)

```

# SECTION 3: Check proc codes

## 3.0 Define base SQL queries for modification
```{r}
spc_proc1 = 'select \'20@yr\' as fy, icn, pcn
  into work.dbo.xz_temp1
  from medicaid.dbo.clm_proc_@yr where
  PROC_ICD_CD_1 = \'@proc\' or
  PROC_ICD_CD_2 = \'@proc\' or
  PROC_ICD_CD_3 = \'@proc\' or
  PROC_ICD_CD_4 = \'@proc\' or
  PROC_ICD_CD_5 = \'@proc\' or
  PROC_ICD_CD_6 = \'@proc\' or
  PROC_ICD_CD_7 = \'@proc\' or
  PROC_ICD_CD_8 = \'@proc\' or
  PROC_ICD_CD_9 = \'@proc\' or
  PROC_ICD_CD_10 = \'@proc\' or
  PROC_ICD_CD_11 = \'@proc\' or
  PROC_ICD_CD_12 = \'@proc\' or
  PROC_ICD_CD_13 = \'@proc\' or
  PROC_ICD_CD_14 = \'@proc\' or
  PROC_ICD_CD_15 = \'@proc\' or
  PROC_ICD_CD_16 = \'@proc\' or
  PROC_ICD_CD_17 = \'@proc\' or
  PROC_ICD_CD_18 = \'@proc\' or
  PROC_ICD_CD_19 = \'@proc\' or
  PROC_ICD_CD_20 = \'@proc\' or
  PROC_ICD_CD_21 = \'@proc\' or
  PROC_ICD_CD_22 = \'@proc\' or
  PROC_ICD_CD_23 = \'@proc\' or
  PROC_ICD_CD_24 = \'@proc\' or
  PROC_ICD_CD_25 = \'@proc\';'

spc_proc2 = 'insert into work.dbo.xz_temp1
  select \'20@yr\' as fy, derv_enc, mem_id
  from medicaid.dbo.enc_proc_@yr where
  PRIM_PROC_CD = \'@proc\' or
  PROC_ICD_CD_1 = \'@proc\' or
  PROC_ICD_CD_2 = \'@proc\' or
  PROC_ICD_CD_3 = \'@proc\' or
  PROC_ICD_CD_4 = \'@proc\' or
  PROC_ICD_CD_5 = \'@proc\' or
  PROC_ICD_CD_6 = \'@proc\' or
  PROC_ICD_CD_7 = \'@proc\' or
  PROC_ICD_CD_8 = \'@proc\' or
  PROC_ICD_CD_9 = \'@proc\' or
  PROC_ICD_CD_10 = \'@proc\' or
  PROC_ICD_CD_11 = \'@proc\' or
  PROC_ICD_CD_12 = \'@proc\' or
  PROC_ICD_CD_13 = \'@proc\' or
  PROC_ICD_CD_14 = \'@proc\' or
  PROC_ICD_CD_15 = \'@proc\' or
  PROC_ICD_CD_16 = \'@proc\' or
  PROC_ICD_CD_17 = \'@proc\' or
  PROC_ICD_CD_18 = \'@proc\' or
  PROC_ICD_CD_19 = \'@proc\' or
  PROC_ICD_CD_20 = \'@proc\' or
  PROC_ICD_CD_21 = \'@proc\' or
  PROC_ICD_CD_22 = \'@proc\' or
  PROC_ICD_CD_23 = \'@proc\' or
  PROC_ICD_CD_24 = \'@proc\';'

spc_proc_htw = 'insert into work.dbo.xz_temp1
  select \'2018\' as fy, icn, pcn
  from medicaid.dbo.CLM_PROC_1819_HTW where
  PROC_ICD_CD_1 = \'@proc\' or
  PROC_ICD_CD_2 = \'@proc\' or
  PROC_ICD_CD_3 = \'@proc\' or
  PROC_ICD_CD_4 = \'@proc\' or
  PROC_ICD_CD_5 = \'@proc\' or
  PROC_ICD_CD_6 = \'@proc\' or
  PROC_ICD_CD_7 = \'@proc\' or
  PROC_ICD_CD_8 = \'@proc\' or
  PROC_ICD_CD_9 = \'@proc\' or
  PROC_ICD_CD_10 = \'@proc\' or
  PROC_ICD_CD_11 = \'@proc\' or
  PROC_ICD_CD_12 = \'@proc\' or
  PROC_ICD_CD_13 = \'@proc\' or
  PROC_ICD_CD_14 = \'@proc\' or
  PROC_ICD_CD_15 = \'@proc\' or
  PROC_ICD_CD_16 = \'@proc\' or
  PROC_ICD_CD_17 = \'@proc\' or
  PROC_ICD_CD_18 = \'@proc\' or
  PROC_ICD_CD_19 = \'@proc\' or
  PROC_ICD_CD_20 = \'@proc\' or
  PROC_ICD_CD_21 = \'@proc\' or
  PROC_ICD_CD_22 = \'@proc\' or
  PROC_ICD_CD_23 = \'@proc\' or
  PROC_ICD_CD_24 = \'@proc\' or
  PROC_ICD_CD_25 = \'@proc\';'
```

## 3.1 ICD-9 modify and send queries
```{r}

#define the proc code and years for ICD-9
proc = proc9

ending_year = if (ending_year_global > 2018) { 2018 } else { ending_year_global }
starting_year = if (starting_year_global < ending_year) { starting_year_global
  } else { ending_year}

starting_yr = starting_year - 2000
ending_yr = ending_year - 2000

#initialize df for holding spc results
spc_results = data.frame(matrix(ncol=4, nrow=0))
colnames(spc_results) = c('fy', 'rows', 'distinct_icn', 'distinct_pcn')

# we're just gonna tweak the sql query for getting counts a bit so that
# we can reuse it here.
spc_sql3.proc = spc_sql3 %>% gsub('temp3', 'temp1', .)

#tweak tac_sql query as well
tac_sql1.proc = tac_sql1 %>% gsub('_diag_', '_icd_proc_', .) %>%
  gsub('diag_cd','proc_cd',.) %>% 
  gsub('@dx', proc, .) %>%
  gsub('@starting_year', starting_year, .) %>%
  gsub('@ending_year', ending_year, .)

#get counts for 
for (yr in starting_yr:ending_yr) {
  print(paste0("Getting icd-9 proc counts from SPC for fy 20", yr))
  
  spc_proc1.mod = spc_proc1 %>% gsub('@yr', yr, .) %>% gsub('@proc', proc, .)
  spc_proc2.mod = spc_proc2 %>% gsub('@yr', yr, .) %>% gsub('@proc', proc, .)
  
  dbExecute(spc, 'drop table if exists work.dbo.xz_temp1;')
  dbGetQuery(spc, spc_proc1.mod) #look for proc codes in clm tables
  if (yr != 12) dbGetQuery(spc, spc_proc2.mod) #look for proc codes in enc tables
  
  if (yr==18) #for 2018, also look in HTW table
  {
    print("Now looking in HTW for 2018")
    spc_proc_htw.mod = spc_proc_htw %>% gsub('@proc', proc, .)
    dbGetQuery(spc, spc_proc_htw.mod) #looks for dx codes and creates temp_htw
  }
  
  current_results = dbGetQuery(spc, spc_sql3.proc) #get counts
  if (nrow(current_results) > 0) {
    spc_results = rbind(spc_results, current_results)
  } else {
    spc_results = rbind(spc_results, c(yr+2000, 0, 0, 0))
  }
}


dbGetQuery(tac, 'drop table if exists dev.xz_temp1;')
dbGetQuery(tac, tac_sql1.proc)
tac_results = dbGetQuery(tac, tac_sql2)
```

## 3.2 ICD-9 make results table
```{r}
#rename columns
colnames(spc_results) = c('fy', 'spc_rows', 'spc_distinct_icn', 'spc_distinct_pcn')
colnames(tac_results) = c('fy', 'dw_rows', 'dw_distinct_icn', 'dw_distinct_pcn')

#coerce spc_results year to int so we can join
spc_results$fy = as.integer(spc_results$fy)

proc_results_icd9 = spc_results %>%
  left_join(tac_results, by = "fy") %>%
  replace(is.na(.), 0) %>%
  mutate(rows_diff = spc_rows - dw_rows,
         icn_diff = spc_distinct_icn - dw_distinct_icn,
         pcn_diff = spc_distinct_pcn - dw_distinct_pcn)
```

## 3.3 ICD-10 modify and send queries
```{r}

#define the proc code and years for ICD-10
proc = proc10

starting_year = starting_year_global
ending_year = ending_year_global

starting_yr = starting_year - 2000
ending_yr = ending_year - 2000

#initialize df for holding spc results
spc_results = data.frame(matrix(ncol=4, nrow=0))
colnames(spc_results) = c('fy', 'rows', 'distinct_icn', 'distinct_pcn')

# we're just gonna tweak the sql query for getting counts a bit so that
# we can reuse it here.
spc_sql3.proc = spc_sql3 %>% gsub('temp3', 'temp1', .)

#tweak tac_sql query as well
tac_sql1.proc = tac_sql1 %>% gsub('_diag_', '_icd_proc_', .) %>%
  gsub('diag_cd','proc_cd',.) %>% 
  gsub('@dx', proc, .) %>%
  gsub('@starting_year', starting_year, .) %>%
  gsub('@ending_year', ending_year, .)

#get counts for 
for (yr in starting_yr:ending_yr) {
  print(paste0("Getting icd-10 proc counts from SPC for fy 20", yr))
  
  spc_proc1.mod = spc_proc1 %>% gsub('@yr', yr, .) %>% gsub('@proc', proc, .)
  spc_proc2.mod = spc_proc2 %>% gsub('@yr', yr, .) %>% gsub('@proc', proc, .)
  
  dbExecute(spc, 'drop table if exists work.dbo.xz_temp1;')
  dbGetQuery(spc, spc_proc1.mod) #look for proc codes in clm tables
  if (yr != 12) dbGetQuery(spc, spc_proc2.mod) #look for proc codes in enc tables
  
  if (yr==18) #for 2018, also look in HTW table
  {
    print("Now looking in HTW for 2018")
    spc_proc_htw.mod = spc_proc_htw %>% gsub('@proc', proc, .)
    dbGetQuery(spc, spc_proc_htw.mod) #looks for dx codes and creates temp_htw
  }
  
  current_results = dbGetQuery(spc, spc_sql3.proc) #get counts
  
  if (nrow(current_results) > 0) {
    spc_results = rbind(spc_results, current_results)
  } else {
    spc_results = rbind(spc_results, c(yr+2000, 0, 0, 0))
    colnames(spc_results) = c('fy', 'rows', 'distinct_icn', 'distinct_pcn')
  }
  
}


dbGetQuery(tac, 'drop table if exists dev.xz_temp1;')
dbGetQuery(tac, tac_sql1.proc)
tac_results = dbGetQuery(tac, tac_sql2)
```

## 3.4 ICD-10 make results table
```{r}
#rename columns
colnames(spc_results) = c('fy', 'spc_rows', 'spc_distinct_icn', 'spc_distinct_pcn')
colnames(tac_results) = c('fy', 'dw_rows', 'dw_distinct_icn', 'dw_distinct_pcn')

#coerce spc_results year to int so we can join
spc_results$fy = as.integer(spc_results$fy)

proc_results_icd10 = spc_results %>%
  left_join(tac_results, by = "fy") %>%
  replace(is.na(.), 0) %>%
  mutate(rows_diff = spc_rows - dw_rows,
         icn_diff = spc_distinct_icn - dw_distinct_icn,
         pcn_diff = spc_distinct_pcn - dw_distinct_pcn)

# NOTE: The extra icns and member IDs in 2019 are actually duplicated records that
# belong to FY 2020 - data_warehouse has the correct FY (SPC raw tables are wrong)
```

# SECTION 4: Check NDC codes
## 4.0 Define base SQL queries for modification
```{r}
# Hallelujah there's no impact of ICD version switch

spc_ndc1 = 'select \'20@yr\' as fy, concat(pcn, ndc, replace(rx_fill_dt, \'-\', \'\')) as rx_id, pcn
  into work.dbo.xz_temp1
  from medicaid.dbo.chip_rx_fy@yr where ndc = \'@ndc\' and
  pcn is not null and trim(pcn) != \'\';'

spc_ndc2 = 'insert into work.dbo.xz_temp1
  select \'20@yr\' as fy, concat(pcn, ndc, replace(rx_fill_dt, \'-\', \'\')) as rx_id, pcn
  from medicaid.dbo.ffs_rx_fy@yr where ndc = \'@ndc\' and
  pcn is not null and trim(pcn) != \'\';'

spc_ndc3 = 'select a.*
into work.dbo.xz_temp2
from work.dbo.xz_temp1 a inner join
	(select client_nbr as pcn from medicaid.dbo.enrl_20@yr
	union all
	select client_nbr as pcn from medicaid.dbo.chip_uth_sfy20@yr_final
	) b on a.pcn = b.pcn;'

tac_ndc = 'select fiscal_year as fy, rx_claim_id_src as rx_id, member_id_src as pcn
  into dev.xz_temp1
  from data_warehouse.pharmacy_claims_1_prt_mdcd
  where ndc = \'@ndc\'
  and fiscal_year between @starting_year and @ending_year;'

tac_ndc2 = 'select fy, count(*) as rows, count(distinct rx_id) as distinct_rx_id,
  count(distinct pcn) as distinct_pcn
  from dev.xz_temp1
  group by fy
  order by fy;'

```

## 4.1 Modify and send queries
```{r}

starting_year = starting_year_global
ending_year = ending_year_global

starting_yr = starting_year - 2000
ending_yr = ending_year - 2000

#initialize df for holding spc results
spc_results = data.frame(matrix(ncol=4, nrow=0))
spc_results2 = data.frame(matrix(ncol=4, nrow=0))
colnames(spc_results) = c('fy', 'rows', 'distinct_rx_id', 'distinct_pcn')
colnames(spc_results2) = c('fy', 'rows', 'distinct_rx_id', 'distinct_pcn')

# we're just gonna tweak the sql query for getting counts a bit so that
# we can reuse it here.
spc_sql3.ndc1 = spc_sql3 %>% gsub('temp3', 'temp1', .) %>%
  gsub('icn', 'rx_id', .)

spc_sql3.ndc2 = spc_sql3 %>% gsub('temp3', 'temp2', .) %>%
  gsub('icn', 'rx_id', .)

#tweak tac_sql query as well
tac_ndc.mod = tac_ndc %>% 
  gsub('@ndc', ndc, .) %>%
  gsub('@starting_year', starting_year, .) %>%
  gsub('@ending_year', ending_year, .)

#get counts for 
for (yr in starting_yr:ending_yr) {
  print(paste0("Getting rx counts from SPC for fy 20", yr))
  
  spc_ndc1.mod = spc_ndc1 %>% gsub('@yr', yr, .) %>% gsub('@ndc', ndc, .)
  spc_ndc2.mod = spc_ndc2 %>% gsub('@yr', yr, .) %>% gsub('@ndc', ndc, .)
  spc_ndc2.mod2 = spc_ndc2.mod %>% gsub('ffs', 'mco', .) #modify query to look in MCO tables
  spc_ndc3.mod = spc_ndc3 %>% gsub('@yr', yr, .)
  
  dbExecute(spc, 'drop table if exists work.dbo.xz_temp1;')
  dbExecute(spc, 'drop table if exists work.dbo.xz_temp2;')
  
  dbGetQuery(spc, spc_ndc1.mod) # look for matching ndcs in CHIP tables
  dbGetQuery(spc, spc_ndc2.mod) # look for matching ndcs in FFS tables
  dbGetQuery(spc, spc_ndc2.mod2) # look for matching ndcs in MCO tables
  
  if (yr==18) #for 2018, also look in HTW table
  {
    print("Now looking in HTW for 2018")
    spc_ndc2.htw = spc_ndc2.mod %>% gsub('ffs_rx_fy18', 'ffs_rx_fy18_19_htw', .)
    dbGetQuery(spc, spc_ndc2.htw) # look for matching ndcs in HTW RX
  }
  
  # join to enrollment table to filter out bad PCNs
  dbGetQuery(spc, spc_ndc3.mod)
  
  # make two tables: one with pcn matching and one without
  # rationale: pcn matching is done year-by-year and filters out
  # people enrolled in mcd but not for that fy
  # dw matches on if a member is enrolled at any time
  current_results1 = dbGetQuery(spc, spc_sql3.ndc1) # get counts w/o pcn matching
  current_results2 = dbGetQuery(spc, spc_sql3.ndc2) # get counts w/ pcn matching
  
  if (nrow(current_results) > 0) {
    spc_results = rbind(spc_results, current_results1)
    spc_results2 = rbind(spc_results2, current_results2)
  } else {
    spc_results = rbind(spc_results, c(yr+2000, 0, 0, 0))
    spc_results2 = rbind(spc_results2, c(yr+2000, 0, 0, 0))
    colnames(spc_results) = c('fy', 'rows', 'distinct_rx_id', 'distinct_pcn')
    colnames(spc_results2) = c('fy', 'rows', 'distinct_rx_id', 'distinct_pcn')
  }
  
}


dbGetQuery(tac, 'drop table if exists dev.xz_temp1;')
dbGetQuery(tac, tac_ndc.mod)
tac_results = dbGetQuery(tac, tac_ndc2)

```

## 4.2 Make results tables
```{r}

#rename columns
colnames(spc_results) = c('fy', 'spc_rows', 'spc_distinct_rx_id', 'spc_distinct_pcn')
colnames(spc_results2) = c('fy', 'spc_rows', 'spc_distinct_rx_id', 'spc_distinct_pcn')
colnames(tac_results) = c('fy', 'dw_rows', 'dw_distinct_rx_id', 'dw_distinct_pcn')

#coerce spc_results year to int so we can join
spc_results$fy = as.integer(spc_results$fy)
spc_results2$fy = as.integer(spc_results2$fy)

ndc_results1 = spc_results %>%
  left_join(tac_results, by = "fy") %>%
  replace(is.na(.), 0) %>%
  mutate(rows_diff = spc_rows - dw_rows,
         rx_id_diff = spc_distinct_rx_id - dw_distinct_rx_id,
         pcn_diff = spc_distinct_pcn - dw_distinct_pcn)

ndc_results2 = spc_results2 %>%
  left_join(tac_results, by = "fy") %>%
  replace(is.na(.), 0) %>%
  mutate(rows_diff = spc_rows - dw_rows,
         rx_id_diff = spc_distinct_rx_id - dw_distinct_rx_id,
         pcn_diff = spc_distinct_pcn - dw_distinct_pcn)

# See note on PCN matching in previous chunk

```


# SECTION 5: Check CPT/HCSPCS codes
## 5.0 Define base SQL queries for modification
```{r}

#query for clm
spc_cpt1 = 'select \'20@yr\' as fy, a.icn, b.pcn
into work.dbo.xz_temp1
from medicaid.dbo.CLM_DETAIL_@yr a inner join medicaid.dbo.CLM_PROC_@yr b
on a.ICN = b.ICN
where PROC_CD = \'@cpt\' or SUB_PROC_CD = \'@cpt\';'

#query for enc
spc_cpt2 = 'insert into work.dbo.xz_temp1
  select \'20@yr\' as fy, a.derv_enc, b.MEM_ID
  from medicaid.dbo.ENC_DET_@yr a inner join medicaid.dbo.ENC_PROC_@yr b
  on a.derv_enc = b.derv_enc
  where PROC_CD = \'@cpt\';'

spc_cpt_htw = 'insert into work.dbo.xz_temp1
  select \'2018\' as fy, a.icn, b.pcn
  from medicaid.dbo.CLM_DETAIL_1819_HTW a inner join medicaid.dbo.CLM_PROC_1819_HTW b
  on a.ICN = b.ICN
  where PROC_CD = \'@cpt\' or SUB_PROC_CD = \'@cpt\';'

tac_cpt = 'select fiscal_year as fy, claim_id_src as icn, member_id_src as pcn
  into dev.xz_temp1
  from data_warehouse.claim_detail_1_prt_mdcd
  where cpt_hcpcs_cd = \'@cpt\'
  and fiscal_year between @starting_year and @ending_year;'

tac_cpt2 = 'select fy, count(*) as rows, count(distinct icn) as distinct_icn,
  count(distinct pcn) as distinct_pcn
  from dev.xz_temp1
  group by fy
  order by fy;'

```

## 5.1 Modify and send queries
```{r}

starting_year = starting_year_global
ending_year = ending_year_global

starting_yr = starting_year - 2000
ending_yr = ending_year - 2000

#initialize df for holding spc results
spc_results = data.frame(matrix(ncol=4, nrow=0))
colnames(spc_results) = c('fy', 'rows', 'distinct_icn', 'distinct_pcn')

# we're just gonna tweak the sql query for getting counts a bit so that
# we can reuse it here.
spc_sql3.cpt = spc_sql3 %>% gsub('temp3', 'temp1', .)

#tweak tac_sql query as well
tac_cpt.mod = tac_cpt %>% 
  gsub('@cpt', cpt, .) %>%
  gsub('@starting_year', starting_year, .) %>%
  gsub('@ending_year', ending_year, .)

#get counts for 
for (yr in starting_yr:ending_yr) {
  print(paste0("Getting cpt counts from SPC for fy 20", yr))
  
  spc_cpt1.mod = spc_cpt1 %>% gsub('@yr', yr, .) %>% gsub('@cpt', cpt, .)
  spc_cpt2.mod = spc_cpt2 %>% gsub('@yr', yr, .) %>% gsub('@cpt', cpt, .)
  
  dbExecute(spc, 'drop table if exists work.dbo.xz_temp1;')
  
  dbGetQuery(spc, spc_cpt1.mod) # look for matching cpts in clm tables
  if (yr>12) dbGetQuery(spc, spc_cpt2.mod) # look for matching cpts in enc tables
  
  if (yr==18) #for 2018, also look in HTW table
  {
    print("Now looking in HTW for 2018")
    spc_cpt_htw.mod = spc_cpt_htw %>% gsub('@yr', yr, .) %>% gsub('@cpt', cpt, .)
    dbGetQuery(spc, spc_cpt_htw.mod) # look for matching cpts in HTW details
  }
  
  # get counts
  current_results = dbGetQuery(spc, spc_sql3.cpt)
  
  if (nrow(current_results) > 0) {
    spc_results = rbind(spc_results, current_results)
  } else {
    spc_results = rbind(spc_results, c(yr+2000, 0, 0, 0))
    colnames(spc_results) = c('fy', 'rows', 'distinct_icn', 'distinct_pcn')
  }
  
}

dbGetQuery(tac, 'drop table if exists dev.xz_temp1;')
dbGetQuery(tac, tac_cpt.mod)
tac_results = dbGetQuery(tac, tac_cpt2)

```

## 5.2 Make results tables
```{r}

#rename columns
colnames(spc_results) = c('fy', 'spc_rows', 'spc_distinct_icn', 'spc_distinct_pcn')
colnames(tac_results) = c('fy', 'dw_rows', 'dw_distinct_icn', 'dw_distinct_pcn')

#coerce spc_results year to int so we can join
spc_results$fy = as.integer(spc_results$fy)

cpt_results = spc_results %>%
  left_join(tac_results, by = "fy") %>%
  replace(is.na(.), 0) %>%
  mutate(rows_diff = spc_rows - dw_rows,
         icn_diff = spc_distinct_icn - dw_distinct_icn,
         pcn_diff = spc_distinct_pcn - dw_distinct_pcn)

# The mismatches are bc we dropped the sub_proc_cd. I checked and 


```

# SECTION 6: Output it all to a spreadsheet
```{r}
wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "dw-test-queries.xlsx")

addWorksheet(wb, sheetName = "dx codes")
addWorksheet(wb, sheetName = "proc codes")
addWorksheet(wb, sheetName = "ndc codes")
addWorksheet(wb, sheetName = "cpt codes")

#Write DX codes
writeData(wb, sheet = 1, "Comparison of dx codes found in SPC raw data and data_warehouse", startCol=1, startRow=1)
writeData(wb, sheet = 1, paste("Run time:", Sys.time()), startCol=1, startRow=2)

writeData(wb, sheet = 1, paste("DX code searched for:", dx9), startCol=1, startRow=4)
writeData(wb, sheet = 1, dx_results_icd9, startCol=1, startRow=5)
nextrow = nrow(dx_results_icd9) + 7

writeData(wb, sheet = 1, paste("DX code searched for:", dx10), startCol=1, startRow=nextrow)
writeData(wb, sheet = 1, dx_results_icd10, startCol=1, startRow=nextrow+1)

setColWidths(wb, sheet = 1, cols=1:ncol(dx_results_icd9)+1, widths="auto")
setColWidths(wb, sheet = 1, cols=1, widths=10)

#Write PROC codes
writeData(wb, sheet = 2, "Comparison of proc codes found in SPC raw data and data_warehouse", startCol=1, startRow=1)
writeData(wb, sheet = 2, paste("Run time:", Sys.time()), startCol=1, startRow=2)

writeData(wb, sheet = 2, paste("ICD-9 proc code searched for:", proc9), startCol=1, startRow=4)
writeData(wb, sheet = 2, proc_results_icd9, startCol=1, startRow=5)
nextrow = nrow(proc_results_icd9) + 7

writeData(wb, sheet = 2, paste("ICD-10 proc code searched for:", proc10), startCol=1, startRow=nextrow)
writeData(wb, sheet = 2, proc_results_icd10, startCol=1, startRow=nextrow+1)
nextrow = nextrow + nrow(proc_results_icd10) + 3

writeData(wb, sheet = 2, "NOTE: The PROC code discrepancy in 2019 is because several claims that are supposed to be in FY2020 ended up duplicated in the raw FY2019 tables.", startCol=1, startRow=nextrow)
writeData(wb, sheet = 2, "data_warehouse has the fiscal_year for claims assigned correctly", startCol=1, startRow=nextrow+1)

setColWidths(wb, sheet = 2, cols=1:ncol(proc_results_icd9)+1, widths="auto")
setColWidths(wb, sheet = 2, cols=1, widths=10)



#Write NDC codes
writeData(wb, sheet = 3, "Comparison of NDC codes found in SPC raw data and data_warehouse", startCol=1, startRow=1)
writeData(wb, sheet = 3, paste("Run time:", Sys.time()), startCol=1, startRow=2)

writeData(wb, sheet = 3, paste("NDC code searched for:", ndc), startCol=1, startRow=4)
writeData(wb, sheet = 3, "Without matching PCNs to enrollment tables", startCol=1, startRow=6)
writeData(wb, sheet = 3, ndc_results1, startCol=1, startRow=7)
nextrow = nrow(ndc_results1) + 9

writeData(wb, sheet = 3, "WITH matching PCNs to enrollment tables", startCol=1, startRow=nextrow)
writeData(wb, sheet = 3, ndc_results2, startCol=1, startRow=nextrow+1)
nextrow = nextrow + nrow(ndc_results2) + 3

writeData(wb, sheet = 3, "NOTE: Several PCNs in the RX tables do not map to any PCNs in enrollment tables.", startCol=1, startRow=nextrow)
writeData(wb, sheet = 3, "Additionally, many PCNs will map to enrollment tables but the member is not enrolled for that fiscal year", startCol=1, startRow=nextrow+1)
writeData(wb, sheet = 3, "DW member_id mapping checks against all years of enrollment and includes rows where the member is enrolled in Medicaid in ANY year", startCol=1, startRow=nextrow+2)
writeData(wb, sheet = 3, "The code written for the SPC side matches each RX table up with the enrollment tables (CHIP and ENRL) for just that year alone", startCol=1, startRow=nextrow+3)

setColWidths(wb, sheet = 3, cols=1:ncol(ndc_results1)+1, widths="auto")
setColWidths(wb, sheet = 3, cols=1, widths=10)

#Write CPT codes
writeData(wb, sheet = 4, "Comparison of CPT/HCSPCS codes found in SPC raw data and data_warehouse", startCol=1, startRow=1)
writeData(wb, sheet = 4, paste("Run time:", Sys.time()), startCol=1, startRow=2)

writeData(wb, sheet = 4, paste("CPT code searched for:", cpt), startCol=1, startRow=4)
writeData(wb, sheet = 4, cpt_results, startCol=1, startRow=5)
nextrow = nrow(cpt_results) + 7

writeData(wb, sheet = 4, "NOTE: the entirety of the disparity is due to the fact that SUB_PROC_CD (a field that only exists in CLM tables) doesn't get included in data_warehouse", startCol=1, startRow=nextrow)

setColWidths(wb, sheet = 4, cols=1:ncol(cpt_results)+1, widths="auto")
setColWidths(wb, sheet = 4, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```







# 99 Troubleshooting
```{r}
spc_out = dbReadTable(spc, SQL("work.dbo.xz_temp2"))
names(spc_out) = tolower(names(spc_out))
dbWriteTable(tac, SQL("dev.xz_temp5"), spc_out, overwrite = TRUE)

```

```{r close-connections}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env}
# clears R environment
rm(list=ls())
```



