---
title: "dw-qa-test"
author: "XRZ"
date: '2022-12-2'
output: html_document
---


# Purpose
things are different on SPC side and TACC side

I need to figure out what

# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

#packages I don't use anymore: rstudioapi

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password


#Connect to Greenplum
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(), dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc")))
```

## 0.5 Set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation

```

# SECTION 1: Define global variables
```{r}

```

# SECTION 2: Pull and upload data
```{sql, connection = spc}

select count(distinct client_nbr)
from stage.dbo.AGG_ENRL_MCD_FY
where ENRL_FY= 2021;
--5766346	

```

```{sql, connection = tac}

select count(distinct member_id_src) from dev.member_enrollment_fiscal_yearly
where fiscal_year = 2021;

--5753239, about 13107 missing in tacc

--6167446 including HTW

```

```{sql, connection = spc}

drop table if exists work.dbo.xz_temp1;

select *
into work.dbo.xz_temp1
from stage.dbo.AGG_ENRL_MCD_FY
where ENRL_FY= 2021;

```

```{sql, connection = spc, output.var = spc_out}

SELECT * FROM work.dbo.xz_temp1;

```

```{r}
#make names lowercase
names(spc_out) <- tolower(names(spc_out))

#upload spc table to tacc
dbWriteTable(tac, SQL("dev.xz_temp1"), spc_out, overwrite = TRUE)

```

# SECTION 3: Compare data
```{sql, connection = tac}
drop table if exists dev.xz_temp2;
```

```{sql, connection = tac}
--compare tables

select a.*, b.*
into dev.xz_temp2
from dev.xz_temp1 a full join dev.member_enrollment_fiscal_yearly b
on a.client_nbr = b.member_id_src and a.fy = b.fiscal_year::text
where b.fiscal_year = 2021;


```

```{sql, connection = tac, output.var = differences}

select * from dev.xz_temp2 where member_id_src is null or client_nbr is null;

```

# SECTION 4: Print out results






```{r close-connections}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env}
# clears R environment
rm(list=ls())
```



