---
title: "dwqa-truven-claim-header-counts"
author: "XRZ"
date: '2023-01-03'
output: html_document
---


#Purpose:
This R markdown script examines the accuracy of conversions from raw source tables to
data_warehouse tables


# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

#packages I don't use anymore: rstudioapi

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password

# Function for connecting to TACC/Greenplum
# TACC kicks you out for inactivity so just call function before connections
connect_to_tacc <- function() {
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
}

```

## 0.3 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("connect_to_tacc")))
```

## 0.5 Set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation

```
# SECTION 1: Get counts of rows and distinct ENROLIDs

## 1.1 Get counts
```{r}
tac = connect_to_tacc()

tic("Count distinct member IDs from dw")
dw_monthly_counts = dbGetQuery(tac, "select table_id_src,
  count(*) as dw_rows, count(distinct member_id_src) as dw_enrolids,
  count(distinct uth_member_id) as uth_member_ids
  from dw_staging.member_enrollment_monthly_1_prt_truv
  group by table_id_src;")
toc()

#I checkec the counts in A tables - they match the counts from T tables
# ccaea_counts = dbGetQuery(tac, "select 'ccaea'::text as table_id_src,
#  count(*) as truv_rows, count(distinct enrolid) as truv_enrolids from truven.ccaea;")

# mdcra_counts = dbGetQuery(tac, "select 'mdcra'::text as table_src,
#  count(*) as truv_rows, count(distinct enrolid) as truv_enrolids from truven.mdcra;")

tic("Count distinct member IDs from ccaet")
ccaet_counts = dbGetQuery(tac, "select 'ccaet'::text as table_id_src,
  count(*) as truv_rows, count(distinct enrolid) as truv_enrolids from truven.ccaet;")
toc()

tic("Count distinct member IDs from mdcrt")
mdcrt_counts = dbGetQuery(tac, "select 'mdcrt'::text as table_id_src,
  count(*) as truv_rows, count(distinct enrolid) as truv_enrolids from truven.mdcrt;")
toc()

```

## 1.2 Make it into a table
```{r}

counts_merged = rbind(ccaet_counts, mdcrt_counts) %>%
  left_join(dw_monthly_counts, by = "table_id_src") %>%
  mutate(rows_diff = truv_rows - dw_rows,
         enrolids_diff = truv_enrolids - dw_enrolids)

```

# SECTION 2: Get counts of distinct ENROLID-YEAR-MONTH combinations

## 2.1 Make tables of distinct memid_yr_mth combos

```{r}
tac = connect_to_tacc()

dbExecute(tac, "drop table if exists dev.xz_temp1")
dbExecute(tac, "drop table if exists dev.xz_temp2")
dbExecute(tac, "drop table if exists dev.xz_temp3")

tic("Creating mym table from dw")
dbExecute(tac, "create table dev.xz_temp1 as
  select table_id_src, year, member_id_src || month_year_id as memid_yr_mth
  from dw_staging.member_enrollment_monthly_1_prt_truv
  distributed by (memid_yr_mth);")
toc()

tic("Creating mym table from ccaet")
dbExecute(tac, "create table dev.xz_temp2 as
  select 'ccaet'::text as table_id_src, year,
  enrolid || substring(replace(dtstart::varchar, '-', ''), 1, 6) as memid_yr_mth
  from truven.ccaet
  distributed by (memid_yr_mth)")
toc()

tic("Creating mym tables from mdcrt")
dbExecute(tac, "create table dev.xz_temp3 as
  select 'mdcrt'::text as table_id_src, year,
  enrolid || substring(replace(dtstart::varchar, '-', ''), 1, 6) as memid_yr_mth
  from truven.mdcrt
  distributed by (memid_yr_mth);")
toc()

dbExecute(tac, "analyze dev.xz_temp1;")
dbExecute(tac, "analyze dev.xz_temp2;")
dbExecute(tac, "analyze dev.xz_temp3;")

```

## 2.2 Count 'em

```{r}
tac = connect_to_tacc()

tic("Counting mym from dw")
dw_mym_counts = dbGetQuery(tac, "select table_id_src, year, count(distinct memid_yr_mth) as memid_yr_mths
  from dev.xz_temp1
  group by table_id_src, year;")
toc()

tic("Counting mym from ccaet")
ccaet_mym_counts = dbGetQuery(tac, "select table_id_src, year, count(distinct memid_yr_mth) as memid_yr_mths
  from dev.xz_temp2
  group by table_id_src, year;")
toc()

tic("Counting mym from mdcrt")
mdcrt_mym_counts = dbGetQuery(tac, "select table_id_src, year, count(distinct memid_yr_mth) as memid_yr_mths
  from dev.xz_temp3
  group by table_id_src, year;")
toc()

```


## 2.3 Make it into a table
```{r, eval=FALSE}

ccaet_mym_counts = ccaet_mym_counts %>% rename(truv_memid_yr_mths = memid_yr_mths)
mdcrt_mym_counts = mdcrt_mym_counts %>% rename(truv_memid_yr_mths = memid_yr_mths)
dw_mym_counts = dw_mym_counts %>% rename(dw_memid_yr_mths = memid_yr_mths)

mym_counts_merged = rbind(ccaet_mym_counts, mdcrt_mym_counts) %>%
  left_join(dw_mym_counts, by = c("table_id_src", "year")) %>%
  mutate(mym_diffs = truv_memid_yr_mths - dw_memid_yr_mths) %>%
  arrange(table_id_src, year)

```

# SECTION 3: Output to spreadsheet
```{r}

here::i_am("enrollment-counts.Rmd")

wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "truven-enrollment-monthly-counting.xlsx")

addWorksheet(wb, sheetName = "Enrolids")
addWorksheet(wb, sheetName = "Enrolid - Year - Months")

current_sheet = 1; current_df = counts_merged
writeData(wb, sheet = current_sheet,
          "Count of distinct ENROLIDS in data_warehouse and Truven schema on TACC server",
          startCol=1, startRow=1)
writeData(wb, sheet = current_sheet, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = current_sheet, current_df, startCol=1, startRow=4)
nextrow = nrow(current_df) + 6

writeData(wb, sheet=current_sheet, "Notes:", startCol=1, startRow=nextrow)
writeData(wb, sheet=current_sheet, "Rows are produced by count(*)", startCol=1, startRow=nextrow+1)
writeData(wb, sheet=current_sheet, "ENROLIDs are distinct counts", startCol=1, startRow=nextrow+2)
writeData(wb, sheet=current_sheet, "UTH_MEMBER_IDs are distinct counts", startCol=1, startRow=nextrow+3)

setColWidths(wb, sheet = 1, cols=1:ncol(current_df)+1, widths="auto")
setColWidths(wb, sheet = 1, cols=1, widths=10)

current_sheet = 2; current_df = mym_counts_merged
writeData(wb, sheet = current_sheet,
          "Count of distinct ENROLID-YEAR-MONTH combinations in data_warehouse and Truven schema on TACC server",
          startCol=1, startRow=1)
writeData(wb, sheet = current_sheet, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = current_sheet, current_df, startCol=1, startRow=4)

setColWidths(wb, sheet = 1, cols=1:ncol(current_df)+1, widths="auto")
setColWidths(wb, sheet = 1, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```



