---
title: "dwqa-truven-claim-header-counts"
author: "XRZ"
date: '2023-01-06'
output: html_document
---


#Purpose:
This R markdown script examines the accuracy of conversions from raw source tables to
data_warehouse tables


# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

#packages I don't use anymore: rstudioapi

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password

# Function for connecting to TACC/Greenplum
# TACC kicks you out for inactivity so just call function before connections
connect_to_tacc <- function() {
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
}

```

## 0.3 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("connect_to_tacc")))
```

## 0.5 Set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation

```
# SECTION 1: Get counts of rows and distinct ENROLIDs

## 1.1 Base SQL queries for modification
```{r}

dw_sql1 = "select year, table_id_src, count(distinct claim_id_src) as count from dw_staging.claim_header
where table_id_src = '@table'
group by year, table_id_src
order by year;"

truv_sql1 = "select year, '@table'::text as table, count(distinct msclmid) as count from truven.@table
group by year
order by year;"

#this is the list of tables to look in and count
list_of_tables = c("ccaes", "ccaeo", "mdcrs", "mdcro")

```

## 1.2 Get counts from dw
```{r}
tac = connect_to_tacc()

#rm(dw_counts)

for (i in 1:4){
  
  # we count in pieces bc otherwise the query takes too long
  
  table = list_of_tables[i]
  dw_sql1.mod = dw_sql1 %>% gsub("@table", table, .)
  
  tic(paste("Count distinct claim IDs from dw -", table))
  
  current_results = dbGetQuery(tac, dw_sql1.mod)
  
  if (i == 1) {
    dw_counts = current_results
  } else {
    dw_counts = rbind(dw_counts, current_results)
  }
  
  toc()

}
  
```
## 1.3 Get counts from truven schema
```{r}
tac = connect_to_tacc()

for (i in 1:4){
  
  # we count in pieces bc otherwise the query takes too long
  
  table = list_of_tables[i]
  truv_sql1.mod = truv_sql1 %>% gsub("@table", table, .)
  
  tic(paste("Count distinct claim IDs from truven -", table))
  
  current_results = dbGetQuery(tac, truv_sql1.mod)
  
  if (i == 1) {
    truv_counts = current_results
  } else {
   truv_counts = rbind(truv_counts, current_results)
  }
  
  toc()

}
  
```

# SECTION 2: Make it a table
```{r}

# rearrange dw table so that each column is a table_id_src

for (i in 1:4){
  current_table = list_of_tables[i]
  newcolname = paste0("dw_", current_table)
  
  current = dw_counts %>%
    filter(table_id_src == current_table) %>%
    rename(!!newcolname := count) %>%
    select(-table_id_src)
  
  
  if (i==1) {
    all_counts = current
  } else {
    all_counts = all_counts %>%
    left_join(current, by = "year")
  }
}

# rerrange truven table so that each column is a separate table
# (Must be run after dw results - just appends to the same table)

for (i in 1:4){
  
  current_table = list_of_tables[i]
  newcolname = paste0("truv_", current_table)
  
  current = truv_counts %>%
    filter(table == current_table) %>%
    rename(!!newcolname := count) %>%
    select(-table)

    all_counts = all_counts %>%
    left_join(current, by = "year")
}


# get the difference

difference = all_counts %>%
  mutate(ccaes_diff = truv_ccaes - dw_ccaes,
         ccaeo_diff = truv_ccaeo - dw_ccaeo,
         mdcrs_diff = truv_mdcrs - dw_mdcrs,
         mdcro_diff = truv_mdcro - dw_mdcro,) %>%
  select(year, ccaes_diff, ccaeo_diff, mdcrs_diff, mdcro_diff)

```

# SECTION 3: Output to spreadsheet
```{r}

here::i_am("03-claim-header-counts.Rmd")

wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "truven-claim-header-counting.xlsx")

addWorksheet(wb, sheetName="claim-header")

current_sheet = 1; current_df = all_counts
writeData(wb, sheet = current_sheet,
          "Count of distinct claim IDs (msclmid) in data_warehouse and Truven schema on TACC server",
          startCol=1, startRow=1)
writeData(wb, sheet = current_sheet, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = current_sheet, current_df, startCol=1, startRow=4)
nextrow = nrow(current_df) + 6

writeData(wb, sheet=current_sheet, "Difference between Truven schema and data_warehouse (Truven - DW):", startCol=1, startRow = nextrow)
writeData(wb, sheet = current_sheet, difference, startCol=1, startRow=nextrow+1)

setColWidths(wb, sheet = 1, cols=1:ncol(current_df)+1, widths="auto")
setColWidths(wb, sheet = 1, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```



