---
title: "dw-enrollment-check"
author: "XRZ"
date: '2022-10-31'
output: html_document
---

#Purpose:
This R markdown script examines the accuracy of conversions from raw source tables to
data_warehouse tables

It selects random rows from the enrollment table created on the SPC server
and compares them to the dw_staging yearly enrollment table

Spotcheck2 runs in the spc -> dw direction (Spotcheck1 runs in the reverse direction)

# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, rstudioapi, keyring, openxlsx, tidyverse, beepr, tictoc, here)

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password


#Connect to Greenplum
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(),
	 dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc")))
```

## 0.5 Set some options for R
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation

```

# SECTION 1: Define global variables

```{r}
#Define how many rows to check per year
rows_to_check = 500000

#Define how many sets of errors to print out per year
records_to_print = 5

```

# SECTION 2: Compare SPC and TACC tables
## 2.1 Pull TACC data and upload to SPC
```{r}

rows_to_sample = as.integer(rows_to_check) * 1.2

spc_sql = 'select top @rows_to_check *
from work.dbo.xz_mcd_enrl_cy_reconciled
tablesample(@rows_to_sample rows);'

spc_sql.mod = spc_sql %>% gsub('@rows_to_check', rows_to_check, .) %>%
  gsub('@rows_to_sample', rows_to_sample, .)
spc_selection = dbGetQuery(spc, spc_sql.mod)

dbGetQuery(tac, 'drop table if exists dev.xz_dwqa_temp1;')

tic("Write to TACC")
dbWriteTable(tac, SQL('dev.xz_dwqa_temp1'), spc_selection)
toc()

```

## 2.2 Make boolean table of mismatches
```{sql, connection = tac}
--Make boolean table of matches
drop table if exists dev.xz_mcd_enrl_mismatches;
```

```{sql, connection = tac}
with c as (select race_cd_src, race_cd from reference_tables.ref_race
	where data_source = 'mdcd' and race_cd_src is not null)
select b.mem_id as member_id, b.cy as year,
	case when a.member_id_src is null then 1 else 0 end as member_id_mismatch,
	case when a.total_enrolled_months != b.enrolled_months then 1 else 0 end as em_mismatch,
	case when a.gender_cd != b.sex then 1 else 0 end as sex_mismatch,
	case when c.race_cd_src != b.race and b.race is not null then 1 else 0 end as race_mismatch,
	case when a.dob_derived != b.dob::date then 1 else 0 end as dob_mismatch,
	case when a.zip5 != b.zip then 1 else 0 end as zip_mismatch,
	case when trim(a.plan_type) != trim(b.mco) then 1 else 0 end as plan_mismatch,
	case when a.dual::text !=  b.smib then 1 else 0 end as dual_mismatch,
	case when a.htw != b.htw then 1 else 0 end as htw_mismatch,
	a.gender_cd as tacc_sex, b.sex as spc_sex,
	c.race_cd_src as tacc_race, b.race as spc_race,
	a.zip5 as tacc_zip, b.zip as spc_zip,
	a.plan_type as tacc_plan, b.mco as spc_plan,
	a.dob_derived as tacc_dob, b.dob as spc_dob
into dev.xz_mcd_enrl_mismatches
from dev.xz_dwqa_temp1 b
	left join dw_staging.member_enrollment_yearly a
	on a.member_id_src = b.mem_id and a.year::text = b.cy
	left join c
	on a.race_cd = c.race_cd;

```

##2.3 Calculate the sum of errors
```{sql, connection = tac, output.var = sum_errors}

select sum(member_id_mismatch) as member_id_mismatches,
	sum(em_mismatch) as em_mismatches,
	sum(sex_mismatch) as sex_mismatches,
	sum(race_mismatch) as race_mismatches,
	sum(dob_mismatch) as dob_mismatches,
	sum(zip_mismatch) as zip_mismatches,
	sum(plan_mismatch) as plan_mismatches,
	sum(dual_mismatch) as dual_mismatches,
	sum(htw_mismatch) as htw_mismatches
from dev.xz_mcd_enrl_mismatches;


```

******************************************************************************
UH EVERYTHING PASSED QC SO I'M GOING TO STOP CODING HERE
EVERYTHING ELSE BELOW HERE NEEDS TO BE CHECKED BEFORE PROCEEDING, OKAY????
*******************************************************************************

# SECTION 3: Closer look at what's going wrong
## 3.1: Pull mismatches
```{r}
#SEX, RACE, ZIP, AND PLAN HAVE MISMATCHES
#Pull lists of mismatches

sex_mismatches = dbGetQuery(tac, 'select member_id, year
              from dev.xz_mcd_enrl_mismatches
              where sex_mismatch = 1;')

race_mismatches = dbGetQuery(tac, 'select member_id, year
              from dev.xz_mcd_enrl_mismatches
              where race_mismatch = 1;')

zip_mismatches = dbGetQuery(tac, 'select member_id, year
              from dev.xz_mcd_enrl_mismatches
              where zip_mismatch = 1;')

plan_mismatches = dbGetQuery(tac, 'select member_id, year
              from dev.xz_mcd_enrl_mismatches
              where plan_mismatch = 1;')

```

## 3.2 Define base queries
```{r}
#Define base queries

mismatch_query = 'select member_id, year,tacc_sex, spc_sex, tacc_race, spc_race,
  tacc_zip, spc_zip, tacc_plan, spc_plan
  from dev.xz_mcd_enrl_mismatches where member_id = \'@memid\' and year = \'@year\''

tac_sql1 = 'with b as (select race_cd_src, race_cd from reference_tables.ref_race
	where data_source = \'mdcd\' and race_cd_src is not null)

select a.member_id_src, a.year, a.month_year_id, a.gender_cd, b.race_cd_src,
a.zip5, a.plan_type
from dw_staging.member_enrollment_monthly a left join b
	on a.race_cd = b.race_cd
	where member_id_src = \'@memid\' and year = \'@year\'
  order by a.month_year_id;'

spc_sql1 = 'select client_nbr, cy, elig_date, sex, race, zip, mco from work.dbo.xz_mcd_reconciliation_cy_etl
  where client_nbr = \'@memid\' and cy = \'@year\'
  order by elig_date;'


```

## 3.3 Data Exploration: Not executed
```{r, eval=FALSE}
#this chunk for data exploration
#just set current_mismatch to the dataframe and row you want to check

current_mismatch = dob_mismatches[1,]

tac_sql1.mod = tac_sql1 %>% gsub('@memid', current_mismatch[1,1], .) %>% 
  gsub('@year', current_mismatch[1,2], .)

spc_sql1.mod = spc_sql1 %>% gsub('@memid', current_mismatch[1,1], .) %>% 
  gsub('@year', current_mismatch[1,2], .)

mismatch_query.mod = mismatch_query %>% gsub('@memid', current_mismatch[1,1], .) %>% 
  gsub('@year', current_mismatch[1,2], .)

mismatch_details = dbGetQuery(spc, mismatch_query.mod)
tacc_details = dbGetQuery(tac, tac_sql1.mod)
spc_details = dbGetQuery(spc, spc_sql1.mod)

mismatch_details
tacc_details
spc_details
```

## 3.4 Define the function to get mismatch info
```{r}
get_mismatch_info = function(current_mismatch){
  tac_sql1.mod = tac_sql1 %>% gsub('@memid', current_mismatch[1,1], .) %>% 
  gsub('@year', current_mismatch[1,2], .)

  spc_sql1.mod = spc_sql1 %>% gsub('@memid', current_mismatch[1,1], .) %>% 
    gsub('@year', current_mismatch[1,2], .)
  
  mismatch_query.mod = mismatch_query %>% gsub('@memid', current_mismatch[1,1], .) %>% 
    gsub('@year', current_mismatch[1,2], .)
  
  mismatch_details = dbGetQuery(tac, mismatch_query.mod)
  tacc_details = dbGetQuery(tac, tac_sql1.mod)
  spc_details = dbGetQuery(spc, spc_sql1.mod)
  
  output = list(mismatch_details = mismatch_details,
                tacc_details = tacc_details,
                spc_details = spc_details)
  
  return(output)
}

```

## 3.5 Assemble into a spreadsheet
```{r, eval=FALSE}
#this chunk spits out the final table

wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "dw-enrollment-spotcheck-spc-to-tacc.xlsx")

addWorksheet(wb, sheetName = "Summary of Mismatches") #1
addWorksheet(wb, sheetName = "sex mismatches")        #2
addWorksheet(wb, sheetName = "race mismatches")       #3
addWorksheet(wb, sheetName = "zip mismatches")        #4
addWorksheet(wb, sheetName = "plan mismatches")       #5

#write data into sheet 1
writeData(wb, sheet = 1, "Data Warehouse Enrollment Tables Spot Check", startCol=1, startRow=1)
writeData(wb, sheet = 1, paste("Run date:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = 1, "Direction: Records selected from TACC server, checked against SPC server",
                              startCol=1, startRow=3)
writeData(wb, sheet = 1, paste("Rows checked:", rows_to_check), startCol = 1, startRow = 4)
writeData(wb, sheet = 1, sum_errors, startCol=1, startRow=6)

#write headers for all other sheets
writeData(wb, sheet = 2, "Sex Mismatches", startCol=1, startRow=1)
writeData(wb, sheet = 3, "Race Mismatches", startCol=1, startRow=1)
writeData(wb, sheet = 4, "Zip Mismatches", startCol=1, startRow=1)
writeData(wb, sheet = 5, "Plan Type Mismatches", startCol=1, startRow=1)

print("Writing mismatches for sex")


#Write mismatches for sex
next_row = 3 #reset next_row
for (i in 1:min(nrow(sex_mismatches), records_to_print)){
  current_mismatch = sex_mismatches[i,]
  output = get_mismatch_info(current_mismatch)
  
  writeData(wb, sheet = 2, "Mismatch details from yearly tables", startCol = 1, startRow = next_row)
  writeData(wb, sheet = 2, output$mismatch_details, startCol = 1, startRow = next_row + 1)
  next_row = next_row + nrow(output$mismatch_details) + 3
  
  writeData(wb, sheet = 2, "Mismatch details from TACC dw_staging monthly table",
            startCol = 1, startRow = next_row)
  writeData(wb, sheet = 2, output$tacc_details, startCol = 1, startRow = next_row+1)
  next_row = next_row + nrow(output$tacc_details) + 3
  
  writeData(wb, sheet = 2, "Mismatch details from SPC monthly tables", startCol = 1, startRow = next_row)
  writeData(wb, sheet = 2, output$spc_details, startCol = 1, startRow = next_row+1)
  next_row = next_row + nrow(output$spc_details) + 4
}

print("Writing mismatches for race")

#Write mismatches for race
next_row = 3 #reset next_row
for (i in 1:min(nrow(race_mismatches), records_to_print)){
  current_mismatch = race_mismatches[i,]
  output = get_mismatch_info(current_mismatch)
  
  writeData(wb, sheet = 3, "Mismatch details from yearly tables", startCol = 1, startRow = next_row)
  writeData(wb, sheet = 3, output$mismatch_details, startCol = 1, startRow = next_row + 1)
  next_row = next_row + nrow(output$mismatch_details) + 3
  
  writeData(wb, sheet = 3, "Mismatch details from TACC dw_staging monthly table",
            startCol = 1, startRow = next_row)
  writeData(wb, sheet = 3, output$tacc_details, startCol = 1, startRow = next_row+1)
  next_row = next_row + nrow(output$tacc_details) + 3
  
  writeData(wb, sheet = 3, "Mismatch details from SPC monthly tables", startCol = 1, startRow = next_row)
  writeData(wb, sheet = 3, output$spc_details, startCol = 1, startRow = next_row+1)
  next_row = next_row + nrow(output$spc_details) + 4
}

print("Writing mismatches for zip")

#Write mismatches for zip
next_row = 3 #reset next_row
for (i in 1:min(nrow(zip_mismatches), records_to_print)){
  current_mismatch = zip_mismatches[i,]
  output = get_mismatch_info(current_mismatch)
  
  writeData(wb, sheet = 4, "Mismatch details from yearly tables", startCol = 1, startRow = next_row)
  writeData(wb, sheet = 4, output$mismatch_details, startCol = 1, startRow = next_row + 1)
  next_row = next_row + nrow(output$mismatch_details) + 3
  
  writeData(wb, sheet = 4, "Mismatch details from TACC dw_staging monthly table",
            startCol = 1, startRow = next_row)
  writeData(wb, sheet = 4, output$tacc_details, startCol = 1, startRow = next_row+1)
  next_row = next_row + nrow(output$tacc_details) + 3
  
  writeData(wb, sheet = 4, "Mismatch details from SPC monthly tables", startCol = 1, startRow = next_row)
  writeData(wb, sheet = 4, output$spc_details, startCol = 1, startRow = next_row+1)
  next_row = next_row + nrow(output$spc_details) + 4
}

print("Writing mismatches for plan type")

#Write mismatches for plan type
next_row = 3 #reset next_row
for (i in 1:min(nrow(plan_mismatches), records_to_print)){
  current_mismatch = plan_mismatches[i,]
  output = get_mismatch_info(current_mismatch)
  
  writeData(wb, sheet = 5, "Mismatch details from yearly tables", startCol = 1, startRow = next_row)
  writeData(wb, sheet = 5, output$mismatch_details, startCol = 1, startRow = next_row + 1)
  next_row = next_row + nrow(output$mismatch_details) + 3
  
  writeData(wb, sheet = 5, "Mismatch details from TACC dw_staging monthly table",
            startCol = 1, startRow = next_row)
  writeData(wb, sheet = 5, output$tacc_details, startCol = 1, startRow = next_row+1)
  next_row = next_row + nrow(output$tacc_details) + 3
  
  writeData(wb, sheet = 5, "Mismatch details from SPC monthly tables", startCol = 1, startRow = next_row)
  writeData(wb, sheet = 5, output$spc_details, startCol = 1, startRow = next_row+1)
  next_row = next_row + nrow(output$spc_details) + 4
}


setColWidths(wb, sheet = 1, cols=1:10, widths="auto")

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```

# SECTION 99: Close connections and clean-up

```{sql connection = spc, eval=FALSE}
drop table if exists work.dbo.xz_dwqa_temp1;
drop table if exists work.dbo.xz_mcd_enrl_mismatches;

```

```{r close-connections, eval=FALSE}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env, eval=FALSE}
# clears R environment
rm(list=ls())
```



