---
title: "dw-rx-counting-pt2"
author: "XRZ"
date: '2022-11-22'
output: html_document
---

#PURPOSE
This R markdown script counts distinct rx from TACC tables

# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

#packages I don't use anymore: rstudioapi

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password


#Connect to Greenplum
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(),
	 dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc")))
```

## 0.5 Set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation

```

#DOWNLOAD SELECTION OF RX_IDS FROM SPC, UPLOAD TO TACC

```{sql, connection = spc, output.var = temp}
select top 1000 fy, 'chip' as src_table, rx_id from work.dbo.xz_dwqa_chiprx tablesample(2000 rows);

select top 1000 fy, 'ffs' as src_table, rx_id from work.dbo.xz_dwqa_ffsrx tablesample(2000 rows);

select top 1000 fy, 'mco' as src_table, rx_id from work.dbo.xz_dwqa_mcorx tablesample(2000 rows);

```

```{r}
#write to tacc

dbWriteTable(tac, SQL("dev.xz_dwqa_temp"), temp, overwrite = TRUE)

```

#DOWNLOAD LISTS OF PCN-NDC-DT AND UPLOADS TO TACC BASED ON YEAR AND TABLE

```{r}
#define base queries
spc_sql = 'select \'20@yr\' as fy, concat(pcn, ndc, replace(rx_fill_dt, \'-\', \'\')) as rx_id
into work.dbo.xz_dwqa_rxid_list
from medicaid.dbo.@table_rx_fy@yr;'

```

```{r}
#define year and table
yr = 12
table = "ffs"

#modify queries
spc_sql.mod = spc_sql %>% gsub('@yr', yr, .) %>% gsub('@table', table, .)

tic("Pulling rx_ids from SPC")
dbGetQuery(spc, 'drop table if exists work.dbo.xz_dwqa_rxid_list;')
dbGetQuery(spc, spc_sql.mod)
rxid_list = dbGetQuery(spc, "select distinct * from work.dbo.xz_dwqa_rxid_list;")
toc()
#2 mins for FFS 2012


#write to tacc
tic("Writing to TACC")
dbWriteTable(tac, SQL("dev.xz_dwqa_rxid_list"), rxid_list, overwrite = TRUE)
toc()

```


```{r}
#sample from HTW
spc_sql2 = 'select \'HTW\' as fy, concat(pcn, ndc, replace(rx_fill_dt, \'-\', \'\')) as rx_id
into work.dbo.xz_dwqa_rxid_list
from medicaid.dbo.FFS_RX_FY18_19_HTW;'

```

```{r}

tic("Pulling rx_ids from SPC - HTW table")
dbGetQuery(spc, 'drop table if exists work.dbo.xz_dwqa_rxid_list;')
dbGetQuery(spc, spc_sql2)
rxid_list = dbGetQuery(spc, "select distinct * from work.dbo.xz_dwqa_rxid_list;")
toc()
#2 mins for FFS 2012


#write to tacc
tic("Writing to TACC")
dbWriteTable(tac, SQL("dev.xz_dwqa_rxid_list"), rxid_list, overwrite = TRUE)
toc()

```






#SECTION 99: Delete temp tables, Close connections, clear R environment

```{r close-connections, eval = FALSE}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env, eval = FALSE}
# clears R environment
rm(list=ls())
```
