---
title: "dwqa-truven-pharmacy-claim-counts"
author: "XRZ"
date: '2023-01-12'
output: html_document
---

#Purpose:
This R markdown script examines the accuracy of conversions from raw source tables to
data_warehouse tables


# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password

# Function for connecting to TACC/Greenplum
# TACC kicks you out for inactivity so just call function before connections
connect_to_tacc <- function() {
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
}

```

## 0.3 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("connect_to_tacc")))
```

## 0.5 Set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation
here::i_am("06-rx-counts.Rmd")
```

# SECTION 1: Get counts
## 1.1 Get counts from TRUVEN RAW COUNTS table
```{r}

# Check to see if raw counts for Truven exists

path = here("outputs", "truven-raw-counts.xlsx")

if (!file.exists(path)) {

 print("Missing counts from Truven schema! Go back and run 02-truven-schema-counts.Rmd")

} else {
  
  truv_rx_in = read.xlsx(path, sheet = 6, startRow = 4, rows=c(4:16),
                             colNames = TRUE, rowNames = FALSE)
  
}

```

## 1.1 Base SQL queries for modification
```{r}

# RX table is surprisingly not huge so we don't need to split into years

list_of_tables_rx = c("ccaed", "mdcrd")

#sql query to get rx_claim_id_src from dw to a temp table by table_id_src (dw)
dw_sql1 = "create table dev.xz_dwqa_temp as
  select year, table_id_src, rx_claim_id_src as rx_id from dw_staging.pharmacy_claims
  where table_id_src = '@table'
  distributed by (rx_id);"

#sql query to count unique enrolid || msclmids (dw)
dw_sql2 = "select year, table_id_src, count(distinct rx_id) from dev.xz_dwqa_temp
  group by year, table_id_src;"

```

## 1.2 Get counts of distinct claim ids
```{r}


tac = connect_to_tacc()

for (i in 1:2){
  
  # we count in pieces bc otherwise the query takes too long
  dbExecute(tac, "drop table if exists dev.xz_dwqa_temp;")
  
  current_table = list_of_tables_rx[i]
  
  # modify sql query to grab only the rx_ids for one table
  dw_sql1.mod = dw_sql1 %>% gsub("@table", current_table, .)
  
  # make temp table with rx_ids
  tic(paste("Making temp table for", current_table))
  dbExecute(tac, dw_sql1.mod)
  toc()
  
  # count distinct rx_ids for one table
  tic(paste("Counting distinct rx_ids for", current_table))
  
  current_results = dbGetQuery(tac, dw_sql2)
  
  toc()
  
  if (i == 1) {
    dw_concat_counts = current_results
  } else {
    dw_concat_counts = rbind(dw_concat_counts, current_results)
  }
}

  
```

# SECTION 2: Make table

## 2.1 Make table for distinct enrolid-clmid combos
```{r}
#make dw long table more wide - each column is a table_id_src

for (i in 1:2){
  current_table = list_of_tables_rx[i]
  newcolname = paste0("dw_rx_", current_table)
  
  current = dw_concat_counts %>%
    filter(table_id_src == current_table) %>%
    rename(!!newcolname := count) %>%
    select(-table_id_src) %>%
    arrange(year)
  
  if (i==1) {
    dw_concat_tbl = current
  } else {
    dw_concat_tbl = dw_concat_tbl %>%
    left_join(current, by = "year")
  }
}

# make raw truven counts int int bc apparently it imported as chr
truv_rx_in$truv_rx_ccaed = as.integer(truv_rx_in$truv_rx_ccaed)
truv_rx_in$truv_rx_mdcrd = as.integer(truv_rx_in$truv_rx_mdcrd)

# combine truven raw counts with dw counts

all_concat_tbl = dw_concat_tbl %>%
  left_join(truv_rx_in, by = "year") %>%
  mutate(diff_ccaed = truv_rx_ccaed - dw_rx_ccaed,
         diff_mdcrd = truv_rx_mdcrd - dw_rx_mdcrd) %>%
  mutate(ccaed_pct = diff_ccaed/truv_rx_ccaed,
         mdcrd_pct = diff_mdcrd/truv_rx_mdcrd) %>%
  arrange(year)

```

# SECTION 3: Output to spreadsheet
```{r}

wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "truven-pharmacy-claims-counting.xlsx")

addWorksheet(wb, sheetName="distinct-rx-ids")

#sheet 1
current_sheet = 1; current_df = all_concat_tbl
writeData(wb, sheet = current_sheet,
          "Count of distinct enrolid || ndcnum || svcdate in data_warehouse and Truven schema on TACC server",
          startCol=1, startRow=1)
writeData(wb, sheet = current_sheet, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = current_sheet, current_df, startCol=1, startRow=4)
nextrow = nrow(current_df) + 6

# writeData(wb, sheet=current_sheet,
#           "Note: the higher number in 2021 is probably because we didn't add enrolids that # don't exist in 'a' but exist in the claim tables to dim_uth_member_id", startCol=1, startRow = nextrow)

setColWidths(wb, sheet = current_sheet, cols=1:ncol(current_df)+1, widths="auto")
setColWidths(wb, sheet = current_sheet, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```

