---
title: "dw-enrollment-check"
author: "XRZ"
date: '2022-10-26'
output: html_document
---

#Purpose:
This R markdown script examines the accuracy of conversions from raw source tables to
data_warehouse tables

It counts:
  distinct members
  distinct member-year-month combinations
  
Counted from:
  SPCDEDPWPVS1 server
  TACC server medicaid schema
  TACC server dw_staging.mcd_member_enrollment_monthly
  TACC server dw_staging.mcd_member_enrollment_yearly
  TACC server dw_staging.mcd_member_enrollment_fiscal_yearly
  
09/05/2023: Updated for changed table names (added mcd prefix)
            TACC connection is now a function
            Converted to RPostgres but in the process broke some stuff
            It's fine nbd I fixed it
            Added code for fiscal yearly table
            Updated for 2022

# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password


#Connect to Greenplum
connect_to_tacc <- function() {
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
}
```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(),
	 dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc", "connect_to_tacc")))
```

## 0.5 Set misc options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
here::i_am("00-dw-enrollment-qa.rmd")

```

# SECTION 1: Define global variables

```{r}
#Define the starting and ending years for checking (4-digit year)

starting_year = 2016
ending_year = 2022

starting_yr = starting_year - 2000
ending_yr = ending_year - 2000

starting_fymon = (starting_year-1)*100+9
ending_fymon = ending_year*100+8

```

# SECTION 2: Build tables of distinct member-year-month combos
## 2.0 Initialize TACC connection
```{r}
tac = connect_to_tacc()

```


## 2.1 Build table from data_warehouse monthly table
```{r}
dbExecute(tac, "drop table if exists dev.xz_dwqa_temp1;")
dbExecute(tac, "select distinct member_id_src, month_year_id
into dev.xz_dwqa_temp1
from dw_staging.mcd_member_enrollment_monthly;")
```


## 2.2 Build table from data_warehouse yearly table

```{sql, connection = tac}
drop table if exists dev.xz_dwqa_temp2;
```
```{sql, connection = tac}
select *
into dev.xz_dwqa_temp2
from
	(select member_id_src, year::text || '01' from dw_staging.mcd_member_enrollment_yearly as month_year_id where enrolled_jan = 1
	union select member_id_src, year::text || '02' from dw_staging.mcd_member_enrollment_yearly where enrolled_feb = 1
	union select member_id_src, year::text || '03' from dw_staging.mcd_member_enrollment_yearly where enrolled_mar = 1
	union select member_id_src, year::text || '04' from dw_staging.mcd_member_enrollment_yearly where enrolled_apr = 1
	union select member_id_src, year::text || '05' from dw_staging.mcd_member_enrollment_yearly where enrolled_may = 1
	union select member_id_src, year::text || '06' from dw_staging.mcd_member_enrollment_yearly where enrolled_jun = 1
	union select member_id_src, year::text || '07' from dw_staging.mcd_member_enrollment_yearly where enrolled_jul = 1
	union select member_id_src, year::text || '08' from dw_staging.mcd_member_enrollment_yearly where enrolled_aug = 1
	union select member_id_src, year::text || '09' from dw_staging.mcd_member_enrollment_yearly where enrolled_sep = 1
	union select member_id_src, year::text || '10' from dw_staging.mcd_member_enrollment_yearly where enrolled_oct = 1
	union select member_id_src, year::text || '11' from dw_staging.mcd_member_enrollment_yearly where enrolled_nov = 1
	union select member_id_src, year::text || '12' from dw_staging.mcd_member_enrollment_yearly where enrolled_dec = 1) z;
```

## 2.2 Build table from data_warehouse fiscal yearly table

```{sql, connection = tac}
drop table if exists dev.xz_dwqa_temp3;
```
```{sql, connection = tac}
select *
into dev.xz_dwqa_temp3
from
	(select member_id_src, fiscal_year::text || '01' as month_year_id from dw_staging.mcd_member_enrollment_fiscal_yearly  where enrolled_jan = 1
	union select member_id_src, fiscal_year::text || '02' from dw_staging.mcd_member_enrollment_fiscal_yearly where enrolled_feb = 1
	union select member_id_src, fiscal_year::text || '03' from dw_staging.mcd_member_enrollment_fiscal_yearly where enrolled_mar = 1
	union select member_id_src, fiscal_year::text || '04' from dw_staging.mcd_member_enrollment_fiscal_yearly where enrolled_apr = 1
	union select member_id_src, fiscal_year::text || '05' from dw_staging.mcd_member_enrollment_fiscal_yearly where enrolled_may = 1
	union select member_id_src, fiscal_year::text || '06' from dw_staging.mcd_member_enrollment_fiscal_yearly where enrolled_jun = 1
	union select member_id_src, fiscal_year::text || '07' from dw_staging.mcd_member_enrollment_fiscal_yearly where enrolled_jul = 1
	union select member_id_src, fiscal_year::text || '08' from dw_staging.mcd_member_enrollment_fiscal_yearly where enrolled_aug = 1
	union select member_id_src, (fiscal_year-1)::text || '09' from dw_staging.mcd_member_enrollment_fiscal_yearly where enrolled_sep = 1
	union select member_id_src, (fiscal_year-1)::text || '10' from dw_staging.mcd_member_enrollment_fiscal_yearly where enrolled_oct = 1
	union select member_id_src, (fiscal_year-1)::text || '11' from dw_staging.mcd_member_enrollment_fiscal_yearly where enrolled_nov = 1
	union select member_id_src, (fiscal_year-1)::text || '12' from dw_staging.mcd_member_enrollment_fiscal_yearly where enrolled_dec = 1) z;
```


## 2.4 Build table from medicaid schema (TACC)
```{sql, connection = tac}
drop table if exists dev.xz_dwqa_temp4;
```
```{sql, connection = tac}
select distinct client_nbr, elig_date
into dev.xz_dwqa_temp4
from (select client_nbr, elig_date from medicaid.enrl union
    select client_nbr, elig_month from medicaid.chip_enrl union
    select client_nbr, elig_date from medicaid.htw_enrl) z;
```

## 2.5 Build table from SPC
```{r}

sql1 = 'insert into chcdwork.dbo.xz_dwqa_temp1 select distinct client_nbr, elig_date
      from medicaid.dbo.enrl_@year;'

sql2 = 'insert into chcdwork.dbo.xz_dwqa_temp1 select distinct client_nbr, elig_month
      from medicaid.dbo.CHIP_ENRL_FY@yr;'

dbGetQuery(spc, 'drop table if exists chcdwork.dbo.xz_dwqa_temp1;') #drop table if exists
dbGetQuery(spc, 'select * into chcdwork.dbo.xz_dwqa_temp1
    from (select client_nbr, elig_date from medicaid.dbo.ENRL_2018_HTW union
    select client_nbr, elig_date from medicaid.dbo.ENRL_2019_HTW) z;') #initialize using HTW tables

for (year in starting_year:ending_year){
  yr = year - 2000
  
  print(paste('Processing', year))
  
  sql1.mod = sql1 %>% gsub('@year', year, .)
  sql2.mod = sql2 %>% gsub('@yr', yr, .)
  
  dbGetQuery(spc, sql1.mod)
  dbGetQuery(spc, sql2.mod)
}

```


# SECTION 3: Counting

## 3.1 Do the actual counting
```{r}
#base TACC queries
tac_sql1 = "select count(distinct member_id_src) from dev.xz_dwqa_temp1
            where month_year_id between @starting_fymon and @ending_fymon;"

tac_sql2 = "select count(distinct member_id_src) from dev.xz_dwqa_temp2
            where month_year_id::int between @starting_fymon and @ending_fymon;"

tac_sql3 = "select count(distinct member_id_src) from dev.xz_dwqa_temp3
            where month_year_id::int between @starting_fymon and @ending_fymon;"

tac_sql4 = "select count(distinct client_nbr) from dev.xz_dwqa_temp4
            where elig_date::int between @starting_fymon and @ending_fymon;"

tac_sql5 = "select count(*) from dev.xz_dwqa_temp1
          where month_year_id between @starting_fymon and @ending_fymon;"

tac_sql6 = "select count(*) from dev.xz_dwqa_temp2
          where month_year_id::int between @starting_fymon and @ending_fymon;"

tac_sql7 = "select count(*) from dev.xz_dwqa_temp3
          where month_year_id::int between @starting_fymon and @ending_fymon;"

tac_sql8 = "select count(*) from dev.xz_dwqa_temp4
          where elig_date::int between @starting_fymon and @ending_fymon;"

#mod TACC queries so they only count the years of interest
tac_sql1.mod = tac_sql1 %>% gsub("@starting_fymon", starting_fymon, .) %>% gsub("@ending_fymon", ending_fymon, .)
tac_sql2.mod = tac_sql2 %>% gsub("@starting_fymon", starting_fymon, .) %>% gsub("@ending_fymon", ending_fymon, .)
tac_sql3.mod = tac_sql3 %>% gsub("@starting_fymon", starting_fymon, .) %>% gsub("@ending_fymon", ending_fymon, .)
tac_sql4.mod = tac_sql4 %>% gsub("@starting_fymon", starting_fymon, .) %>% gsub("@ending_fymon", ending_fymon, .)
tac_sql5.mod = tac_sql5 %>% gsub("@starting_fymon", starting_fymon, .) %>% gsub("@ending_fymon", ending_fymon, .)
tac_sql6.mod = tac_sql6 %>% gsub("@starting_fymon", starting_fymon, .) %>% gsub("@ending_fymon", ending_fymon, .)
tac_sql7.mod = tac_sql7 %>% gsub("@starting_fymon", starting_fymon, .) %>% gsub("@ending_fymon", ending_fymon, .)
tac_sql8.mod = tac_sql8 %>% gsub("@starting_fymon", starting_fymon, .) %>% gsub("@ending_fymon", ending_fymon, .)

dw_monthly_memcount = dbGetQuery(tac, tac_sql1.mod)
dw_yearly_memcount = dbGetQuery(tac, tac_sql2.mod)
dw_fyearly_memcount = dbGetQuery(tac, tac_sql3.mod)
tac_monthly_memcount = dbGetQuery(tac, tac_sql4.mod)
spc_monthly_memcount = dbGetQuery(spc, "select count(distinct client_nbr) from chcdwork.dbo.xz_dwqa_temp1;")

dw_monthly_combocount = dbGetQuery(tac, tac_sql5.mod)
dw_yearly_combocount = dbGetQuery(tac, tac_sql6.mod)
dw_fyearly_combocount = dbGetQuery(tac, tac_sql7.mod)
tac_monthly_combocount = dbGetQuery(tac, tac_sql8.mod)
spc_monthly_combocount = dbGetQuery(spc, "with cte as (select distinct client_nbr, elig_date from chcdwork.dbo.xz_dwqa_temp1)
                                    select count(*) from cte;")

```

## 3.2 Make tables
```{r}
#list sources
source_list = c("Data_warehouse Monthly Enrollment Table",
                "Data_warehouse Yearly Enrollment Table",
                "Data_warehouse Fiscal Yearly Enrollment Table",
                "TACC server medicaid schema",
                "SPC server medicaid schema")

#compose numbers into table (distinct members)
distinct_members = c(dw_monthly_memcount[1,1], dw_yearly_memcount[1,1], dw_fyearly_memcount[1,1],
                     tac_monthly_memcount[1,1], spc_monthly_memcount[1,1])

#compose numbers into table (distinct member-year-month combos)
distinct_combos = c(dw_monthly_combocount[1,1], dw_yearly_combocount[1,1], dw_fyearly_combocount[1,1],
                     tac_monthly_combocount[1,1], spc_monthly_combocount[1,1])

colnames = c("Distinct Members", "Distinct Member-Year-Month combinations")

output_table = data.frame(source_list, distinct_members, distinct_combos)


```

## 3.3 Make spreadsheet
```{r}

wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "dw-enrollment-qa.xlsx")
here()

addWorksheet(wb, sheetName = "dw enrollment qa")

writeData(wb, sheet = 1, "Data Warehouse Enrollment Tables QA", startCol=1, startRow=1)
writeData(wb, sheet = 1, paste("Run date:", Sys.Date()), startCol=1, startRow=2)
writeData(wb, sheet = 1, output_table, startCol=1, startRow=4)

setColWidths(wb, sheet = 1, cols=1:3, widths="auto")

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```
# SECTION 4: Output to spreadsheet

# SECTION 99: Close connections and clean-up

```{sql connection = spc, eval=FALSE}
drop table if exists chcdwork.dbo.xz_dwqa_temp1;

```

```{sql connection = tac, eval=FALSE}
drop table if exists dev.xz_dwqa_temp1;
drop table if exists dev.xz_dwqa_temp2;
drop table if exists dev.xz_dwqa_temp3;

```

```{r close-connections, eval=FALSE}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env, eval=FALSE}
# clears R environment
rm(list=ls())
```



