---
title: "dw-claims-counting-pt2"
author: "XRZ"
date: '2022-10-24'
output: html_document
---

#PURPOSE
This R markdown script counts distinct claims from TACC tables


11/31/22 Modifications:
  * changed connection method for Greenplum from odbc to RPostgres
  * Modified SQL sections so that each section only contains 1 statement
    (this is required after changing connection method to RPostgres)
  * Other misc sequelae of changing connection method
  
09/12/23 Modifications:
  * In section 4.2, the code to prep dw_staging for joining was modified to use 
    dwstage_head_comb and dwstage_det_comb instead of dwstage_head and dwstage_det. 
    Additionally, the location to place 'Total' within the dwstage_head_prep df and 
    dwstage_det_prep df was changed. 
  


# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

#packages I don't use anymore: rstudioapi

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password


#Connect to Greenplum
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "sharrah17",
	 password = key_get("Greenplum", "sharrah17"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(),
	 dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc")))
```

## 0.5 Set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation

```

# SECTION 1: Read in runs from previous code

## 1.1 Read in output if it exists
```{r}
#SPC server shouldn't have major changes year to year, so if output exists already
#use that

path = here("outputs", "spc-claims-counting.xlsx")

if (file.exists(path)) {

spc_counts = read.xlsx(path, sheet=1, startRow = 4)

} else {
  stop("Output is missing! Go back and run the previous code file!")
}

```

## 1.2 Define global variables
```{r}
#define starting and ending year
starting_year = 2016
ending_year = 2022

#conver to 2-digit year
starting_yr = starting_year - 2000
ending_yr = ending_year - 2000

```

# SECTION 2: Count distinct claims from medicaid schema on TACC

## 2.1 From headers
```{sql, connection = tac, output.var = TACCmcd_clm_head}
--get distinct ICNs from medicaid schema (TACC) by year claims
select a.year_fy::text, count(distinct a.icn) as count
from medicaid.clm_header a inner join medicaid.clm_proc b
	on a.icn = b.icn
group by a.year_fy
order by a.year_fy;

```

```{sql, connection = tac, output.var = TACCmcd_enc_head}
--get distinct ICNs from medicaid schema (TACC) by year encounters
select a.year_fy::text, count(distinct a.derv_enc) as count
from medicaid.enc_header a inner join medicaid.enc_proc b
	on a.derv_enc = b.derv_enc 
group by a.year_fy
order by a.year_fy;
```

```{sql, connection = tac, output.var = TACCmcd_htw_head}
--get distinct ICNs from htw_clms
select 'HTW' as year_fy, count(distinct a.icn) as count
from medicaid.htw_clm_detail a inner join medicaid.htw_clm_proc b
  on a.icn = b.icn;
```

```{sql, connection = tac, output.var = TACCmcd_total_head}
--get distinct ICNs from medicaid schema (TACC, Total)
select 'Total' as year_fy, count(distinct a.icn) as count
from (select icn from medicaid.clm_header
	union all select derv_enc from medicaid.enc_header
	union all select icn from medicaid.htw_clm_header) a
	 inner join
	 (select icn from medicaid.clm_proc
	union select derv_enc from medicaid.enc_proc
	union select icn from medicaid.htw_clm_proc) b
	on a.icn = b.icn;
```

## 2.2 From details
```{sql, connection = tac, output.var = TACCmcd_clm_det}
--get distinct ICNs from medicaid schema (TACC) by year claims
select a.year_fy::text, count(distinct a.icn) as count
from medicaid.clm_detail a inner join medicaid.clm_proc b
	on a.icn = b.icn
group by a.year_fy
order by a.year_fy;

```

```{sql, connection = tac, output.var = TACCmcd_enc_det}
--get distinct ICNs from medicaid schema (TACC) by year encounters
select a.year_fy::text, count(distinct a.derv_enc) as count
from medicaid.enc_det a inner join medicaid.enc_proc b
	on a.derv_enc = b.derv_enc 
group by a.year_fy
order by a.year_fy;
```

```{sql, connection = tac, output.var = TACCmcd_htw_det}
--get distinct ICNs from htw_clms
select 'HTW' as year_fy, count(distinct a.icn) as count
from medicaid.htw_clm_detail a inner join medicaid.htw_clm_proc b
  on a.icn = b.icn;
```

```{sql, connection = tac, output.var = TACCmcd_total_det}
--get distinct ICNs from medicaid schema (TACC, Total)
select 'Total' as year_fy, count(distinct a.icn) as count
from (select icn from medicaid.clm_detail
	union all select derv_enc from medicaid.enc_det
	union all select icn from medicaid.htw_clm_detail) a
	 inner join
	 (select icn from medicaid.clm_proc
	union select derv_enc from medicaid.enc_proc
	union select icn from medicaid.htw_clm_proc) b
	on a.icn = b.icn;
```

# SECTION 3: Count distinct claims from dw_staging schema on TACC

## 3.1 From headers
```{sql, connection = tac, output.var = dwstage_head}

--gets distinct ICNs from data_warehouse by year
select fiscal_year::text, count(distinct claim_id_src)
from dw_staging.mcd_claim_header
group by fiscal_year
order by fiscal_year; 

```

```{sql, connection = tac, output.var = dwstage_head_total}
--gets distinct ICNs from data_warehouse (Total)
select 'all' as fiscal_year, count(distinct claim_id_src)
from dw_staging.mcd_claim_header;

```

## 3.2 From details
```{sql, connection = tac, output.var = dwstage_det}

--gets distinct ICNs from data_warehouse by year
select fiscal_year::text, count(distinct claim_id_src)
from dw_staging.mcd_claim_detail
group by fiscal_year
order by fiscal_year; 

```

## 3.2 From details
```{sql, connection = tac, output.var = dwstage_det_total}
--gets distinct ICNs from data_warehouse (Total)
select 'all' as fiscal_year, count(distinct claim_id_src)
from dw_staging.mcd_claim_detail;

```

# SECTION 4: Compile it all into a table and compare

## 4.1 rbind in totals for data_warehouse
```{r}

dwstage_det_comb = rbind(dwstage_det, dwstage_det_total)
dwstage_head_comb = rbind(dwstage_head, dwstage_head_total)

```

## 4.2 Complile table for TACC medicaid schema
```{r}
#join in yearly counts
claim_counts_TACCmcd = full_join(TACCmcd_clm_head, TACCmcd_clm_det, by = 'year_fy') %>%
  rename(CLM_HEAD = count.x, CLM_DET = count.y) %>%
  full_join(., TACCmcd_enc_head, by = 'year_fy') %>%
  rename(ENC_HEAD = count) %>%
  full_join(., TACCmcd_enc_det, by = 'year_fy') %>%
  rename(ENC_DET = count)

#fix ENC_HEAD and ENC_DET for 2012
claim_counts_TACCmcd[1, 4] = claim_counts_TACCmcd[1, 5] = 0

#prep HTW for joining in
claim_counts_TACCmcd_htw = full_join(TACCmcd_htw_head, TACCmcd_htw_det, by = 'year_fy') %>%
    rename(CLM_HEAD = count.x, CLM_DET = count.y) %>%
    add_column(ENC_HEAD = 0, ENC_DET = 0)

#prep totals count for joining in
claim_counts_TACCmcd_total = full_join(TACCmcd_total_head, TACCmcd_total_det, by = 'year_fy') %>%
  rename(TACmcd_HEAD = count.x, TACmcd_DET = count.y) %>%
  add_column(CLM_HEAD = 0, CLM_DET = 0, ENC_HEAD = 0, ENC_DET = 0) %>%
  select(year_fy, CLM_HEAD, CLM_DET, ENC_HEAD, ENC_DET, TACmcd_HEAD, TACmcd_DET)

#join in HTW, TOTALs counts and calculate totals
claim_counts_TACCmcd = claim_counts_TACCmcd %>%
  rbind(., claim_counts_TACCmcd_htw) %>%
  mutate(TACmcd_HEAD = CLM_HEAD + ENC_HEAD,
         TACmcd_DET = CLM_DET + ENC_DET) %>%
  rbind(., claim_counts_TACCmcd_total)

#prep dw_staging for joining
dwstage_head_prep = dwstage_head_comb
dwstage_det_prep = dwstage_det_comb
dwstage_head_prep[length(dwstage_head_prep$fiscal_year),1] = 'Total'
dwstage_det_prep[length(dwstage_det_prep$fiscal_year),1] = 'Total'
colnames(dwstage_head_prep)=c('year_fy', 'DW_HEAD')
colnames(dwstage_det_prep)=c('year_fy', 'DW_DET')

#join in dw_staging counts
claim_counts_TACC = claim_counts_TACCmcd %>%
  full_join(., dwstage_head_prep, by = 'year_fy') %>%
  full_join(., dwstage_det_prep, by = 'year_fy')

#prep spc_counts for merge
spc_counts_merge = spc_counts %>%
  mutate(SPC_HEAD = CLM_HEAD + ENC_HEAD,
         SPC_DET = CLM_DET + ENC_DET) %>%
  rename(year_fy = Year) %>%
  select(year_fy, SPC_HEAD, SPC_DET)

#join in dw_staging counts
claim_counts_TACC = claim_counts_TACC %>%
  full_join(., spc_counts_merge, by = 'year_fy')

#replace na with 0
claim_counts_TACC[is.na(claim_counts_TACC)] = 0

#see if there are differenes
count_diffs = claim_counts_TACC %>%
  mutate(DW_V_TACm_HEAD = TACmcd_HEAD - DW_HEAD,
         DW_V_TACm_DET = TACmcd_DET - DW_DET) %>%
  add_column(spacer1 = NA, spacer2 = NA) %>%
   mutate(DW_V_SPC_HEAD = SPC_HEAD - DW_HEAD,
         DW_V_SPC_DET = SPC_DET - DW_DET) %>%
  select(year_fy, 12:17)

#subset for output
claim_counts_TACC_out = claim_counts_TACC %>%
  select(year_fy, 6:11)

```



# SECTION 5: Output to spreadsheet
## 5.1 Make table legend

```{r}
#make table legends so we know what the columns are

column_name = colnames(claim_counts_TACC_out)
description <- c( "Fiscal Year",
                  "Count of distinct claims in TACC medicaid schema - headers",
                  "Count of distinct claims in TACC medicaid schema - details",
                  "Count of distinct claims in dw_staging.claim_header",
                  "Count of distinct claims in dw_staging.claim_detail",
                  "Count of distinct claims in SPC medicaid schema headers joined to procs",
                  "Count of distinct claims in SPC medicaid schema details joined to procs")
table_legend <- data.frame(column_name, description)
colnames(table_legend) = c("Column Name", "Description")
```

## 5.2 Output to spreadsheet
```{r}
wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "dw-staging-claims-counting.xlsx")

addWorksheet(wb, sheetName = "Count of distinct claims")

writeData(wb, sheet = 1, "Count of distinct claims across SPC and TACC servers (DW Staging)", startCol=1, startRow=1)
writeData(wb, sheet = 1, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = 1, claim_counts_TACC_out, startCol=1, startRow=4)
nextrow = nrow(claim_counts_TACC_out) + 6
writeData(wb, sheet = 1, "Difference between counts (Raw data count - DW count)", startCol=1, startRow=nextrow)
writeData(wb, sheet = 1, count_diffs, startCol=1, startRow=nextrow + 1)

#overwrite the spacer columns
writeData(wb, sheet = 1, '', startCol=4, startRow=nextrow + 1)
writeData(wb, sheet = 1, '', startCol=5, startRow=nextrow + 1)

#write the legend
nextrow = nextrow + nrow(count_diffs) + 3
writeData(wb, sheet = 1, table_legend, startCol=1, startRow=nextrow)

#write notes
nextrow = nextrow + nrow(table_legend) + 3
writeData(wb, sheet = 1, "Notes:", startCol=1, startRow=nextrow)
nextrow = nextrow + 1
writeData(wb, sheet = 1, "The 124 claims difference in 2016 is due to joining proc, details, and headers - the missing claims do not exist in the header table", startCol=1, startRow=nextrow)
nextrow = nextrow + 1
writeData(wb, sheet = 1, "The discrepancy in 2018 is largely due to HTW claims", startCol=1, startRow=nextrow)
nextrow = nextrow + 1
writeData(wb, sheet = 1, "HTW discrepancy: see 2018", startCol=1, startRow=nextrow)

#set colwidths
setColWidths(wb, sheet = 1, cols=1:ncol(claim_counts_TACC_out)+1, widths="auto")
setColWidths(wb, sheet = 1, cols=1:2, widths=c(15, 15))

#save to file
dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```


#SECTION 99: Delete temp tables, Close connections, clear R environment

```{r close-connections, eval = FALSE}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env, eval = FALSE}
# clears R environment
rm(list=ls())
```
