---
title: "dw-claims-details-qa"
author: "XRZ"
date: '2022-10-24'
output: html_document
---

# PURPOSE
This R markdown script spot checks for matching details information in dw_staging

09/13/23: updated for FY22
  changed work -> chcdwork
  changed dw_staging.claim_detail -> dw_staging.mcd_claim_detail
  changed all temp tables to be named xz_dwqa15_temp so they don't interfere with other QA scripts if run concurrently

# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requiring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password


#Connect to Greenplum
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(),
	 dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc")))
```

## 0.5 Set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation
here::i_am("15-dw-claims-details-spotcheck.rmd")
```

# SECTION 1: Declare global variables
```{r}
#Define the starting and ending years for checking (4-digit year)
starting_year = 2012
ending_year = 2022

#Define how many rows to check - will check this many rows 
#from each of the clm and enc tables so double this number
#for rows checked per year (except for 2012)
rows_to_check = 5000

#convert to 2-digit year
starting_yr = starting_year - 2000
ending_yr = ending_year - 2000
```

# SECTION 2: Randomly select rows from SPC details tables and uploads to TACC
## 2.1 Define base queries
```{r}
#set rows_to_sample as slightly higher than rows to check b/c of
#the funny way that tablesample works
rows_to_sample = as.integer(rows_to_check) * 1.2

#select random rows from the claims table
spc_sql1 = "select top @rows_to_check  '20@yr' as spc_fy,
a.clm_dtl_nbr as spc_claim_sequence_number,
a.from_dos as spc_from_date_of_service,
a.to_dos as spc_to_date_of_service,
a.pos as spc_place_of_service,
a.proc_cd as spc_cpt_hcpcs_cd,
a.sub_proc_cd,
a.proc_mod_1 as spc_proc_mod_1,
a.proc_mod_2 as spc_proc_mod_2,
a.rev_cd as spc_revenue_cd,
a.dtl_bill_amt as spc_charge_amount,
a.dtl_alwd_amt as spc_allowed_amount,
a.dtl_pd_amt as spc_paid_amount,
a.ref_prov_npi as spc_ref_provider,
a.perf_prov_npi as spc_perf_rn_provider,
'          ' as spc_perf_op_provider,
a.txm_cd as spc_provider_type,
b.adm_dt as spc_admit_date,
b.dis_dt as spc_discharge_date,
b.pat_stat_cd as spc_discharge_status,
b.icn as spc_claim_id_src,
c.drg as spc_drg_cd,
substring(c.bill, 1, 1) as spc_bill_type_inst,
substring(c.bill, 2, 1) as spc_bill_type_class,
substring(c.bill, 3, 1) as spc_bill_type_freq,
'          ' as spc_units,
c.pcn as spc_member_id_src
into chcdwork.dbo.xz_dwqa15_temp1
from medicaid.dbo.clm_detail_@yr a tablesample(@rows_to_sample rows) inner join
	medicaid.dbo.clm_header_@yr b on a.icn = b.icn inner join 
	medicaid.dbo.clm_proc_@yr c on a.icn = c.icn;"

spc_sql2 = "insert into chcdwork.dbo.xz_dwqa15_temp1
select top @rows_to_check  '20@yr' as spc_fy,
a.ln_nbr as spc_claim_sequence_number,
a.fdos_dt  as spc_from_date_of_service,
a.tdos_csl  as spc_to_date_of_service,
a.pos  as spc_place_of_service,
a.proc_cd  as spc_cpt_hcpcs_cd,
'' as sub_proc_cd,
a.proc_mod_cd_1  as spc_proc_mod_1,
a.proc_mod_cd_2  as spc_proc_mod_2,
a.rev_cd  as spc_revenue_cd,
a.sub_chrg_amt  as spc_charge_amount,
a.dt_pd_amt  as spc_allowed_amount,
'' as spc_paid_amount,
a.sub_ref_prov_npi  as spc_ref_provider,
a.sub_rend_prov_npi  as spc_perf_rn_provider,
a.sub_opt_phy_npi as spc_perf_op_provider,
a.sub_rend_prv_tax_cd  as spc_provider_type,
b.adm_dt  as spc_admit_date,
b.dis_dt  as spc_discharge_date,
b.pat_stat  as spc_discharge_status,
b.derv_enc  as spc_claim_id_src,
c.drg  as spc_drg_cd,
substring(c.bill, 1, 1) as spc_bill_type_inst,
substring(c.bill, 2, 1) as spc_bill_type_class,
substring(c.bill, 3, 1) as spc_bill_type_freq,
a.dt_ln_unt as spc_units,
c.mem_id  as spc_member_id_src
from medicaid.dbo.enc_det_@yr a tablesample(@rows_to_sample rows) inner join
	medicaid.dbo.enc_header_@yr b on a.derv_enc = b.derv_enc inner join 
	medicaid.dbo.enc_proc_@yr c on a.derv_enc = c.derv_enc;"

spc_sql3 = "select top @rows_to_check  'HTW' as spc_fy,
a.clm_dtl_nbr as spc_claim_sequence_number,
a.from_dos as spc_from_date_of_service,
a.to_dos as spc_to_date_of_service,
a.pos as spc_place_of_service,
a.proc_cd as spc_cpt_hcpcs_cd,
a.sub_proc_cd,
a.proc_mod_1 as spc_proc_mod_1,
a.proc_mod_2 as spc_proc_mod_2,
a.rev_cd as spc_revenue_cd,
a.dtl_bill_amt as spc_charge_amount,
a.dtl_alwd_amt as spc_allowed_amount,
a.dtl_pd_amt as spc_paid_amount,
a.ref_prov_npi as spc_ref_provider,
a.perf_prov_npi as spc_perf_rn_provider,
'          ' as spc_perf_op_provider,
a.txm_cd as spc_provider_type,
b.adm_dt as spc_admit_date,
b.dis_dt as spc_discharge_date,
b.pat_stat_cd as spc_discharge_status,
b.icn as spc_claim_id_src,
c.drg as spc_drg_cd,
substring(c.bill, 1, 1) as spc_bill_type_inst,
substring(c.bill, 2, 1) as spc_bill_type_class,
substring(c.bill, 3, 1) as spc_bill_type_freq,
'          ' as spc_units,
c.pcn as spc_member_id_src
into chcdwork.dbo.xz_dwqa15_temp1
from medicaid.dbo.clm_detail_1819_htw a tablesample(@rows_to_sample rows) inner join
	medicaid.dbo.clm_header_1819_htw b on a.icn = b.icn inner join 
	medicaid.dbo.clm_proc_1819_htw c on a.icn = c.icn;"

spc_sql4 = "alter table chcdwork.dbo.xz_dwqa15_temp1
alter column spc_perf_op_provider varchar(50);

alter table chcdwork.dbo.xz_dwqa15_temp1
alter column spc_units varchar(50);"

```

## 2.2 Send, year by year, random selections from details tables
```{r}

#clear the holding table on TACC side
dbGetQuery(tac, 'drop table if exists dev.xz_dwqa15_temp1;')
print("tacc temp table dropped")

#yr = 14

for (yr in starting_yr:ending_yr){
  
  #clear tables
  dbGetQuery(spc, 'drop table if exists chcdwork.dbo.xz_dwqa15_temp1;')
  print("spc temp table dropped")
  
  if (yr == 12){
    print("Sampling records for 2012, the special year")
    
    #for 2012,
    #modify just the claims queries
    spc_sql1.mod = spc_sql1 %>% gsub('@rows_to_check', rows_to_check, .) %>%
      gsub('@rows_to_sample', rows_to_sample, .) %>%
      gsub('@yr', yr, .)
    
    #and send query
    tic("sample from claims")
    dbGetQuery(spc, spc_sql1.mod)
    toc()
    
  } else {
    print(paste0("Sampling records for 20", yr))
  
    #for all other years
    #modify queries
    spc_sql1.mod = spc_sql1 %>% gsub('@rows_to_check', rows_to_check, .) %>%
      gsub('@rows_to_sample', rows_to_sample, .) %>%
      gsub('@yr', yr, .)
    spc_sql2.mod = spc_sql2 %>% gsub('@rows_to_check', rows_to_check, .) %>%
      gsub('@rows_to_sample', rows_to_sample, .) %>%
      gsub('@yr', yr, .)
        
    tic("sample from claims")
    dbGetQuery(spc, spc_sql1.mod)
    toc()
    
    #fix data_type issue for FY22
    if (yr==22){
      dbExecute(spc, "alter table chcdwork.dbo.xz_dwqa15_temp1
                      alter column spc_claim_id_src varchar(50);")
    }
    
    tic("sample from encounters")
    dbGetQuery(spc, spc_sql2.mod)
    toc()
    
  }

  spc_selection = dbGetQuery(spc, 'select * from chcdwork.dbo.xz_dwqa15_temp1;')
  #make all names lowercase bc GP gets case-sensitive
  names(spc_selection) = tolower(names(spc_selection))
  
  tic("Write to TACC")
  dbWriteTable(tac, SQL('dev.xz_dwqa15_temp1'), spc_selection, append = T, overwrite = F)
  toc()
}

  #Sample HTW claims

  #clear tables
  dbGetQuery(spc, 'drop table if exists chcdwork.dbo.xz_dwqa15_temp1;')
  
  spc_sql3.mod = spc_sql3 %>% gsub('@rows_to_check', rows_to_check, .) %>%
  gsub('@rows_to_sample', rows_to_sample, .)
  
  tic("sample from HTW")
  dbGetQuery(spc, spc_sql3.mod)
  toc()

  spc_selection = dbGetQuery(spc, 'select * from chcdwork.dbo.xz_dwqa15_temp1;')
  #make all names lowercase bc GP gets case-sensitive
  names(spc_selection) = tolower(names(spc_selection))
  
  tic("Write to TACC")
  dbWriteTable(tac, SQL('dev.xz_dwqa15_temp1'), spc_selection, append = T, overwrite = F)
  toc()

```

# SECTION 3: Find mismatches

## 3.1 Modify raw data to match data_warehouse format

```{sql, connection = tac}

--Trim and null things that need to be trimmed and nulled

update dev.xz_dwqa15_temp1
   set spc_claim_sequence_number = case when trim(spc_claim_sequence_number) = '' then null else trim(spc_claim_sequence_number) end,
spc_from_date_of_service = case when trim(spc_from_date_of_service) = '' then null else trim(spc_from_date_of_service) end,
spc_to_date_of_service = case when trim(spc_to_date_of_service) = '' then null else trim(spc_to_date_of_service) end,
spc_place_of_service = case when trim(spc_place_of_service) = '' then null else trim(spc_place_of_service) end,
spc_cpt_hcpcs_cd = case when trim(spc_cpt_hcpcs_cd) = '' then null else trim(spc_cpt_hcpcs_cd) end,
sub_proc_cd = case when trim(sub_proc_cd) = '' then null else trim(sub_proc_cd) end,
spc_proc_mod_1 = case when trim(spc_proc_mod_1) = '' then null else trim(spc_proc_mod_1) end,
spc_proc_mod_2 = case when trim(spc_proc_mod_2) = '' then null else trim(spc_proc_mod_2) end,
spc_revenue_cd = case when trim(spc_revenue_cd) = '' then null else trim(spc_revenue_cd) end,
spc_charge_amount = case when trim(spc_charge_amount) = '' then null else trim(spc_charge_amount) end,
spc_allowed_amount = case when trim(spc_allowed_amount) = '' then null else trim(spc_allowed_amount) end,
spc_paid_amount = case when trim(spc_paid_amount) = '' then null else trim(spc_paid_amount) end,
spc_ref_provider = case when trim(spc_ref_provider) = '' then null else trim(spc_ref_provider) end,
spc_perf_rn_provider = case when trim(spc_perf_rn_provider) = '' then null else trim(spc_perf_rn_provider) end,
spc_perf_op_provider = case when trim(spc_perf_op_provider) = '' then null else trim(spc_perf_op_provider) end,
spc_provider_type = case when trim(spc_provider_type) = '' then null else trim(spc_provider_type) end,
spc_admit_date = case when trim(spc_admit_date) = '' then null else trim(spc_admit_date) end,
spc_discharge_date = case when trim(spc_discharge_date) = '' then null else trim(spc_discharge_date) end,
spc_discharge_status = case when trim(spc_discharge_status) = '' then null else trim(spc_discharge_status) end,
spc_claim_id_src = case when trim(spc_claim_id_src) = '' then null else trim(spc_claim_id_src) end,
spc_drg_cd = case when trim(spc_drg_cd) = '' then null else trim(spc_drg_cd) end,
spc_bill_type_inst = case when trim(spc_bill_type_inst) = '' then null else trim(spc_bill_type_inst) end,
spc_bill_type_class = case when trim(spc_bill_type_class) = '' then null else trim(spc_bill_type_class) end,
spc_bill_type_freq = case when trim(spc_bill_type_freq) = '' then null else trim(spc_bill_type_freq) end,
spc_units = case when trim(spc_units) = '' then null else trim(spc_units) end,
spc_member_id_src = case when trim(spc_member_id_src) = '' then null else trim(spc_member_id_src) end;

```

```{sql, connection = tac}

--Fix numbers if they are not the right length
update dev.xz_dwqa15_temp1
set spc_cpt_hcpcs_cd = case when length(spc_cpt_hcpcs_cd) < 5 then null else spc_cpt_hcpcs_cd end,
	sub_proc_cd = case when length(sub_proc_cd) < 5 then null else sub_proc_cd end,
	spc_revenue_cd = lpad(spc_revenue_cd, 4, '0');

```

```{sql, connection = tac}
	
--Use SUB_PROC_CD to replace PROC_CD in the cases where we're missing a PROC_CD
--Yes we do lose some SUB_PROC_CDs but anyone who needs them will have to go back to the original data
--as none of the other data sources have more than 1 CPT_HCSPCS_CD

update dev.xz_dwqa15_temp1
	set spc_cpt_hcpcs_cd = sub_proc_cd where spc_cpt_hcpcs_cd is null and sub_proc_cd is not null;

```

## 3.2 Find mismatches

```{sql, connection = tac}
	
--Clear results table first

drop table if exists dev.xz_dwqa15_temp2;

```

```{sql, connection = tac}
select a.*,
b.claim_sequence_number,
b.from_date_of_service,
b.to_date_of_service,
b.place_of_service,
b.cpt_hcpcs_cd,
b.proc_mod_1,
b.proc_mod_2,
b.revenue_cd,
b.charge_amount,
b.allowed_amount,
b.paid_amount,
b.ref_provider,
b.perf_rn_provider,
b.perf_op_provider,
b.provider_type,
b.admit_date,
b.discharge_date,
b.discharge_status,
b.claim_id_src,
b.drg_cd,
b.bill_type_inst,
b.bill_type_class,
b.bill_type_freq,
b.units,
b.member_id_src,
case when b.claim_sequence_number is null and a.spc_claim_sequence_number is not null then 1
when b.claim_sequence_number::text != a.spc_claim_sequence_number then 1 else 0 end as claim_sequence_number_mismatch,
case when b.from_date_of_service is null and a.spc_from_date_of_service is not null then 1
when b.from_date_of_service::text != a.spc_from_date_of_service then 1 else 0 end as from_date_of_service_mismatch,
case when b.to_date_of_service is null and a.spc_to_date_of_service is not null then 1 when b.to_date_of_service::text != a.spc_to_date_of_service then 1 else 0 end as to_date_of_service_mismatch,
case when b.place_of_service is null and a.spc_place_of_service is not null then 1 when b.place_of_service::text != a.spc_place_of_service then 1 else 0 end as place_of_service_mismatch,
case when b.cpt_hcpcs_cd is null and a.spc_cpt_hcpcs_cd is not null then 1 when b.cpt_hcpcs_cd::text != a.spc_cpt_hcpcs_cd then 1 else 0 end as cpt_hcpcs_cd_mismatch,
case when b.proc_mod_1 is null and a.spc_proc_mod_1 is not null then 1 when b.proc_mod_1::text != a.spc_proc_mod_1 then 1 else 0 end as proc_mod_1_mismatch,
case when b.proc_mod_2 is null and a.spc_proc_mod_2 is not null then 1 when b.proc_mod_2::text != a.spc_proc_mod_2 then 1 else 0 end as proc_mod_2_mismatch,
case when b.revenue_cd is null and a.spc_revenue_cd is not null then 1 when b.revenue_cd::text != a.spc_revenue_cd then 1 else 0 end as revenue_cd_mismatch,
case when b.charge_amount is null and a.spc_charge_amount is not null then 1 when b.charge_amount::float != a.spc_charge_amount::float then 1 else 0 end as charge_amount_mismatch,
case when b.allowed_amount is null and a.spc_allowed_amount is not null then 1 when b.allowed_amount::float != a.spc_allowed_amount::float then 1 else 0 end as allowed_amount_mismatch,
case when b.paid_amount is null and a.spc_paid_amount is not null then 1 when b.paid_amount::float != a.spc_paid_amount::float then 1 else 0 end as paid_amount_mismatch,
case when b.ref_provider is null and a.spc_ref_provider is not null then 1 when b.ref_provider::text != a.spc_ref_provider then 1 else 0 end as ref_provider_mismatch,
case when b.perf_rn_provider is null and a.spc_perf_rn_provider is not null then 1 when b.perf_rn_provider::text != a.spc_perf_rn_provider then 1 else 0 end as perf_rn_provider_mismatch,
case when b.perf_op_provider is null and a.spc_perf_op_provider is not null then 1 when b.perf_op_provider::text != a.spc_perf_op_provider then 1 else 0 end as perf_op_provider_mismatch,
case when b.provider_type is null and a.spc_provider_type is not null then 1 when b.provider_type::text != a.spc_provider_type then 1 else 0 end as provider_type_mismatch,
case when b.admit_date is null and a.spc_admit_date is not null then 1 when b.admit_date::text != a.spc_admit_date then 1 else 0 end as admit_date_mismatch,
case when b.discharge_date is null and a.spc_discharge_date is not null then 1 when b.discharge_date::text != a.spc_discharge_date then 1 else 0 end as discharge_date_mismatch,
case when b.discharge_status is null and a.spc_discharge_status is not null then 1 when b.discharge_status::text != a.spc_discharge_status then 1 else 0 end as discharge_status_mismatch,
case when b.claim_id_src is null and a.spc_claim_id_src is not null then 1 when b.claim_id_src::text != a.spc_claim_id_src then 1 else 0 end as claim_id_src_mismatch,
case when b.drg_cd is null and a.spc_drg_cd is not null then 1 when b.drg_cd::text != a.spc_drg_cd then 1 else 0 end as drg_cd_mismatch,
case when b.bill_type_inst is null and a.spc_bill_type_inst is not null then 1 when b.bill_type_inst::text != a.spc_bill_type_inst then 1 else 0 end as bill_type_inst_mismatch,
case when b.bill_type_class is null and a.spc_bill_type_class is not null then 1 when b.bill_type_class::text != a.spc_bill_type_class then 1 else 0 end as bill_type_class_mismatch,
case when b.bill_type_freq is null and a.spc_bill_type_freq is not null then 1 when b.bill_type_freq::text != a.spc_bill_type_freq then 1 else 0 end as bill_type_freq_mismatch,
case when b.units is null and a.spc_units is not null then 1 when b.units::float != a.spc_units::float then 1 else 0 end as units_mismatch,
case when b.member_id_src is null and a.spc_member_id_src is not null then 1 when b.member_id_src::text != a.spc_member_id_src then 1 else 0 end as member_id_src_mismatch
into dev.xz_dwqa15_temp2
from dev.xz_dwqa15_temp1 a left join dw_staging.mcd_claim_detail b
on a.spc_claim_id_src = b.claim_id_src and trim(a.spc_claim_sequence_number)::int = b.claim_sequence_number;



```

## 3.3 Get sum of mismatches
```{sql, connection = tac, output.var = sum_mismatches}

select spc_fy,
sum(claim_sequence_number_mismatch) as claim_sequence_number_mismatches,
sum(from_date_of_service_mismatch) as from_date_of_service_mismatches,
sum(to_date_of_service_mismatch) as to_date_of_service_mismatches,
sum(place_of_service_mismatch) as place_of_service_mismatches,
sum(cpt_hcpcs_cd_mismatch) as cpt_hcpcs_cd_mismatches,
sum(proc_mod_1_mismatch) as proc_mod_1_mismatches,
sum(proc_mod_2_mismatch) as proc_mod_2_mismatches,
sum(revenue_cd_mismatch) as revenue_cd_mismatches,
sum(charge_amount_mismatch) as charge_amount_mismatches,
sum(allowed_amount_mismatch) as allowed_amount_mismatches,
sum(paid_amount_mismatch) as paid_amount_mismatches,
sum(ref_provider_mismatch) as ref_provider_mismatches,
sum(perf_rn_provider_mismatch) as perf_rn_provider_mismatches,
sum(perf_op_provider_mismatch) as perf_op_provider_mismatches,
sum(provider_type_mismatch) as provider_type_mismatches,
sum(admit_date_mismatch) as admit_date_mismatches,
sum(discharge_date_mismatch) as discharge_date_mismatches,
sum(discharge_status_mismatch) as discharge_status_mismatches,
sum(claim_id_src_mismatch) as claim_id_src_mismatches,
sum(drg_cd_mismatch) as drg_cd_mismatches,
sum(bill_type_inst_mismatch) as bill_type_inst_mismatches,
sum(bill_type_class_mismatch) as bill_type_class_mismatches,
sum(bill_type_freq_mismatch) as bill_type_freq_mismatches,
sum(units_mismatch) as units_mismatches,
sum(member_id_src_mismatch) as member_id_src_mismatches,
count(*) as rows_checked
from dev.xz_dwqa15_temp2
group by spc_fy
order by spc_fy;

```

# SECTION 4: Outputs results

## 4.1 Write to xlsx
```{r}
output = sum_mismatches

wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "dw-claim-details-spotcheck.xlsx")

addWorksheet(wb, sheetName = "claim_details spotcheck")

writeData(wb, sheet = 1, "Mismatches found in claim_details tables between SPC and dw_staging", startCol=1, startRow=1)
writeData(wb, sheet = 1, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = 1, paste("Rows sampled per SPC table:", rows_to_check), startCol=1, startRow=3)

writeData(wb, sheet = 1, output, startCol=1, startRow=5)

nextrow = nrow(output) + 7
writeData(wb, sheet = 1, "Note: from_dos and to_dos mismatches are corrections of raw data (raw data = 01-01-0001)", startCol=1, startRow=nextrow)
writeData(wb, sheet = 1, "Note: Unit mismatches are due to enc tables allowing partial units (floats), and data_warehouse coercing numbers to int upon import", startCol=1, startRow=nextrow+1)

setColWidths(wb, sheet = 1, cols=1:ncol(output)+1, widths="auto")
setColWidths(wb, sheet = 1, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```

#SECTION 99: Delete temp tables, Close connections, clear R environment

```{sql, connection = spc, eval = FALSE}
drop table if exists chcdwork.dbo.xz_dwqa15_temp1;
drop table if exists chcdwork.dbo.xz_dwqa15_temp2;
drop table if exists chcdwork.dbo.xz_dwqa15_temp3;
```

```{sql, connection = tac, eval = FALSE}
drop table if exists dev.xz_dwqa15_temp1;
drop table if exists dev.xz_dwqa15_temp2;
drop table if exists dev.xz_dwqa15_temp3;
```

```{r close-connections, eval = FALSE}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env, eval = FALSE}
# clears R environment
rm(list=ls())
```
