---
title: "dw-rx-counting"
author: "XRZ"
date: '2022-11-09'
output: html_document
---

#Purpose:
This R markdown script counts distinct pharmacy rx for medicaid in
dw_staging and SPCDEDPWPVS1

9/12/23: Edited for 2022, changed
  pharmacy_claims -> mcd_pharmacy_claims
  work.dbo -> chcdwork.dbo
  added here::i_am

# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

#packages I don't use anymore: rstudioapi

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password


#Connect to Greenplum
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(),
	 dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc")))
```

## 0.5 Set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation
here::i_am("20-dw-rx-counting-pt1.rmd")

```

# SECTION 1: Check for previous runs and define global variables

## 1.1 Does output already exist?
```{r}
#SPC server shouldn't have major changes year to year, so if output exists already
#use that

path = here("outputs", "spc-rx-counting.xlsx")

if (file.exists(path)) {

stop("Output already exists!")

}

print("No previous output exists, proceeding...")

```

## 1.2 Otherwise define global variables and proceed
```{r}
#Declare the year range
starting_year = 2012
ending_year = 2022

#get the 2-digit version of years
starting_yr = starting_year - 2000
ending_yr = ending_year - 2000

```

# SECTION 2 Count distinct PCN-NDC-FILLDT combinations

## 2.1 Declare base SQL queries
```{r}
#declare base queries to modify for gathering distinct pcn-ndc-filldt combos

#initialize tables
sql0 = 'select \'20@yr\' as fy, concat(pcn, ndc, replace(rx_fill_dt, \'-\', \'\')) as rx_id
into chcdwork.dbo.xz_dwqa_chiprx
from medicaid.dbo.chip_rx_fy@yr
where pcn != \'000000000\';

select \'20@yr\' as fy, concat(pcn, ndc, replace(rx_fill_dt, \'-\', \'\')) as rx_id
into chcdwork.dbo.xz_dwqa_ffsrx
from medicaid.dbo.ffs_rx_fy@yr
where pcn != \'000000000\';

select \'20@yr\' as fy, concat(pcn, ndc, replace(rx_fill_dt, \'-\', \'\')) as rx_id
into chcdwork.dbo.xz_dwqa_mcorx
from medicaid.dbo.mco_rx_fy@yr
where pcn != \'000000000\';'

#run for each year
sql1 = 'insert into chcdwork.dbo.xz_dwqa_chiprx
select \'20@yr\' as fy, concat(pcn, ndc, replace(rx_fill_dt, \'-\', \'\')) as rx_id
from medicaid.dbo.chip_rx_fy@yr
where pcn != \'000000000\';

insert into chcdwork.dbo.xz_dwqa_ffsrx
select \'20@yr\' as fy, concat(pcn, ndc, replace(rx_fill_dt, \'-\', \'\')) as rx_id
from medicaid.dbo.ffs_rx_fy@yr
where pcn != \'000000000\';

insert into chcdwork.dbo.xz_dwqa_mcorx
select \'20@yr\' as fy, concat(pcn, ndc, replace(rx_fill_dt, \'-\', \'\')) as rx_id
from medicaid.dbo.mco_rx_fy@yr
where pcn != \'000000000\';'

```

## 2.2 Run it for each year
```{r}
dbGetQuery(spc, 'drop table if exists chcdwork.dbo.xz_dwqa_chiprx;')
dbGetQuery(spc, 'drop table if exists chcdwork.dbo.xz_dwqa_ffsrx;')
dbGetQuery(spc, 'drop table if exists chcdwork.dbo.xz_dwqa_mcorx;')

for (yr in starting_yr:ending_yr){
  
  print(paste0("Gathering rx-ndc-fill-dt combos for 20", yr))
  tic("Processing time")
  
  if (yr == starting_yr) { #initialize tables for the first year
    
    sql0.mod = sql0 %>% gsub(pattern = '@yr', replacement = yr)
    dbGetQuery(spc, sql0.mod)
  
  } else {
    
    sql1.mod = sql1 %>% gsub(pattern = '@yr', replacement = yr)
    dbGetQuery(spc, sql1.mod)
  }
  toc()
  
}

```

## 2.3 Get results
```{r}
#Next bit of code takes a while, so let's time it
tic("Aggregate numbers")

```

```{sql, connection = spc}

drop table if exists chcdwork.dbo.xz_dwqa_rxtemp2;

with a as (select fy, count(distinct rx_id) as chip from chcdwork.dbo.xz_dwqa_chiprx group by fy),
b as (select fy, count(distinct rx_id) as ffs from chcdwork.dbo.xz_dwqa_ffsrx group by fy),
c as (select fy, count(distinct rx_id) as mco from chcdwork.dbo.xz_dwqa_mcorx group by fy)

select a.fy, a.chip, b.ffs, c.mco, (a.chip + b.ffs + c.mco) as sum
into chcdwork.dbo.xz_dwqa_rxtemp2
from a left join b on a.fy = b.fy left join c on a.fy = c.fy;

```

```{sql, connection = spc, output.var = spc_counts}

select * from chcdwork.dbo.xz_dwqa_rxtemp2 order by fy;

```

```{sql, connection = spc, output.var = htw_counts}

select 'HTW' as fy, NULL as chip, NULL as ffs, NULL as mco, count(*) as sum
from medicaid.dbo.FFS_RX_FY18_19_HTW;

```

```{r}
toc()

```
## 2.4 Rbind the HTW numbers to other numbers
```{r}

spc_counts = rbind(spc_counts, htw_counts)

```


# SECTION 3: Print it out so we won't have to do this again

## 3.1 Write to spreadsheet
```{r}
wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "spc-rx-counting.xlsx")

output = spc_counts

addWorksheet(wb, sheetName = "SPCDEDPWPVS1 rx counting")

writeData(wb, sheet = 1, "Count of distinct pcn-ndc-fill_dt combos in SPCDEDPWPVS1", startCol=1, startRow=1)
writeData(wb, sheet = 1, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = 1, output, startCol=1, startRow=4)

setColWidths(wb, sheet = 1, cols=1:ncol(output)+1, widths="auto")
setColWidths(wb, sheet = 1, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```

#SECTION 99: Delete temp tables, Close connections, clear R environment

```{r close-connections, eval = FALSE}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env, eval = FALSE}
# clears R environment
rm(list=ls())
```
