---
title: "dw-rx-spotcheck"
author: "XRZ"
date: '2022-11-22'
output: html_document
---

# PURPOSE
This R markdown script spot checks for matching details information in dw_staging

# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requiring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password


#Connect to Greenplum
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(),
	 dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc")))
```

## 0.5 Set misc R options
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)
options("scipen"=100, "digits" = 4) #avoid scientific notation

```

# SECTION 1: Declare global variables
```{r}
#Define the starting and ending years for checking (4-digit year)
starting_year = 2012
ending_year = 2021

#Define how many rows to check per table
rows_to_check = 5000

#set rows_to_sample as slightly higher than rows to check b/c of
#the funny way that tablesample works
rows_to_sample = as.integer(rows_to_check) * 1.2

#convert to 2-digit year
starting_yr = starting_year - 2000
ending_yr = ending_year - 2000
```

# SECTION 2: Randomly select rows from SPC details tables and uploads to TACC
## 2.1 Define base queries
```{r}

#select random rows from rx tables
spc_sql1 = 'select top @rows_to_check  \'20@yr\' as spc_fy,
\'chip\' as spc_table,
rx_fill_dt as spc_fill_date,
ndc as spc_ndc,
rx_days_supply as spc_days_supply,
rx_nbr as spc_script_id,
refill_nbr as spc_refill_count,
rx_quantity as spc_quantity,
prescriber_npi as spc_provider_npi,
phmcy_nbr as spc_pharmacy_id,
gross_amt_due  as spc_total_charge_amount,
amount_paid as spc_total_paid_amount,
pcn as spc_member_id_src,
concat(pcn, ndc, replace(rx_fill_dt, \'-\', \'\')) as rx_id
into work.dbo.xz_dwqa_temp1
from medicaid.dbo.chip_rx_fy@yr tablesample(@rows_to_sample rows);'

spc_sql2 = 'insert into work.dbo.xz_dwqa_temp1
select top @rows_to_check  \'20@yr\' as spc_fy,
\'ffs\' as spc_table,
rx_fill_dt as spc_fill_date,
ndc as spc_ndc,
rx_days_supply as spc_days_supply,
rx_nbr as spc_script_id,
refill_nbr as spc_refill_count,
rx_quantity as spc_quantity,
prescriber_npi as spc_provider_npi,
phmcy_nbr as spc_pharmacy_id,
gross_amt_due  as spc_total_charge_amount,
amount_paid as spc_total_paid_amount,
pcn as spc_member_id_src,
concat(pcn, ndc, replace(rx_fill_dt, \'-\', \'\')) as rx_id
from medicaid.dbo.ffs_rx_fy@yr tablesample(@rows_to_sample rows);'

spc_sql3 = 'insert into work.dbo.xz_dwqa_temp1
select top @rows_to_check  \'20@yr\' as spc_fy,
\'mco\' as spc_table,
rx_fill_dt as spc_fill_date,
ndc as spc_ndc,
rx_days_supply as spc_days_supply,
rx_nbr as spc_script_id,
refill_nbr as spc_refill_count,
rx_quantity as spc_quantity,
prescriber_npi as spc_provider_npi,
phmcy_nbr as spc_pharmacy_id,
gross_amt_due  as spc_total_charge_amount,
amount_paid as spc_total_paid_amount,
pcn as spc_member_id_src,
concat(pcn, ndc, replace(rx_fill_dt, \'-\', \'\')) as rx_id
from medicaid.dbo.mco_rx_fy@yr tablesample(@rows_to_sample rows);'

spc_sql4 = 'select top @rows_to_check  \'HTW\' as spc_fy,
\'htw\' as spc_table,
rx_fill_dt as spc_fill_date,
ndc as spc_ndc,
rx_days_supply as spc_days_supply,
rx_nbr as spc_script_id,
refill_nbr as spc_refill_count,
rx_quantity as spc_quantity,
prescriber_npi as spc_provider_npi,
phmcy_nbr as spc_pharmacy_id,
gross_amt_due  as spc_total_charge_amount,
amount_paid as spc_total_paid_amount,
pcn as spc_member_id_src,
concat(pcn, ndc, replace(rx_fill_dt, \'-\', \'\')) as rx_id
into work.dbo.xz_dwqa_temp1
from medicaid.dbo.FFS_RX_FY18_19_HTW tablesample(@rows_to_sample rows);'


```

## 2.2 Send, year by year, random selections from rx tables
```{r}

#clear the holding table on TACC side
dbGetQuery(tac, 'drop table if exists dev.xz_dwqa_temp1;')
print("tacc temp table dropped")

#yr = 14

for (yr in starting_yr:ending_yr){
  
  #clear tables
  dbGetQuery(spc, 'drop table if exists work.dbo.xz_dwqa_temp1;')
  print("spc temp table dropped")
  
  print(paste0("Sampling records for 20", yr))

  #modify queries
  spc_sql1.mod = spc_sql1 %>% gsub('@rows_to_check', rows_to_check, .) %>%
    gsub('@rows_to_sample', rows_to_sample, .) %>%
    gsub('@yr', yr, .)
  
  spc_sql2.mod = spc_sql2 %>% gsub('@rows_to_check', rows_to_check, .) %>%
    gsub('@rows_to_sample', rows_to_sample, .) %>%
    gsub('@yr', yr, .)
  
  spc_sql3.mod = spc_sql3 %>% gsub('@rows_to_check', rows_to_check, .) %>%
    gsub('@rows_to_sample', rows_to_sample, .) %>%
    gsub('@yr', yr, .)
        
  tic("sample from chip")
  dbGetQuery(spc, spc_sql1.mod)
  toc()
  
  tic("sample from ffs")
  dbGetQuery(spc, spc_sql2.mod)
  toc()
  
  tic("sample from mco")
  dbGetQuery(spc, spc_sql3.mod)
  toc()

  spc_selection = dbGetQuery(spc, 'select * from work.dbo.xz_dwqa_temp1;')
  #make all names lowercase bc GP gets case-sensitive
  names(spc_selection) = tolower(names(spc_selection))
  
  tic("Write to TACC")
  dbWriteTable(tac, SQL('dev.xz_dwqa_temp1'), spc_selection, append = T, overwrite = F)
  toc()
}

  #Sample HTW claims

  #clear tables
  dbGetQuery(spc, 'drop table if exists work.dbo.xz_dwqa_temp1;')
  
  spc_sql4.mod = spc_sql4 %>% gsub('@rows_to_check', rows_to_check, .) %>%
  gsub('@rows_to_sample', rows_to_sample, .)
  
  tic("sample from HTW")
  dbGetQuery(spc, spc_sql4.mod)
  toc()

  spc_selection = dbGetQuery(spc, 'select * from work.dbo.xz_dwqa_temp1;')
  #make all names lowercase bc GP gets case-sensitive
  names(spc_selection) = tolower(names(spc_selection))
  
  tic("Write to TACC")
  dbWriteTable(tac, SQL('dev.xz_dwqa_temp1'), spc_selection, append = T, overwrite = F)
  toc()

```

# SECTION 3: Looks for DX codes in dw_staging.clm_dx

## 3.1 Find mismatches

```{sql, connection = tac}
	
--Clear results table first

drop table if exists dev.xz_dwqa_temp2;

```

```{sql, connection = tac}
select a.*,
b.fill_date,
b.ndc,
b.days_supply,
b.script_id,
b.refill_count,
b.quantity,
b.provider_npi,
b.pharmacy_id,
b.total_charge_amount,
b.total_paid_amount,
b.member_id_src,
b.fiscal_year,
case when b.fill_date is null and a.spc_fill_date is not null then 1 when b.fill_date::text != a.spc_fill_date then 1 else 0 end as fill_date_mismatch,
case when b.ndc is null and a.spc_ndc is not null then 1 when b.ndc::text != a.spc_ndc then 1 else 0 end as ndc_mismatch,
case when b.days_supply is null and a.spc_days_supply is not null then 1 when b.days_supply::text != a.spc_days_supply then 1 else 0 end as days_supply_mismatch,
case when b.script_id is null and a.spc_script_id is not null then 1 when b.script_id::text != a.spc_script_id then 1 else 0 end as script_id_mismatch,
case when b.refill_count is null and a.spc_refill_count is not null then 1 when b.refill_count::text != a.spc_refill_count then 1 else 0 end as refill_count_mismatch,
case when b.quantity is null and a.spc_quantity is not null then 1 when b.quantity::float != a.spc_quantity::float then 1 else 0 end as quantity_mismatch,
case when b.provider_npi is null and a.spc_provider_npi is not null then 1 when b.provider_npi::text != a.spc_provider_npi then 1 else 0 end as provider_npi_mismatch,
case when b.pharmacy_id is null and a.spc_pharmacy_id is not null then 1 when b.pharmacy_id::text != a.spc_pharmacy_id then 1 else 0 end as pharmacy_id_mismatch,
case when b.total_charge_amount is null and a.spc_total_charge_amount is not null then 1 when b.total_charge_amount::float != a.spc_total_charge_amount::float then 1 else 0 end as total_charge_amount_mismatch,
case when b.total_paid_amount is null and a.spc_total_paid_amount is not null then 1 when b.total_paid_amount::float != a.spc_total_paid_amount::float then 1 else 0 end as total_paid_amount_mismatch,
case when b.member_id_src is null and a.spc_member_id_src is not null then 1 when b.member_id_src::text != a.spc_member_id_src then 1 else 0 end as member_id_src_mismatch,
case when spc_fy = 'HTW' then 0 when b.fiscal_year is null and a.spc_fy is not null then 1 when b.fiscal_year::text != a.spc_fy then 1 else 0 end as fiscal_year_mismatch
into dev.xz_dwqa_temp2
from dev.xz_dwqa_temp1 a left join dw_staging.pharmacy_claims b
on a.rx_id = b.rx_claim_id_src and
	a.spc_total_charge_amount::float = b.total_charge_amount and
	a.spc_total_paid_amount::float = b.total_paid_amount and
	a.spc_refill_count = b.refill_count::text and
	a.spc_days_supply::int = b.days_supply and
	a.spc_script_id = b.script_id and
	a.spc_provider_npi = b.provider_npi and
	a.spc_pharmacy_id = b.pharmacy_id;

```

## 3.3 Get sum of mismatches
```{sql, connection = tac, output.var = sum_mismatches}

select spc_fy,
sum(fill_date_mismatch) as fill_date_mismatches,
sum(ndc_mismatch) as ndc_mismatches,
sum(days_supply_mismatch) as days_supply_mismatches,
sum(script_id_mismatch) as script_id_mismatches,
sum(refill_count_mismatch) as refill_count_mismatches,
sum(quantity_mismatch) as quantity_mismatches,
sum(provider_npi_mismatch) as provider_npi_mismatches,
sum(pharmacy_id_mismatch) as pharmacy_id_mismatches,
sum(total_charge_amount_mismatch) as total_charge_amount_mismatches,
sum(total_paid_amount_mismatch) as total_paid_amount_mismatches,
sum(member_id_src_mismatch) as member_id_src_mismatches,
sum(fiscal_year_mismatch) as fy_mismatches,
count(*) as rows_checked
from dev.xz_dwqa_temp2
group by spc_fy
order by spc_fy;


```

# SECTION 4: Outputs results

## 4.1 Write to xlsx
```{r}
output = sum_mismatches

wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "dw-rx-spotcheck.xlsx")

addWorksheet(wb, sheetName = "rx spotcheck")

writeData(wb, sheet = 1, "Mismatches found in pharmacy_claims tables between SPC and dw_staging", startCol=1, startRow=1)
writeData(wb, sheet = 1, paste("Run time:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = 1, paste("Rows sampled per SPC table:", rows_to_check), startCol=1, startRow=3)

writeData(wb, sheet = 1, output, startCol=1, startRow=5)

nextrow = nrow(output) + 7
writeData(wb, sheet = 1, "Note: quantity_mismatch is b/c raw data quantities are floats and are coerced to ints upon loading into dw", startCol=1, startRow=nextrow)
writeData(wb, sheet = 1, "Note: I didn't exhaustively check other mismatches, but they seem to be related to '' being converted to NULLs in dw", startCol=1, startRow=nextrow+1)
writeData(wb, sheet = 1, "Note: I also had to match on rx_claim_id_src, total_charge_amount, total_paid_amount, ... etc. 8/11 variables to achieve anything close to unique row-matching.", startCol=1, startRow=nextrow+2)

setColWidths(wb, sheet = 1, cols=1:ncol(output)+1, widths="auto")
setColWidths(wb, sheet = 1, cols=1, widths=10)

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```

#SECTION 99: Delete temp tables, Close connections, clear R environment

```{sql, connection = spc, eval = FALSE}
drop table if exists work.dbo.xz_dwqa_temp1;
drop table if exists work.dbo.xz_dwqa_temp2;
drop table if exists work.dbo.xz_dwqa_temp3;
```

```{sql, connection = tac, eval = FALSE}
drop table if exists dev.xz_dwqa_temp1;
drop table if exists dev.xz_dwqa_temp2;
drop table if exists dev.xz_dwqa_temp3;
```

```{r close-connections, eval = FALSE}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env, eval = FALSE}
# clears R environment
rm(list=ls())
```
