---
title: "dw-enrollment-check"
author: "XRZ"
date: '2022-10-26'
output: html_document
---

#Purpose:
This R markdown script examines the accuracy of conversions from raw source tables to
data_warehouse tables

It selects random rows from the dw_staging yearly enrollment table and compares
them to a table that is created using (mostly) the same logic from the SPC-side tables.

Spotcheck1 runs in the dw -> spc direction (Spotcheck2 runs in the reverse direction)


# SECTION 0: Loading required packages, making connections, the usual

## 0.1 Load packages
```{r package-loading, warning = FALSE}
# Package installs/loading 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(RPostgres, DBI, odbc, keyring, openxlsx, tidyverse, beepr, tictoc, here)

```

## 0.2 Connect to TACC
```{r connect-to-tacc}
#PREREQUISITE: Set up your username/password in Keyring
# Instructions: replace indicated areas in code below with your username/password for TACC server
# Run it once, and delete from code - code will not need to be run more than once per user per computer
# Keyring will save your username/password to your OS credential store, and the service/user/password combo
# can be retrieved without hardcoding a password or requring user input.
# key_set_with_value(service = "Greenplum", 
#                   username = "-----------", #replace with your username
#                   password = "-----------") #replace with your password

# Function for connecting to TACC/Greenplum
# TACC kicks you out for inactivity so just call function before connections
connect_to_tacc <- function() {
tac <- dbConnect(RPostgres::Postgres(),
	 dbname = "uthealth",
	 user = "xrzhang",
	 password = key_get("Greenplum", "xrzhang"),
	 host = "greenplum01.corral.tacc.utexas.edu",
	 port = 5432)
}

```

## 0.3 Connect to SPC
```{r connect-to-spcdedpwpvs1}
#PREREQUISITE: Set up connection to SPCDEDPWPVS1 in ODBC Data sources
#Make sure the default schema is correct! This one is set to medicaid

#Connect to SPCDEDPWPVS1
spc <- dbConnect(odbc::odbc(),
	 dsn = "medicaid")
```

## 0.4 Clear R environment (except for DB connections)
```{r clear-environment}
# clears R environment except for DB connections
rm(list=setdiff(ls(), c("tac", "spc", "connect_to_tacc")))
```

## 0.5 Set print to 25 rows
```{r}
knitr::opts_chunk$set(echo=TRUE, rows.print=25)

```

# SECTION 1: Define global variables

```{r}
# Define tables to compare

#fiscal yearly tables
#tacc_table = "dw_staging.mcd_member_enrollment_fiscal_yearly"
#spc_table = "chcdwork.dbo.AGG_ENRL_MCD_FY_Upt"

#calendar yearly tables
tacc_table = "dw_staging.mcd_member_enrollment_fiscal_yearly"
spc_table = "chcdwork.dbo.AGG_ENRL_MCD_FY_Upt"

#Define the starting and ending years for checking (4-digit year)
starting_year = 2015
ending_year = 2021

#Define how many rows to check per year
rows_to_check = '500000'

#Define how many sets of errors to print out per year
records_to_print = 5

#convert to 2-digit year
starting_yr = starting_year - 2000
ending_yr = ending_year - 2000
```

# SECTION 2: Compare SPC and TACC tables
## 2.1 Pull TACC data and upload to SPC
```{r}
# Declare base query
tac_sql = "with b as (select race_cd_src, race_cd from reference_tables.ref_race
	where data_source = 'mdcd' and race_cd_src is not null)

select a.data_source, a.member_id_src, a.fiscal_year, a.enrl_months_nondual,
  a.enrl_months_dual, a.total_enrolled_months, a.gender_cd,
  b.race_cd_src, a.age_derived, a.dob_derived, a.zip5, a.plan_type, a.dual, a.htw
  from @tacc_table a left join b
  	on a.race_cd = b.race_cd
  where a.fiscal_year between @starting_year and @ending_year
    and data_source = 'mdcd'
  order by random()
  limit @rows_to_check;"

# modify base query
tac_sql.mod = tac_sql %>% gsub('@rows_to_check', rows_to_check, .) %>%
  gsub("@tacc_table", tacc_table, .) %>%
  gsub("@starting_year", starting_year, .) %>%
  gsub("@ending_year", ending_year, .)

# connect to tacc
tac = connect_to_tacc()

# Pull selection from TACC-side
tac_selection = dbGetQuery(tac, tac_sql.mod)

# Write to SPC
dbExecute(spc, "drop table if exists chcdwork.dbo.xz_dwqa_temp1;")
dbWriteTable(spc, SQL('chcdwork.dbo.xz_dwqa_temp1'), tac_selection)

```
## 2.2 Make boolean table of mismatches

```{r}
# Declare base query
spc_sql1 = "select a.member_id_src as member_id, a.fiscal_year,
	case when b.CLIENT_NBR is null then 1 else 0 end as member_id_mismatch,
	case when a.enrl_months_nondual != b.NON_DUAL_MONTHS then 1 else 0 end as em_nondual_mismatch,
	case when a.enrl_months_dual != b.DUAL_MONTHS then 1 else 0 end as em_dual_mismatch,
	case when a.total_enrolled_months != b.TOTAL_MONTHS then 1 else 0 end as em_mismatch,
	case when a.gender_cd != b.sex then 1 else 0 end as sex_mismatch,
	case when a.age_derived != b.age then 1 else 0 end as age_mismatch,
	case when a.race_cd_src != b.race and b.race is not null then 1 else 0 end as race_mismatch,
	case when a.zip5 != b.zip then 1 else 0 end as zip_mismatch,
	case when a.plan_type != b.MCO_PROGRAM_NM then 1 else 0 end as plan_mismatch,
	case when a.dual !=  b.smib then 1 else 0 end as dual_mismatch,
	a.enrl_months_nondual as tacc_em_nondual, b.NON_DUAL_MONTHS as spc_em_nondual,
	a.enrl_months_dual as tacc_em_dual, b.DUAL_MONTHS as spc_em_dual,
	a.total_enrolled_months as tacc_em_total, b.TOTAL_MONTHS as spc_em_total,
	a.gender_cd as tacc_sex, b.sex as spc_sex,
	a.age_derived as tacc_age, b.age as spc_age,
	a.race_cd_src as tacc_race, b.race as spc_race,
	a.zip5 as tacc_zip, b.zip as spc_zip,
	a.plan_type as tacc_plan, b.MCO_PROGRAM_NM as spc_plan,
	a.dual as tacc_dual, b.smib as spc_dual
into chcdwork.dbo.xz_mcd_enrl_mismatches
from chcdwork.dbo.xz_dwqa_temp1 a
	left join @spc_table b
	on a.member_id_src = b.CLIENT_NBR and a.fiscal_year = b.ENRL_FY;"

# modify query
spc_sql1.mod = spc_sql1 %>% gsub("@spc_table", spc_table, .)

# Make boolean table of matches
dbExecute(spc, "drop table if exists chcdwork.dbo.xz_mcd_enrl_mismatches;")
dbGetQuery(spc, spc_sql1.mod)

# unused
# 	case when a.race_cd_src != b.race and b.race is not null then 1 else 0 end as race_mismatch,
# 	case when a.htw != b.htw then 1 else 0 end as htw_mismatch,
# 	case when a.dob_derived != b.dob then 1 else 0 end as dob_mismatch,
#	a.gender_cd as tacc_sex, b.sex as spc_sex,
#	
#	

```

##2.3 Calculate the sum of errors
```{sql, connection = spc, output.var = sum_errors}

select sum(member_id_mismatch) as member_id_mismatches,
  sum(em_nondual_mismatch) as em_nondual_mismatches,
  sum(em_dual_mismatch) as em_dual_mistmaches,
	sum(em_mismatch) as em_mismatches,
	sum(sex_mismatch) as sex_mismatches,
	sum(age_mismatch) as age_mismatches,
	sum(race_mismatch) as race_mismaches,
	sum(zip_mismatch) as zip_mismatches,
	sum(plan_mismatch) as plan_mismatches,
	sum(dual_mismatch) as dual_mismatches
from chcdwork.dbo.xz_mcd_enrl_mismatches;

```


# SECTION 3: Closer look at what's going wrong
## 3.1: Pull mismatches
```{r}
#SEX, RACE, ZIP, AND PLAN HAVE MISMATCHES
#Pull lists of mismatches

em_dual_mismatches = dbGetQuery(spc, 'select member_id, fiscal_year
              from chcdwork.dbo.xz_mcd_enrl_mismatches
              where em_dual_mismatch = 1;')

em_nondual_mismatches = dbGetQuery(spc, 'select member_id, fiscal_year
              from chcdwork.dbo.xz_mcd_enrl_mismatches
              where em_nondual_mismatch = 1;')

em_mismatches = dbGetQuery(spc, 'select member_id, fiscal_year
              from chcdwork.dbo.xz_mcd_enrl_mismatches
              where em_mismatch = 1;')

sex_mismatches = dbGetQuery(spc, 'select member_id, fiscal_year
              from chcdwork.dbo.xz_mcd_enrl_mismatches
              where sex_mismatch = 1;')

age_mismatches = dbGetQuery(spc, 'select member_id, fiscal_year
              from chcdwork.dbo.xz_mcd_enrl_mismatches
              where age_mismatch = 1;')

# race_mismatches = dbGetQuery(spc, 'select member_id, fiscal_year
#              from chcdwork.dbo.xz_mcd_enrl_mismatches
#              where race_mismatch = 1;')

zip_mismatches = dbGetQuery(spc, 'select member_id, fiscal_year
              from chcdwork.dbo.xz_mcd_enrl_mismatches
              where zip_mismatch = 1;')

plan_mismatches = dbGetQuery(spc, 'select member_id, fiscal_year
              from chcdwork.dbo.xz_mcd_enrl_mismatches
              where plan_mismatch = 1;')

```

## 3.2 Setup to pull individual rows
```{r}
#Define variables and corresponding variable names
# Create the dataframe with 3 columns
var_list <- data.frame(variable = c("em_dual", "em_nondual", "em", "sex", "age", "zip", "plan", "dual"),
                 tacc = c("enrl_months_dual", "enrl_months_nondual", "total_enrolled_months", "gender_cd", "age_derived", "zip5", "plan_type", "dual"),
                 spc = c("dual_months", "non_dual_months", "months", "sex", "age", "zip", "mco_program_nm", "smib"))

#Define base queries

mismatch_query = 'select member_id, fiscald_year,tacc_@variable, spc_@variable
  from chcdwork.dbo.xz_mcd_enrl_mismatches where member_id = \'@memid\' and year = \'@year\''

tac_sql1 = 'with b as (select race_cd_src, race_cd from reference_tables.ref_race
	where data_source = \'mdcd\' and race_cd_src is not null)

select a. fiscal_year, a.member_id_src, a.year, a.month_year_id, a.gender_cd, b.race_cd_src,
a.zip5, a.plan_type
from dw_staging.member_enrollment_monthly a left join b
	on a.race_cd = b.race_cd
	where member_id_src = \'@memid\' and year = \'@year\'
  order by a.month_year_id;'

spc_sql1 = 'select client_nbr, cy, elig_date, sex, race, zip, mco from chcdwork.dbo.xz_mcd_reconciliation_cy_etl
  where client_nbr = \'@memid\' and cy = \'@year\'
  order by elig_date;'


```

## 3.3 Data Exploration: Not executed
```{r, eval=FALSE}
#this chunk for data exploration
#just set current_mismatch to the dataframe and row you want to check

current_mismatch = dob_mismatches[1,]

tac_sql1.mod = tac_sql1 %>% gsub('@memid', current_mismatch[1,1], .) %>% 
  gsub('@year', current_mismatch[1,2], .)

spc_sql1.mod = spc_sql1 %>% gsub('@memid', current_mismatch[1,1], .) %>% 
  gsub('@year', current_mismatch[1,2], .)

mismatch_query.mod = mismatch_query %>% gsub('@memid', current_mismatch[1,1], .) %>% 
  gsub('@year', current_mismatch[1,2], .)

mismatch_details = dbGetQuery(spc, mismatch_query.mod)
tacc_details = dbGetQuery(tac, tac_sql1.mod)
spc_details = dbGetQuery(spc, spc_sql1.mod)

mismatch_details
tacc_details
spc_details
```

## 3.4 Define the function to get mismatch info
```{r}
get_mismatch_info = function(current_mismatch){
  tac_sql1.mod = tac_sql1 %>% gsub('@memid', current_mismatch[1,1], .) %>% 
  gsub('@year', current_mismatch[1,2], .)

  spc_sql1.mod = spc_sql1 %>% gsub('@memid', current_mismatch[1,1], .) %>% 
    gsub('@year', current_mismatch[1,2], .)
  
  mismatch_query.mod = mismatch_query %>% gsub('@memid', current_mismatch[1,1], .) %>% 
    gsub('@year', current_mismatch[1,2], .)
  
  mismatch_details = dbGetQuery(spc, mismatch_query.mod)
  tacc_details = dbGetQuery(tac, tac_sql1.mod)
  spc_details = dbGetQuery(spc, spc_sql1.mod)
  
  output = list(mismatch_details = mismatch_details,
                tacc_details = tacc_details,
                spc_details = spc_details)
  
  return(output)
}

```

## 3.5 Assemble into a spreadsheet
```{r, eval=TRUE}
#this chunk spits out the final table

wb = createWorkbook()
dir = here("outputs")
path = here("outputs", "dw-enrollment-spotcheck-tacc-to-spc.xlsx")

addWorksheet(wb, sheetName = "Summary of Mismatches") #1
addWorksheet(wb, sheetName = "sex mismatches")        #2
addWorksheet(wb, sheetName = "race mismatches")       #3
addWorksheet(wb, sheetName = "zip mismatches")        #4
addWorksheet(wb, sheetName = "plan mismatches")       #5

#write data into sheet 1
writeData(wb, sheet = 1, "Data Warehouse Enrollment Tables Spot Check", startCol=1, startRow=1)
writeData(wb, sheet = 1, paste("Run date:", Sys.time()), startCol=1, startRow=2)
writeData(wb, sheet = 1, "Direction: Records selected from TACC server, checked against SPC server",
                              startCol=1, startRow=3)
writeData(wb, sheet = 1, paste("Rows checked:", rows_to_check), startCol = 1, startRow = 4)
writeData(wb, sheet = 1, sum_errors, startCol=1, startRow=6)

#write headers for all other sheets
writeData(wb, sheet = 2, "Sex Mismatches", startCol=1, startRow=1)
writeData(wb, sheet = 3, "Race Mismatches", startCol=1, startRow=1)
writeData(wb, sheet = 4, "Zip Mismatches", startCol=1, startRow=1)
writeData(wb, sheet = 5, "Plan Type Mismatches", startCol=1, startRow=1)

print("Writing mismatches for sex")


#Write mismatches for sex
next_row = 3 #reset next_row
for (i in 1:min(nrow(sex_mismatches), records_to_print)){
  current_mismatch = sex_mismatches[i,]
  output = get_mismatch_info(current_mismatch)
  
  writeData(wb, sheet = 2, "Mismatch details from yearly tables", startCol = 1, startRow = next_row)
  writeData(wb, sheet = 2, output$mismatch_details, startCol = 1, startRow = next_row + 1)
  next_row = next_row + nrow(output$mismatch_details) + 3
  
  writeData(wb, sheet = 2, "Mismatch details from TACC dw_staging monthly table",
            startCol = 1, startRow = next_row)
  writeData(wb, sheet = 2, output$tacc_details, startCol = 1, startRow = next_row+1)
  next_row = next_row + nrow(output$tacc_details) + 3
  
  writeData(wb, sheet = 2, "Mismatch details from SPC monthly tables", startCol = 1, startRow = next_row)
  writeData(wb, sheet = 2, output$spc_details, startCol = 1, startRow = next_row+1)
  next_row = next_row + nrow(output$spc_details) + 4
}

print("Writing mismatches for race")

#Write mismatches for race
next_row = 3 #reset next_row
for (i in 1:min(nrow(race_mismatches), records_to_print)){
  current_mismatch = race_mismatches[i,]
  output = get_mismatch_info(current_mismatch)
  
  writeData(wb, sheet = 3, "Mismatch details from yearly tables", startCol = 1, startRow = next_row)
  writeData(wb, sheet = 3, output$mismatch_details, startCol = 1, startRow = next_row + 1)
  next_row = next_row + nrow(output$mismatch_details) + 3
  
  writeData(wb, sheet = 3, "Mismatch details from TACC dw_staging monthly table",
            startCol = 1, startRow = next_row)
  writeData(wb, sheet = 3, output$tacc_details, startCol = 1, startRow = next_row+1)
  next_row = next_row + nrow(output$tacc_details) + 3
  
  writeData(wb, sheet = 3, "Mismatch details from SPC monthly tables", startCol = 1, startRow = next_row)
  writeData(wb, sheet = 3, output$spc_details, startCol = 1, startRow = next_row+1)
  next_row = next_row + nrow(output$spc_details) + 4
}

print("Writing mismatches for zip")

#Write mismatches for zip
next_row = 3 #reset next_row
for (i in 1:min(nrow(zip_mismatches), records_to_print)){
  current_mismatch = zip_mismatches[i,]
  output = get_mismatch_info(current_mismatch)
  
  writeData(wb, sheet = 4, "Mismatch details from yearly tables", startCol = 1, startRow = next_row)
  writeData(wb, sheet = 4, output$mismatch_details, startCol = 1, startRow = next_row + 1)
  next_row = next_row + nrow(output$mismatch_details) + 3
  
  writeData(wb, sheet = 4, "Mismatch details from TACC dw_staging monthly table",
            startCol = 1, startRow = next_row)
  writeData(wb, sheet = 4, output$tacc_details, startCol = 1, startRow = next_row+1)
  next_row = next_row + nrow(output$tacc_details) + 3
  
  writeData(wb, sheet = 4, "Mismatch details from SPC monthly tables", startCol = 1, startRow = next_row)
  writeData(wb, sheet = 4, output$spc_details, startCol = 1, startRow = next_row+1)
  next_row = next_row + nrow(output$spc_details) + 4
}

print("Writing mismatches for plan type")

#Write mismatches for plan type
next_row = 3 #reset next_row
for (i in 1:min(nrow(plan_mismatches), records_to_print)){
  current_mismatch = plan_mismatches[i,]
  output = get_mismatch_info(current_mismatch)
  
  writeData(wb, sheet = 5, "Mismatch details from yearly tables", startCol = 1, startRow = next_row)
  writeData(wb, sheet = 5, output$mismatch_details, startCol = 1, startRow = next_row + 1)
  next_row = next_row + nrow(output$mismatch_details) + 3
  
  writeData(wb, sheet = 5, "Mismatch details from TACC dw_staging monthly table",
            startCol = 1, startRow = next_row)
  writeData(wb, sheet = 5, output$tacc_details, startCol = 1, startRow = next_row+1)
  next_row = next_row + nrow(output$tacc_details) + 3
  
  writeData(wb, sheet = 5, "Mismatch details from SPC monthly tables", startCol = 1, startRow = next_row)
  writeData(wb, sheet = 5, output$spc_details, startCol = 1, startRow = next_row+1)
  next_row = next_row + nrow(output$spc_details) + 4
}


setColWidths(wb, sheet = 1, cols=1:10, widths="auto")

dir.create(file.path(dir), showWarnings = FALSE) #create directory if it does not exist
saveWorkbook(wb, file=path, overwrite=TRUE)

```

# SECTION 99: Close connections and clean-up

```{sql connection = spc, eval=FALSE}
drop table if exists chcdwork.dbo.xz_dwqa_temp1;
drop table if exists chcdwork.dbo.xz_mcd_enrl_mismatches;

```

```{r close-connections, eval=FALSE}
# closes connections if they are open
if (dbIsValid(spc)) {dbDisconnect(spc)}

if (dbIsValid(tac)) {dbDisconnect(tac)} 

```

```{r clear-all-env, eval=FALSE}
# clears R environment
rm(list=ls())
```



